### 2023-05-12 paper/main.tex
Project proposal - WIP

\documentclass{llncs}

%%%%%%%%%%%%%%%%%%%
%%% Packages
%%%%%%%%%%%%%%%%%%%
\usepackage{xcolor}

%%%%%%%%%%%%%%%%%%%
%%% General Cmds
%%%%%%%%%%%%%%%%%%%
\newcommand{\todo}[1]{{\color{red}\bfseries{}TODO: #1}}

\begin{document}
\title{Quantum Pseudo-Telepathy}
\subtitle{The Magic Square Game}

\author{Luigi Soares \and Roberto Rosmaninho}
\institute{%
  Department of Computer Science, UFMG - Brazil \\
  \email{\{luigi.domenico, \todo{email roberto}\}@dcc.ufmg.br}}

\maketitle
% \begin{abstract}
% \end{abstract}

\section*{Proposal}
\label{sec:prop}

We shall rely on the following references (\todo{add proper refs with bib})
\begin{itemize}
\item Quantum Pseudo-Telepathy (Gilles Brassard, Anne Broadbent and
  Alain Tapp; Magic Square = Sec.\ 5)
\end{itemize}

\end{document}

### 2023-05-13 paper/main.tex
Initial description of the magic square game

@@
 
-We shall rely on the following references (\todo{add proper refs with bib})
+Telepathy, the ability of transmitting information from one person's
+mind to another's, would certainly come in handy in many situations,
+right? Unfortunately (or not), (to the best of our knowledge)
+telepathy is not a thing. At least, not according to classical
+physics. Certain aspects of the quantum realm, however, provide a way
+of communication that for a layman looks as magical as ``true''
+telepathy. This phenomenon is called quantum
+\emph{pseudo-telepathy}~\cite{brassard:2005}.
+
+Quantum pseudo-telepathy is observed in many contexts, usually
+described in the format of a game: the ``impossible colouring games'',
+based on the Kochen-Specker theorem~\cite{brassard:2005, xxx}; the
+parity games, in which \(n \geq 3\) players are given bit-strings and,
+without communicating to each other, they output one of their bits,
+winning if their outputs combined obey certain parity
+conditions~\cite{brassard:2005, xxx}; the Deutsch-Jozsa games, where
+Alice and Bob are given bit strings \(x\) and \(y\), and must output
+bit strings \(a\) and \(b\) such that \(a = b\) if and only if
+\(x = y\)~\cite{brassard:2005, xxx}; and, the Magic Square game, the
+topic of this research\cite{brassard:2005, xxx}. None of these games
+admit a classical winning strategy (i.e.\ is not possible to always
+win), yet they can be won systematically, without any communication,
+provided that the players share prior
+entanglement\cite{brassard:2005}.
+
+A \emph{Magic Square} is a \(3 \times 3\) matrix whose entries are
+\{-1, 1\} (or sometimes \{0,~1\}), with the property that the sum of
+each row is \(1\) and the sum of each column is \(1\). The Magic
+Square game is defined as follows: a referee Charlie asks Alice to
+fill the entries of a row \(x \in \{0, 1, 2\}\), which he chooses
+uniformly at random. Charlie, then, asks Bob to fill the entries of a
+column \(y \in \{0, 1, 2\}\), also chosen at random. Alice and Bob win
+if the product of the row given by Alice is \(1\), the product of the
+column given by Bob is \(-1\) and the intersection of the given row
+and column agrees. A successful implementation of a quantum winning
+strategy for any pseudo-telepathy game must convince an observer that
+something classicaly impossible is
+happening\cite{brassard:2005}. Fortunately, as we shall see, proving
+the classical impossibility of the Magic Square game is extremely easy.
+
+We shall rely on the following references (\todo{add proper refs with
+  bib})
 \begin{itemize}

### 2023-05-15 paper/main.tex
Step by step

@@
 \{-1, 1\} (or sometimes \{0,~1\}), with the property that the sum of
-each row is \(1\) and the sum of each column is \(1\). The Magic
+each row is \(1\) and the sum of each column is \(-1\). The Magic
 Square game is defined as follows: a referee Charlie asks Alice to
@@
 column given by Bob is \(-1\) and the intersection of the given row
-and column agrees. A successful implementation of a quantum winning
-strategy for any pseudo-telepathy game must convince an observer that
-something classicaly impossible is
-happening\cite{brassard:2005}. Fortunately, as we shall see, proving
-the classical impossibility of the Magic Square game is extremely easy.
+and column agrees.
 
-We shall rely on the following references (\todo{add proper refs with
+A successful implementation of a quantum winning strategy for any
+pseudo-telepathy game must convince an observer that something
+classicaly impossible is happening\cite{brassard:2005}. Fortunately,
+proving the classical impossibility of the Magic Square game is
+extremely easy. Assuming a deterministic strategy, even if Alice and
+Bob are allowed to talk \emph{before} the game starts, the best that
+they can do is to construct two grids in advance, one for Alice and
+another for Bob, and give the entries according to the matrices
+that they prepared. However, the product of Alice's matrix will always
+be \(1\) and the product of Bob's matrix will always be \(-1\), so
+there must be one cell that does not agree. Probabilistic strategies
+cannot do better than deterministic~\cite[Theorem 2]{brassard:2005}, so
+the Magic Square game cannot be won under classical assumptions.
+
+We will approach this project as follows:
+
+\begin{enumerate}
+\item Describe the quantum Magic Square game in details;
+\item Discuss classical solutions: illustrate with examples and
+  implement them (and make the code available through a jupyter
+  notebook).
+\item Demonstrate that no classical strategy can win with probability
+  1. Show that the best that a classical strategy can achieve is
+  is win 8 out of 9 rounds;
+\item Discuss the quantum solution, using entanglement: illustrate
+  with examples;
+\item Demonstrate that the quantum strategy can win with probability
+  1; and
+\item Implement the quantum solution in Qiskit
+  (and make the code available through a jupyter notebook).
+\end{enumerate}
+
+We will rely on the following references (\todo{add proper refs with
   bib})

### 2023-05-27 paper/main.tex
Add references
skeleton of paper

--- 2023-05-12 paper/main.tex
@@
 \usepackage{xcolor}
+\usepackage[backend=biber, style=lncs]{biblatex}
+\addbibresource{ref.bib}
+% !TEX TS-program = pdflatexmk
 
+\usepackage{geometry}
+\geometry{
+  a4paper,         % or letterpaper
+  textwidth=15cm,  % llncs has 12.2cm
+  textheight=24cm, % llncs has 19.3cm
+  hratio=1:1,      % horizontally centered
+  vratio=2:3,      % not vertically centered
+}
 %%%%%%%%%%%%%%%%%%%
@@
   Department of Computer Science, UFMG - Brazil \\
-  \email{\{luigi.domenico, \todo{email roberto}\}@dcc.ufmg.br}}
+  \email{\{luigi.domenico, robertogomes\}@dcc.ufmg.br}}
 
@@
 
-\section*{Proposal}
-\label{sec:prop}
+\section{Introduction}
+\label{sec:intro}
 
-We shall rely on the following references (\todo{add proper refs with bib})
-\begin{itemize}
-\item Quantum Pseudo-Telepathy (Gilles Brassard, Anne Broadbent and
-  Alain Tapp; Magic Square = Sec.\ 5)
-\end{itemize}
+Telepathy, the ability of transmitting information from one
+person's mind to another's, would certainly come in handy in
+many situations, right? Unfortunately (or not), (to the best
+of our knowledge) telepathy is not a thing. At least, not
+according to classical physics. Certain aspects of the
+quantum realm, however, provide a way of communication that
+for a layman looks as magical as ``true'' telepathy. This
+phenomenon is called quantum
+\emph{pseudo-telepathy}~\cite{brassard:2005}.
 
+Quantum pseudo-telepathy is observed in many contexts,
+usually described in the format of a game: the ``impossible
+colouring games''~\cite{brassard:2005, Kochen1975}; the
+parity games, in which \(n \geq 3\) players are given
+bit-strings and, without communicating to each other, they
+output one of their bits, winning if their outputs combined
+obey certain parity conditions~\cite{brassard:2005,
+  Mermin1990}; the Deutsch-Jozsa games, where Alice and Bob
+are given bit strings \(x\) and \(y\), and must output bit
+strings \(a\) and \(b\) such that \(a = b\) if and only if
+\(x = y\)~\cite{brassard:2005, Brassard_1999}; and, the
+Magic Square game~\cite{brassard:2005, Mermin1990}. None of
+these games admit a classical winning strategy (i.e.\ is not
+possible to always win), yet they can be won systematically,
+without any communication, provided that the players share
+prior entanglement~\cite{brassard:2005}.
+
+In this project, we shall explore the Mermin-Peres Magic
+Square game. The origins of this game date back to the
+ninities. It was first described ---~albeit not in the format of a
+game~--- in the works of Mermin~\cite{mermin:1990} and of
+Peres~\cite{peres:1990}. Their results provided (as per the
+title of Mermin's review letter) a simplied proof for the
+Kochen-Specker theorem~\cite{Kocher1975}. Later, in 2002,
+Aravind demonstrated how to transform Mermin-Peres's proof
+of then Kochen-Specker theorem into a proof of Bell's
+theorem~\cite{aravind:xxx}. Bell's theorem shows the
+incompatibility of hidden variables (i.e. determinism) and
+locality, whereas Kochen-Specker's theorem demonstrates the
+conflicting nature of determinism and non-contextuality.
+These sort of results may seem challenging, but their
+descriptions can be greatly simplified by modeling them as
+quantum games.  In particular, it is extremely easy to show
+that there cannot be a classical solution to the the Magic
+Square game, and to convince an observer that something
+``magical'' (classically impossible) is happening in a
+successful implementation of a quantum winnin
+strategy~\cite{brassard:2005}.
+
+\paragraph{Outline of this paper.}
+\section{Non-Locality and Contextuality}
+\label{sec:local-context}
+
+\section{Quantum Pseudo-Telepathy}
+\label{sec:telepathy}
+
+\section{The Magic Square Game}
+\label{sec:magic-square}
+
+\subsection{Classical Solution}
+\label{sec:classic-sol}
+
+\subsection{Quantum Solution}
+\label{sec:quantum-sol}
+
+\section{Quantum Unitaries (? research)}
+\label{sec:quantum-unitaries}
+
+\printbibliography{}
 \end{document}

### 2023-05-27 paper/proposal.tex
skeleton of paper

\documentclass{llncs}

%%%%%%%%%%%%%%%%%%%
%%% Packages
%%%%%%%%%%%%%%%%%%%
\usepackage{xcolor}
\usepackage[backend=biber, style=lncs]{biblatex}
\addbibresource{ref.bib}
% !TEX TS-program = pdflatexmk

%%%%%%%%%%%%%%%%%%%
%%% General Cmds
%%%%%%%%%%%%%%%%%%%
\newcommand{\todo}[1]{{\color{red}\bfseries{}TODO: #1}}

\begin{document}
\title{Quantum Pseudo-Telepathy}
\subtitle{The Magic Square Game}

\author{Luigi Soares \and Roberto Rosmaninho}
\institute{%
  Department of Computer Science, UFMG - Brazil \\
  \email{\{luigi.domenico, robertogomes\}@dcc.ufmg.br}}

\maketitle
% \begin{abstract}
% \end{abstract}

\section*{Proposal}
\label{sec:prop}

Telepathy, the ability of transmitting information from one person's
mind to another's, would certainly come in handy in many situations,
right? Unfortunately (or not), (to the best of our knowledge)
telepathy is not a thing. At least, not according to classical
physics. Certain aspects of the quantum realm, however, provide a way
of communication that for a layman looks as magical as ``true''
telepathy. This phenomenon is called quantum
\emph{pseudo-telepathy}~\cite{brassard:2005}.

Quantum pseudo-telepathy is observed in many contexts, usually
described in the format of a game: the ``impossible colouring games'',
based on the Kochen-Specker theorem~\cite{brassard:2005, Kochen1975}; the
parity games, in which \(n \geq 3\) players are given bit-strings and,
without communicating to each other, they output one of their bits,
winning if their outputs combined obey certain parity
conditions~\cite{brassard:2005, Mermin1990}; the Deutsch-Jozsa games, where
Alice and Bob are given bit strings \(x\) and \(y\), and must output
bit strings \(a\) and \(b\) such that \(a = b\) if and only if
\(x = y\)~\cite{brassard:2005, Brassard_1999}; and, the Magic Square game, the
topic of this research\cite{brassard:2005, Mermin1990}. None of these games
admit a classical winning strategy (i.e.\ is not possible to always
win), yet they can be won systematically, without any communication,
provided that the players share prior
entanglement\cite{brassard:2005}.

A \emph{Magic Square} is a \(3 \times 3\) matrix whose entries are
\{-1, 1\} (or sometimes \{0,~1\}), with the property that the sum of
each row is \(1\) and the sum of each column is \(-1\). The Magic
Square game is defined as follows: a referee Charlie asks Alice to
fill the entries of a row \(x \in \{0, 1, 2\}\), which he chooses
uniformly at random. Charlie, then, asks Bob to fill the entries of a
column \(y \in \{0, 1, 2\}\), also chosen at random. Alice and Bob win
if the product of the row given by Alice is \(1\), the product of the
column given by Bob is \(-1\) and the intersection of the given row
and column agrees.

A successful implementation of a quantum winning strategy for any
pseudo-telepathy game must convince an observer that something
classicaly impossible is happening\cite{brassard:2005}. Fortunately,
proving the classical impossibility of the Magic Square game is
extremely easy. Assuming a deterministic strategy, even if Alice and
Bob are allowed to talk \emph{before} the game starts, the best that
they can do is to construct two grids in advance, one for Alice and
another for Bob, and give the entries according to the matrices
that they prepared. However, the product of Alice's matrix will always
be \(1\) and the product of Bob's matrix will always be \(-1\), so
there must be one cell that does not agree. Probabilistic strategies
cannot do better than deterministic~\cite[Theorem 2]{brassard:2005}, so
the Magic Square game cannot be won under classical assumptions.

We will approach this project as follows:

\begin{enumerate}
\item Describe the quantum Magic Square game in details;
\item Discuss classical solutions: illustrate with examples and
  implement them (and make the code available through a jupyter
  notebook).
\item Demonstrate that no classical strategy can win with probability
  1. Show that the best that a classical strategy can achieve is
  is win 8 out of 9 rounds;
\item Discuss the quantum solution, using entanglement: illustrate
  with examples;
\item Demonstrate that the quantum strategy can win with probability
  1; and
\item Implement the quantum solution in Qiskit
  (and make the code available through a jupyter notebook).
\end{enumerate}

\printbibliography{}
\end{document}

### 2023-06-01 paper/main.tex
Classical sol

@@
 %%%%%%%%%%%%%%%%%%%
-\usepackage{xcolor}
 \usepackage[backend=biber, style=lncs]{biblatex}
@@
 }
+
+\usepackage[table]{xcolor}
+\usepackage{subcaption}
+\usepackage{amsmath}
+\usepackage{nicefrac}
+\usepackage{hhline}
+\usepackage{bigdelim}
+
 %%%%%%%%%%%%%%%%%%%
@@
 
-In this project, we shall explore the Mermin-Peres Magic
-Square game. The origins of this game date back to the
-ninities. It was first described ---~albeit not in the format of a
-game~--- in the works of Mermin~\cite{mermin:1990} and of
-Peres~\cite{peres:1990}. Their results provided (as per the
+In this project, we shall explore the Mermin-Peres Magic Square game
+(hereinafter referred simply as Magic Square). The origins of this
+game date back to the ninities. It was first described ---~albeit not
+in the format of a game~--- in the works of Mermin~\cite{mermin:1990}
+and of Peres~\cite{peres:1990}. Their results provided (as per the
 title of Mermin's review letter) a simplied proof for the
-Kochen-Specker theorem~\cite{Kocher1975}. Later, in 2002,
-Aravind demonstrated how to transform Mermin-Peres's proof
-of then Kochen-Specker theorem into a proof of Bell's
-theorem~\cite{aravind:xxx}. Bell's theorem shows the
-incompatibility of hidden variables (i.e. determinism) and
-locality, whereas Kochen-Specker's theorem demonstrates the
-conflicting nature of determinism and non-contextuality.
-These sort of results may seem challenging, but their
-descriptions can be greatly simplified by modeling them as
-quantum games.  In particular, it is extremely easy to show
-that there cannot be a classical solution to the the Magic
-Square game, and to convince an observer that something
-``magical'' (classically impossible) is happening in a
-successful implementation of a quantum winnin
-strategy~\cite{brassard:2005}.
+Kochen-Specker theorem~\cite{Kocher1975}. Later, in 2002, Aravind
+demonstrated how to transform Mermin-Peres's proof of then
+Kochen-Specker theorem into a proof of Bell's
+theorem~\cite{aravind:xxx}. Bell's theorem shows the incompatibility
+of hidden variables (i.e. determinism) and locality, whereas
+Kochen-Specker's theorem demonstrates the conflicting nature of
+determinism and non-contextuality.  These sort of results may seem
+challenging, but their descriptions can be greatly simplified by
+modeling them as quantum games.  In particular, it is extremely easy
+to show that there cannot be a classical solution to the the Magic
+Square game, and to convince an observer that something ``magical''
+(classically impossible) is happening in a successful implementation
+of a quantum winnin strategy~\cite{brassard:2005}.
+
+\todo{FIX: they talk about contextuality only (both theorems)}
 
 \paragraph{Outline of this paper.}
-\section{Non-Locality and Contextuality}
+\section{Contextuality}
 \label{sec:local-context}
-
-\section{Quantum Pseudo-Telepathy}
-\label{sec:telepathy}
 
@@
 
+A magic square is a \(3 \times 3\) matrix whose entries are filled
+with \(\pm 1\)'s. The product of every row of a magic square must be
+\(+1\). Similarly, the product of every column of a magic square must
+be \(-1\). Is impossible to satisfy these two properties at the same
+time, hence the term \emph{magic}: such a matrix cannot exist. The
+Magic Square game features two players, Alice and Bob, that must work
+together to fill in entries of the \(3 \times 3\) table.  At the
+beginning of the game, Alice and Bob are separated by a referee,
+Charlie, so that communication between them is impossible. At each
+round, Charlie assigns one row of the matrix at random to Alice, and
+asks Alice to give him the entries to fill in that particular
+row. After that, Charlie visits Bob and asks him to fill one column of
+the table, which Charlie draws at random.  Bob does not know which row
+Alice was assigned, and Alice does not know which colum Bob was
+assigned. Alice and Bob win the round if their answers are valid,
+i.e.\ the product of the row filled by Alice is \(+1\) and the product
+of the column filled by Bob is \(-1\), and, in addition, the
+intersection of the row and the column agrees (i.e. both answered
+\(+1\) or both answered \(-1\)). Before the game starts, Alice and Bob
+are allowed to communicate, so they can come up with an strategy.  For
+example, they may prepare their answers for each row and column
+beforehand, or they may decide to follow a probabilistic strategy.
+
 \subsection{Classical Solution}
@@
 
+Assume that Alice and Bob decided to adopt a deterministic strategy.
+For that, they met before the beginning of the game, and prepared
+their answers for each possible row and column. For example, they
+might have agreed that, if given the first column, Bob shall fill it
+with three \(-1\)'s. Then, whatever row Alice is given, she must fill
+it with either \(\{-1, +1, -1\}\) or \(\{-1, -1, +1\}\). Suppose that
+Alice decided that she would fill any row in the same way:
+\(\{-1, -1, +1\}\). Figure~\ref{fig:classical} (a) shows how the
+predefined matrix would look like. Notice that Alice's rows are
+already defined, but Bob still has to decide how to fill the second
+and third columns. He can, and must, fill the second column with three
+\(-1\)'s, so that whatever row Alice is given, the intersection
+agrees. Intuitively, for the same reason, he should then fill the
+third column with three \(+1\)'s. However, this is not a valid
+strategy, since the product of the last column will be \(+1\) and not
+\(-1\), as required. Thus, Bob must fill at least one of the
+entries of the last column with \(-1\).  By doing that, there will be
+one row and column whose intersection does not agree, and thus one row
+and column for which Alice and Bob lose, as illustrated in
+Figure~\ref{fig:classical} (b). It is not difficult to convince yourself that,
+no matter how Alice and Bob decide to fill in their entries, it is impossible
+for them to come up with predefined answers that always win. In fact,
+the best that they can do is to win with probability \(\nicefrac{8}{9}\).
+
+{\renewcommand{\arraystretch}{2}
+\begin{figure}
+  \centering
+  \begin{subfigure}[t]{0.475\textwidth}
+    \[\begin{array}{|>{\quad\columncolor{gray!50}}c<{\quad}|*{2}{>{\quad}c<{\quad}|}}
+        \hhline{---}
+        -1 & -1 & +1 
+        \\ \hhline{---}
+        -1 & -1 & +1 
+        \\ \hhline{---}
+        -1 & -1 & +1 
+        \\ \hhline{---}
+      \end{array}\]
+    \caption{Initially, Alice and Bob agree that Bob shall fill the
+      first column with \(\{-1, -1, -1\}\). Based on this choice,
+      Alice decides to fill all of her rows with
+      \(\{-1, -1, +1\}\).}
+  \end{subfigure}
+  \hfill{}
+  \begin{subfigure}[t]{0.475\textwidth}
+    \[\begin{array}{|*{3}{>{\quad\columncolor{gray!50}}c<{\quad}|}}
+        \hhline{---}
+        -1 & -1 & \cellcolor{red!80!black!55}\pm 1
+        \\ \hhline{---}
+        -1 & -1 & +1
+        \\ \hhline{---}
+        -1 & -1 & +1
+        \\ \hhline{---}
+      \end{array}\]
+    \caption{Bob has to fill the second column with \(-1\)'s, to match
+      Alice's choice. He should also match Alice's choice for each
+      cell of the third column, but he cannot, for the product of
+      the column must be \(-1\).}
+  \end{subfigure}
+  \caption{One possible classical deterministic strategy for the Magic
+    Square game. Following this predefined strategy, Alice and Bob
+    lose when assigned, respectively, the first row and third column,
+    but win in any other scenario. That is, their probability of
+    winning a round is \(\nicefrac{8}{9}\). Gray cells are entries for
+    which Alice's and Bob's choices agree.\label{fig:classical}}
+\end{figure}}
+
+What if Alice and Bob decide for a probabilistic strategy? That is,
+Alice and Bob each carry a coin. When assigned a row/column, they flip
+their coins and fill the entries of the row/column based on the
+outcomes of the coins. Can they do better? To randomly assign values
+to one row (equivalently, one column) is essentially the same as
+randomly selecting one of the \(2^{9}\) possible predefined
+\(3 \times 3\) grids (including those matrices that would lead to
+invalid answers). In other words, a probabilistic strategy for the
+Magic Square game is one in which Alice and Bob randomly select a
+deterministic strategy. Hence, no matter how lucky Alice and Bob are,
+the probability of success of any strategy that they come up with is
+bounded by the winning probability of the best deterministic
+strategy, which is
+\(\nicefrac{8}{9}\). Theorem~\ref{thm:classical-success} formalizes
+this argument.
 \subsection{Quantum Solution}

### 2023-06-04 paper/main.tex
quantum initial state + grid

@@
 \usepackage{bigdelim}
+
+\usepackage{tikz}
+\usetikzlibrary{quantikz2}
+
+\newcommand{\ketbra}[2]{\ensuremath{| #1 \rangle \langle #2 |}}
+\newcommand{\ci}{\mathrm{i}}
+\DeclarePairedDelimiter{\card}{\lvert}{\rvert}
+\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
+\DeclareMathOperator{\tr}{tr}
 
@@
 this argument.
+
 \subsection{Quantum Solution}
 \label{sec:quantum-sol}
+The quantum strategy for the Magic Square game consists of Alice and
+Bob carrying entangled qubits with them. For each round, they need a
+pair of qubits each. Then, when Charlie asks Alice (respectively Bob)
+to fill the entries of the \(i\)-th row (respectively \(j\)-th
+column), Alice measures her two qubits three times. The outcome of
+each measurement gives the value for each cell (in practice, they do
+not even need the third measurement, since they can determine the third
+value from the first two). Key to this strategy is that the outcomes
+of all possible measurements are \(\pm 1\). The initial, entangled state
+is (subscripts \(A\) and \(B\) indicate, respectively,
+Alice's and Bob's qubits)
+\begin{equation}
+  \ket{\psi} = \frac{1}{2}\left(
+    \ket{00}_{A} \otimes \ket{00}_{B} + \ket{01}_{A} \otimes \ket{01}_{B} +
+    \ket{10}_{A} \otimes \ket{10}_{B} + \ket{11}_{A} \otimes \ket{11}_{B}
+  \right).
+\end{equation}
+Figure~\ref{fig:circuit-psi} shows the quantum circuit that can be
+used to prepare the initial state \(\ket{\psi}\).
+
+\begin{figure}[htbp]
+  \centering
+  \begin{quantikz}
+    \lstick{\ket{0}} & \gate{H}
+    \slice[label style={xshift=-15mm}]
+    {\(\frac{1}{2}(\ket{00} + \ket{01} + \ket{10} +
+      \ket{11}) \otimes \ket{00}\)}
+    &&&&& \ctrl{2} &&
+    \\
+    \lstick{\ket{0}} & \gate{H} &&&&&& \ctrl{2} & \\
+    \lstick{\ket{0}} & &&&&& \targ{} && \\
+    \lstick{\ket{0}} & &&&&&& \targ{}
+    \slice[label style={xshift=5mm}]
+    {\(\frac{1}{2}(\ket{0000} + \ket{0101} + \ket{1010} +
+      \ket{1111})\)}
+    &
+  \end{quantikz}
+  \caption{\label{fig:circuit-psi}}
+\end{figure}
+
+As seen in Section~\ref{sec:classic-sol}, the \emph{magic} square is
+called this way because, under classical assumptions, there is no such
+a square: it is impossible to construct a \(3 \times 3\) matrix filled
+with \(\pm 1\)'s, with the constraints that the product of every row
+is \(+1\) and the product of every column is \(-1\). We can, however,
+construct a ``quantum magic'' square. Figure~\ref{fig:quantum} shows
+the \(3 \times 3\) grid that Alice and Bob can use to win the Magic
+Square game systematically.  Notice that the eigenvalues of the
+observables at each cell are \(\pm 1\). Furthermore, the product of
+every row is \(+I\) and the product of every column is \(-I\). (The
+original observables did not have the negative \(X\) and \(Z\) in the
+last row, so these two properties are not mandatory~\cite{Mermin1990,
+  aravind:xxx}.  We have adapted the observables merely to be
+``consistent'' with the properties of the classical magic square, but
+what really matters for Alice and Bob are the outcomes of the
+measurements, which they will use to fill the entries asked by
+Charlie.)
+
+{\renewcommand{\arraystretch}{2}
+\begin{figure}
+  \centering
+  \[\begin{array}{|*{3}{>{\quad}c<{\quad}|}>{\quad}l<{\quad}}
+      \hhline{---~}
+      +I \otimes Z & +Z \otimes I & +Z \otimes Z & \prod = I \otimes I = I
+      \\ \hhline{---~}
+      +X \otimes I & +I \otimes X & +X \otimes X & \prod = I \otimes I = I
+      \\ \hhline{---~}
+      -X \otimes Z & -Z \otimes X & +Y \otimes Y & \prod = -\ci{}I \otimes \ci{}I = I
+      \\ \hhline{---~}
+      \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
+      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
+      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = \ci{}I \otimes \ci{}I = -I}
+    \end{array}\]
+  \caption{\label{fig:quantum}}
+\end{figure}}
 

### 2023-06-04 paper/tikzlibraryquantikz2.code.tex
quantum initial state + grid

%This is the quantikz library for typesetting quantum circuits using LaTeX/Tikz. version 1.0.0
% Written by Alastair Kay, 2018. Published under a CC-BY-4.0 licence
% Please email me (alastair.kay@rhul.ac.uk) with any bug reports or feature requests.
% If you find this library useful, please cite its usage in your work, using arXiv:1809.03842, and possibly the DOI: 10.17637/rh.7000520.
% Usage is at your own risk.

%version 1.0.0
%major new revision with massive under-the-hood changes in how wires work.
%aiming to reduce technical debt in the code as well.
%use the \wire commands for all your wire needs
%fix wire types using wire types={} key, and function setwiretype{}
%check your circuits for places where you assumed there would be no wire.
%some minor changes in optional parameters (e.g. \meter). In practice, these are rarely used, and unlikely to be an issue.
%should always use quantikz and not tikzcd environment

%to-do
%complete rewrite of manual
%add isosceles triangle example to manual
%fix ampersand replacement (is it even necessary any more?). Check beamer.

%\ProvidesPackage{quantikz}[2023/04/03 typeset quantum circuit diagrams]

% Package(s) to include
\RequirePackage{xargs,ifthen,xstring,xparse,etoolbox,mathtools,pgfmath}
\RequirePackage{environ} %in an attempt to help with compatibility with the external library of tikz.
%\RequirePackage{tikz}
\usetikzlibrary{cd,decorations.pathreplacing,calc,positioning,fit,shapes.symbols,decorations.pathmorphing,shapes.misc,decorations.markings,math}
\pgfdeclarelayer{background}
\pgfdeclarelayer{quantback}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%create the new quantikz environment
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%I need this to facilitate the external library
%solution taken from https://tex.stackexchange.com/questions/171931/are-the-tikz-libraries-cd-and-external-incompatible-with-one-another
%this does a global redefinition of the &. This is not good as it will lead to incompatibilities with other packages.
%there seems to be a solution https://tex.stackexchange.com/a/633066/148934
%another option, more similar to the original: https://tex.stackexchange.com/a/619983/148934
% \newcommand{\mytikzcdcontext}[2]{
%       \begin{tikzcd}[#1]
%         #2
%       \end{tikzcd}%
% }
%could I do this to align instead?
% \NewDocumentEnvironment{quantikz}{O{}+b}{%
%   \begingroup \catcode`&=\active
%   \def\@temp{\tikzcd@[#1]\scantokens{#2}}%
%   \expandafter\@temp\endtikzcd\endgroup
% }{}
%full solution suggested here https://tex.stackexchange.com/a/682872/148934
\ExplSyntaxOn
\NewDocumentEnvironment{quantikz}{O{}+b}{
\gdef\toslice{0}\def\vert{0}%
  \begin{tikzpicture}[/tikz/commutative~diagrams/.cd, every~diagram,baseline={([yshift=-axis_height]\tikzcdmatrixname)}, #1]
  \pgfsetlayers{background,quantback,main}
    \tl_set:Nn \l_tmpa_tl { #2 }
    \tl_replace_all:Nnn \l_tmpa_tl { & } { \pgfmatrixnextcell }
    \begingroup%doing it like this, we don't need to patch tikzcd, so it will continue to work independently.
      \def\tikzpicture[##1]{}
      \let\endtikzpicture\relax
      \tikzcd[#1]
        \l_tmpa_tl
      \endtikzcd
    \endgroup
  \end{tikzpicture}
}{}
\ExplSyntaxOff

% \ExplSyntaxOn
% \NewDocumentEnvironment{quantikz}{O{}+b}{%
%   \tl_rescan:nn { \char_set_catcode_active:N \& } { \begin{tikzcd}[#1] #2 \end{tikzcd} }
% }{}
% \ExplSyntaxOff

% \newcommand{\mytikzcdcontext}[2]{
%   \begin{tikzpicture}[baseline=(maintikzcdnode.base)]
%     \node (maintikzcdnode) [inner sep=0, outer sep=0] {%
%       \begin{tikzcd}[#1]
%         #2
%       \end{tikzcd}%
%     };
%   \end{tikzpicture}%
% }

% \ExplSyntaxOn

% \NewDocumentEnvironment{quantikz}{O{}+b}
%  {
%   \tl_set:Nn \l_tmpa_tl { #2 }
%   \regex_replace_all:nnN { \& } { \cA\& } \l_tmpa_tl
%   \weird_wonderful_mytikzcd:nV { #1 } \l_tmpa_tl
%  }
%  {}

% \cs_set_eq:NN \weird_wonderful_mytikzcd:nn \mytikzcdcontext
% \cs_generate_variant:Nn \weird_wonderful_mytikzcd:nn { nV }

% \ExplSyntaxOff

%patch tikzcd to allow for multiple layers of commands that get deferred until later
% \patchcmd\tikzcd@{\tikzpicture}{%
%   \def\toslice{0}\def\vert{0}%
%  \begin{tikzpicture}}{}{}
%\patchcmd\tikzcd@{\tikzpicture[/tikz/commutative diagrams/.cd,every diagram,#1]}{%
%}{}{}
\patchcmd\tikzcd@
    {\global\let\tikzcd@savedpaths\pgfutil@empty}
    {\global\let\tikzcd@savedpaths\pgfutil@empty
    \pgfutil@g@addto@macro\tikzcd@savedpaths{\begin{scope}[/tikz/commutative diagrams/.cd,#1]}
    \pgfsetlayers{background,quantback,main}
    \global\let\tikzcd@atendsavedpaths\pgfutil@empty
    \global\let\tikzcd@atendlabels\pgfutil@empty
    \global\let\tikzcd@atendslices\pgfutil@empty
    \pgfutil@g@addto@macro\tikzcd@savedpaths\DivideRowsCols
    \def\tikz@lib@matrix@empty@cell{
      \iftikz@lib@matrix@empty\node[name=\tikzmatrixname-\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn,
      minimum width=\ifcsundef{cell@width@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}{0}{\csname cell@width@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn\endcsname},
      minimum height=\ifcsundef{cell@height@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}{0}{\csname cell@height@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn\endcsname}
      ]{};\wire{a}\fi
      \csgundef{cell@width@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
      \csgundef{cell@height@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}}
    %\pgfmathsetmacro{\mname}{random(100000)}
    \ifcsstring{toslice}{1}{\ifcsstring{vert}{0}{\pgfutil@g@addto@macro\tikzcd@atendslices\sliceallr}{\pgfutil@g@addto@macro\tikzcd@atendslices\sliceallvr}}{}
    %\ifthenelse{\toslice=1}{\ifthenelse{\vert=0}{\PackageWarning{quantikz}{We are slicing}\pgfutil@g@addto@macro\tikzcd@atendslices\sliceallr}{\pgfutil@g@addto@macro\tikzcd@atendslices\sliceallvr}}{}
    }{}{}

%this patching works on modern systems, but I believe is incompatible with the old version that arXiv is running
%\patchcmd\endtikzcd{\tikzcd@savedpaths}{\tikzcd@savedpaths\tikzcd@atendsavedpaths\tikzcd@atendlabels\tikzcd@atendslices}{}{}

%instead, completely redefine the function
\def\endtikzcd{%
  \pgfmatrixendrow\egroup%
  \pgfextra{\global\let\tikzcdmatrixname\tikzlastnode};%
  \tikzcdset{\the\pgfmatrixcurrentrow-row diagram/.try}%
  \begingroup%
    \pgfkeys{% `quotes' library support
      /handlers/first char syntax/the character "/.initial=\tikzcd@forward@quotes,%
      /tikz/edge quotes mean={%
        edge node={node [execute at begin node=\iftikzcd@mathmode$\fi,%$
                         execute at end node=\iftikzcd@mathmode$\fi,%$
                         /tikz/commutative diagrams/.cd,every label,##2]{##1}}}}%
    \let\tikzcd@errmessage\errmessage% improve error messages
    \def\errmessage##1{\tikzcd@errmessage{##1^^J...^^Jl.\tikzcd@lineno\space%
        I think the culprit is a tikzcd arrow in cell \tikzcd@currentrow-\tikzcd@currentcolumn}}%
    \tikzcd@before@paths@hook%
    \begin{pgfonlayer}{quantback}
      \tikzcd@savedpaths
    \end{scope}
    \end{pgfonlayer}
    \tikzcd@atendsavedpaths\tikzcd@atendlabels\tikzcd@atendslices%I just added stuff here instead
    \resetwiretypes%reset wire types
    \def\tikz@lib@matrix@empty@cell{\iftikz@lib@matrix@empty\node[name=\tikzmatrixname-\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn]{};\fi}%
  \endgroup%
  \endtikzpicture%
  \ifnum0=`{}\fi}

%end patching

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% the basic wire command
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ExplSyntaxOn
% take a direction, such as d and repeat it the required number of times
\NewExpandableDocumentCommand{\myrepeat}{O{}mm}
 {
  \int_compare:nT { #2 > 0 }
   {
    #3 \prg_replicate:nn { #2 - 1 } { #1#3 }
   }
 }
\ExplSyntaxOff

%this is the main entry point for people
%converts a wire command with distance into one using repeated letters (main directions only)
\NewDocumentCommand{\wire}{O{l}O{1}O{}m}{%direction (l/r/u/d), distance, decoration, quantum/classical/bundle/none
\ifstrequal{#2}{0}{%
\PackageWarning{quantikz}{You seem to have a wire of zero length. I believe the problem is in cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}.
}{%
  \edef\length{\myrepeat{#2}{#1}}
\ifthenelse{\the\pgfmatrixcurrentcolumn>1}{%
\expandafter\fullwire\expandafter{\length}{#1}{#4}{#3}%
}{}
}}
%does the actual business of creating the different wire types with the correct anchors
%uses custom anchors on shapes for classical wires. We'll come to this in a minute.
\newcommand{\fullwire}[4]{%direction with repetition. direction. type. decoration
\edef\wiretype{#3}
\ifstrequal{#3}{a}{%automatic determination
  \ifcsundef{wire@type@\the\pgfmatrixcurrentrow}{%type not defined globally. assume quantum.
  \edef\wiretype{q}
  }{%
  \edef\wiretype{\csname wire@type@\the\pgfmatrixcurrentrow\endcsname}
  \ifdefstring{\wiretype}{u}{%
    \edef\wiretype{q}
  }{}
  }
  \ifcsdef{wire@type@override@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}{%
    \edef\wiretype{\csname wire@type@override@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn\endcsname}
  }{}
}{}
\ifdefstring{\wiretype}{q}{%quantum wire
    \arrow[#1,arrows,#4] {}
  }{%
  \ifdefstring{\wiretype}{c}{%classical wire
    \arrow[arrows,start anchor=#2startone,end anchor=#2endone] {#1}\arrow[arrows,start anchor=#2starttwo,end anchor=#2endtwo,#4] {#1}
  }{%
  \ifdefstring{\wiretype}{b}{%wire bundle
    \arrow[arrows,start anchor=#2startone,end anchor=#2endone,#4] {#1}\arrow[arrows,start anchor=#2starttwo,end anchor=#2endtwo,#4] {#1}\arrow[#1,arrows,#4] {}
  }{%
  \ifdefstring{\wiretype}{n}{%no wire
  }{\ifdefstring{\wiretype}{u}{%unset
  }{\PackageWarning{quantikz}{unknown wire type in cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}}}}}}
}

\newcommand{\setwiretype}[2][\the\pgfmatrixcurrentrow]{%
%this command will record what the current wire type is supposed to be
\ifstrequal{#2}{u}{
  \csgundef{wire@type@#1}
}{
\expandafter\gdef\csname wire@type@#1\endcsname{#2}%will need to reset all these variables at the beginning/end of a circuit.
}
}

\NewDocumentCommand{\wireoverride}{O{\the\pgfmatrixcurrentrow}O{\the\pgfmatrixcurrentcolumn}m}{%
%change the wire type of this specific cell without unsetting the global wire type of this cell.
\expandafter\gdef\csname wire@type@override@#1-#2\endcsname{#3}
}

\newcounter{dummy}
\newcommand{\importwiretypes}[1]{%
%receive a list of wire types. Process them into individual variables
\setcounter{dummy}{1}% 
  \foreach \thiswire [count=\rownum] in {#1} {%
    \expandafter\expandafter\expandafter\setwiretype\expandafter\expandafter\expandafter[\expandafter\rownum\expandafter]\expandafter{\thiswire}
    \stepcounter{dummy}
     }
     \pgfmathparse{\arabic{dummy}/2}
     %\pgfmathresult
     \expandafter\setmiddle\expandafter{\pgfmathresult}
  }%

\newcommand{\resetwiretypes}{%try to reset all definitions of per-row wire types
  \foreach \rownum in {1,...,\the\pgfmatrixcurrentrow} {%
\expandafter\setwiretype\expandafter[\rownum]{u} 
  }
}

\tikzset{%
  strike arrow/.style n args={3}{
    decoration={markings, mark=at position 0.5 with {
        \draw [internal,-] 
            ++ (#1, #2 )
            -- ( -#1, -#2) node [anchor=south west, inner sep=0pt] {$\scriptstyle #3$};} %can I use pgfkeys and do some maths here?
    },
    postaction={decorate},
}}
%this used to be a more complex command, but is now only used for adding the strikethrough + number
\newcommand{\qwbundle}[2][]{%
		%\ifthenelse{\the\pgfmatrixcurrentcolumn=2}{%do the strikethrough
  \pgfkeys{/quantikz/gates/.cd,style=,Strike Width=0.08cm,Strike Height=0.12cm,#1} 
  \pgfkeysgetvalue{/quantikz/gates/style}{\style}
  \pgfkeysgetvalue{/quantikz/gates/Strike Width}{\sw}
  \pgfkeysgetvalue{/quantikz/gates/Strike Height}{\sh}
  \edef\arg{strike arrow={\sw}{\sh}{#2},\style}
			\expandafter\arrow\expandafter[\arg,phantom]{l}%
	}

%%%%%%%%%%%%%%%%%%%%%%%%%
%
% deprecated wire commands provided for backwards compatibility
%
%%%%%%%%%%%%%%%%%%%%%%%%%

%now add some of the basic wire commands for backwards compatibility. These should be largely superfluous once I'm done.
\newcommand{\vcw}[1]{%vertical classical wire. goes down by the amount specified in arg
\ifnumcomp{#1}{>}{0}{%
  \wire[d][#1]{c}
}{\ifnumcomp{#1}{<}{0}{%
  \wire[u][-#1]{c}
}{\PackageWarning{quantikz}{You seem to have a vertical classical wire with no height in cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn!}}}
}
%vertical quantum wire, relative positioning
\newcommand{\vqw}[1]{
\ifnumcomp{#1}{>}{0}{%
  \wire[d][#1]{q}
}{\ifnumcomp{#1}{<}{0}{%
  \wire[u][-#1]{q}
}{\PackageWarning{quantikz}{You seem to have a vertical quantum wire with no height in cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn!}}}
}

%basic horzontal quantum wire, length 1. Goes backwards 1 cell. Won't do anything in the first cell.
\newcommand{\qw}{\wire{q}}
%basic horzontal classical wire, length 1. Goes backwards 1 cell. Won't do anything in the first cell.
\newcommand{\cw}{\wire{c}}
%use for fudging classical wires that have horizontal and vertical sections
%shouldn't really be necessary any more?
\NewExpandableDocumentCommand{\cwbend}{m}{
  \phase{}\vcw{#1}\cw
  % \edef\cell{\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
  % \expandafter\pgfutil@g@addto@macro\expandafter\tikzcd@atendlabels\expandafter{%
  %   \expandafter\latephase@end\expandafter{\cell}
  % }
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% shape definitions
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%we will mainly be using rectangle and circle as base shapes. Also signal, rounded rectangle for some measurement objects. cross out for swap.
%First we need to add custom anchors to them for attaching the wires.

%helper functions
\newcommand*\pgfdeclareanchoralias[3]{%
    \expandafter\def\csname pgf@anchor@#1@#3\expandafter\endcsname
            \expandafter{\csname pgf@anchor@#1@#2\endcsname}}
\def\pgfaddtoshape#1#2{%
  \begingroup
  \def\pgf@sm@shape@name{#1}%
  \let\anchor\pgf@sh@anchor
  #2%
  \endgroup
}

%add anchors to the rectangle
\pgfaddtoshape{rectangle}{%
    \anchor{dendtwo}{%
    \pgf@process{\southwest}%
    \pgf@xa=.5\pgf@x%
    \pgf@process{\northeast}%
    \pgf@x=.5\pgf@x%
    \advance\pgf@x by \pgf@xa%
    \advance\pgf@x by \pgfkeysvalueof{/tikz/commutative diagrams/classical gap}%
  }%
  \anchor{dstarttwo}{%
    \pgf@process{\northeast}%
    \pgf@xa=.5\pgf@x%
    \pgf@process{\southwest}%
    \pgf@x=.5\pgf@x%
    \advance\pgf@x by \pgf@xa%
    \advance\pgf@x by \pgfkeysvalueof{/tikz/commutative diagrams/classical gap}%
  }%
  \anchor{dendone}{%
    \pgf@process{\southwest}%
    \pgf@xa=.5\pgf@x%
    \pgf@process{\northeast}%
    \pgf@x=.5\pgf@x%
    \advance\pgf@x by \pgf@xa%
    \advance\pgf@x by -\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}%
  }%
  \anchor{dstartone}{%
    \pgf@process{\northeast}%
    \pgf@xa=.5\pgf@x%
    \pgf@process{\southwest}%
    \pgf@x=.5\pgf@x%
    \advance\pgf@x by \pgf@xa%
    \advance\pgf@x by -\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}%
  }%
    \anchor{lstarttwo}{%
    \pgf@process{\northeast}%
    \pgf@ya=.5\pgf@y%
    \pgf@process{\southwest}%
    \pgf@y=.5\pgf@y%
    \advance\pgf@y by \pgf@ya%
    \advance\pgf@y by \pgfkeysvalueof{/tikz/commutative diagrams/classical gap}%
  }%
  \anchor{lendtwo}{%
    \pgf@process{\southwest}%
    \pgf@ya=.5\pgf@y%
    \pgf@process{\northeast}%
    \pgf@y=.5\pgf@y%
    \advance\pgf@y by \pgf@ya%
    \advance\pgf@y by \pgfkeysvalueof{/tikz/commutative diagrams/classical gap}%
  }%
  \anchor{lstartone}{%
    \pgf@process{\northeast}%
    \pgf@ya=.5\pgf@y%
    \pgf@process{\southwest}%
    \pgf@y=.5\pgf@y%
    \advance\pgf@y by \pgf@ya%
    \advance\pgf@y by -\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}%
  }%
  \anchor{lendone}{%
    \pgf@process{\southwest}%
    \pgf@ya=.5\pgf@y%
    \pgf@process{\northeast}%
    \pgf@y=.5\pgf@y%
    \advance\pgf@y by \pgf@ya%
    \advance\pgf@y by -\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}%
  }%
  }
\pgfdeclareanchoralias{rectangle}{dendtwo}{ustarttwo}
\pgfdeclareanchoralias{rectangle}{dendone}{ustartone}
\pgfdeclareanchoralias{rectangle}{dstarttwo}{uendtwo}
\pgfdeclareanchoralias{rectangle}{dstartone}{uendone}
\pgfdeclareanchoralias{rectangle}{lendtwo}{rstarttwo}
\pgfdeclareanchoralias{rectangle}{lendone}{rstartone}
\pgfdeclareanchoralias{rectangle}{lstarttwo}{rendtwo}
\pgfdeclareanchoralias{rectangle}{lstartone}{rendone}

%add anchors to the circle
\pgfaddtoshape{circle}{%
  \anchor{dstartone}{
    \centerpoint
    \pgf@xa=\radius
    \advance\pgf@x by-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}
    \ifdimgreater{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}{\radius}{%
\PackageError{quantikz}{You have tried to create a control object with classical control wire, but "classical gap" is set too large.}{Change the environment parameter for the quantikz environment using the "classical gap=" key to a value smaller than 0.06cm.}
    }{}
    \pgfmathparse{-sqrt(\radius*\radius-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap})}
    \advance\pgf@y by\pgfmathresult pt
  }%
  \anchor{dstarttwo}{
    \centerpoint
    \pgf@xa=\radius
    \ifdimgreater{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}{\radius}{%
\PackageError{quantikz}{You have tried to create a control object with classical control wire, but "classical gap" is set too large.}{Change the environment parameter for the quantikz environment using the "classical gap=" key to a value smaller than 0.06cm.}
    }{}
    \advance\pgf@x by\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}
    \pgfmathparse{-sqrt(\radius*\radius-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap})}
    \advance\pgf@y by\pgfmathresult pt
  }%
  \anchor{dendone}{
    \centerpoint
    \pgf@xa=\radius
    \ifdimgreater{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}{\radius}{%
\PackageError{quantikz}{You have tried to create a control object with classical control wire, but "classical gap" is set too large.}{Change the environment parameter for the quantikz environment using the "classical gap=" key to a value smaller than 0.06cm.}
    }{}
    \advance\pgf@x by-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}
    \pgfmathparse{sqrt(\radius*\radius-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap})}
    \advance\pgf@y by\pgfmathresult pt
  }%
  \anchor{dendtwo}{
    \centerpoint
    \pgf@xa=\radius
    \ifdimgreater{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}{\radius}{%
\PackageError{quantikz}{You have tried to create a control object with classical control wire, but "classical gap" is set too large.}{Change the environment parameter for the quantikz environment using the "classical gap=" key to a value smaller than 0.06cm.}
    }{}
    \advance\pgf@x by\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}
    \pgfmathparse{sqrt(\radius*\radius-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap})}
    \advance\pgf@y by\pgfmathresult pt
  }%
  \anchor{lstartone}{
    \centerpoint
    \pgf@xa=\radius
    \ifdimgreater{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}{\radius}{%
\PackageError{quantikz}{You have tried to create a control object with classical control wire, but "classical gap" is set too large.}{Change the environment parameter for the quantikz environment using the "classical gap=" key to a value smaller than 0.06cm.}
    }{}
    \advance\pgf@y by-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}
    \pgfmathparse{-sqrt(\radius*\radius-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap})}
    \advance\pgf@x by\pgfmathresult pt
  }%
  \anchor{lstarttwo}{
    \centerpoint
    \pgf@xa=\radius
    \ifdimgreater{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}{\radius}{%
\PackageError{quantikz}{You have tried to create a control object with classical control wire, but "classical gap" is set too large.}{Change the environment parameter for the quantikz environment using the "classical gap=" key to a value smaller than 0.06cm.}
    }{}
    \advance\pgf@y by\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}
    \pgfmathparse{-sqrt(\radius*\radius-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap})}
    \advance\pgf@x by\pgfmathresult pt
  }%
  \anchor{lendone}{
    \centerpoint
    \pgf@xa=\radius
    \ifdimgreater{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}{\radius}{%
\PackageError{quantikz}{You have tried to create a control object with classical control wire, but "classical gap" is set too large.}{Change the environment parameter for the quantikz environment using the "classical gap=" key to a value smaller than 0.06cm.}
    }{}
    \advance\pgf@y by-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}
    \pgfmathparse{sqrt(\radius*\radius-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap})}
    \advance\pgf@x by\pgfmathresult pt
  }%
  \anchor{lendtwo}{
    \centerpoint
    \pgf@xa=\radius
    \ifdimgreater{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}{\radius}{%
\PackageError{quantikz}{You have tried to create a control object with classical control wire, but "classical gap" is set too large.}{Change the environment parameter for the quantikz environment using the "classical gap=" key to a value smaller than 0.06cm.}
    }{}
    \advance\pgf@y by\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}
    \pgfmathparse{sqrt(\radius*\radius-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap})}
    \advance\pgf@x by\pgfmathresult pt
  }%
}
\pgfdeclareanchoralias{circle}{dendtwo}{ustarttwo}
\pgfdeclareanchoralias{circle}{dendone}{ustartone}
\pgfdeclareanchoralias{circle}{dstarttwo}{uendtwo}
\pgfdeclareanchoralias{circle}{dstartone}{uendone}
\pgfdeclareanchoralias{circle}{lendtwo}{rstarttwo}
\pgfdeclareanchoralias{circle}{lendone}{rstartone}
\pgfdeclareanchoralias{circle}{lstarttwo}{rendtwo}
\pgfdeclareanchoralias{circle}{lstartone}{rendone}

\pgfaddtoshape{rounded rectangle}{%
%I'm going to cheat and assume it's always wide enough to have a flat bottom/top.
	\anchor{dstartone}{%
 		\roundedrectanglepoints%
 		\pgfpointadd{\centerpoint}{\pgfpoint{-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}{-\halfheight-\outerysep}}%
	}
	\anchor{dstarttwo}{%
 		\roundedrectanglepoints%
 		\pgfpointadd{\centerpoint}{\pgfpoint{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}{-\halfheight-\outerysep}}%
	}
	\anchor{dendone}{%
 		\roundedrectanglepoints%
 		\pgfpointadd{\centerpoint}{\pgfpoint{-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}{\halfheight+\outerysep}}%
	}
	\anchor{dendtwo}{%
 		\roundedrectanglepoints%
 		\pgfpointadd{\centerpoint}{\pgfpoint{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}{\halfheight+\outerysep}}%
	}
	\anchor{lstarttwo}{%
	\roundedrectanglepoints%
    \ifx\westarc\pgf@lib@sh@misc@rr@text@concave%
    %not sure! Just leave it. I don't think even the simple quantum wire works as I want it out the box!
    \pgfpointadd{\centerpoint}{\pgfpoint{-\halfwidth-\outerxsep}{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}%
        % \pgfpathlineto{\pgfpoint{-\halfwidth-\arcwidth}{+-\halfheight}}%
        % \pgfpatharc{+-\halfarcangle}{+\halfarcangle}{+\radius}%
    \else%
        \ifx\westarc\pgf@lib@sh@misc@rr@text@convex%
        		\pgfextract@process\arccenter{%
               	\pgfpointadd{\centerpoint}{\pgfpoint{-\halfwidth-\chordwidth+\radius}{+0pt}}%
            }%
            \pgfmathparse{sqrt((\radius+\outerxsep)^2-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}^2)}
            \pgfpointadd{\arccenter}{\pgfpoint{-\pgfmathresult pt}{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}
        \else%
            \pgfpointadd{\centerpoint}{\pgfpoint{-\halfwidth-\outerxsep}{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}%
        \fi%
    \fi%
	}
	\anchor{lstartone}{%
	\roundedrectanglepoints%
   \ifx\westarc\pgf@lib@sh@misc@rr@text@concave%
    %not sure!
    \pgfpointadd{\centerpoint}{\pgfpoint{-\halfwidth-\outerxsep}{-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}%
    %     % \pgfpathlineto{\pgfpoint{-\halfwidth-\arcwidth}{+-\halfheight}}%
    %     % \pgfpatharc{+-\halfarcangle}{+\halfarcangle}{+\radius}%
    \else%
        \ifx\westarc\pgf@lib@sh@misc@rr@text@convex%
        		\pgfextract@process\arccenter{%
               	\pgfpointadd{\centerpoint}{\pgfpoint{-\halfwidth-\chordwidth+\radius}{+0pt}}%
            }%
            \pgfmathparse{sqrt((\radius+\outerxsep)^2-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}^2)}
            \pgfpointadd{\arccenter}{\pgfpoint{-\pgfmathresult pt}{-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}
        \else%
            \pgfpointadd{\centerpoint}{\pgfpoint{-\halfwidth-\outerxsep}{-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}%
        \fi%
    \fi%
	}	
	\anchor{lendtwo}{%
	\roundedrectanglepoints%
    \ifx\eastarc\pgf@lib@sh@misc@rr@text@concave%
    %not sure!
        % \pgfpathlineto{\pgfpoint{-\halfwidth-\arcwidth}{+-\halfheight}}%
        % \pgfpatharc{+-\halfarcangle}{+\halfarcangle}{+\radius}%
    \else%
        \ifx\eastarc\pgf@lib@sh@misc@rr@text@convex%
        		\pgfextract@process\arccenter{%
               	\pgfpointadd{\centerpoint}{\pgfpoint{\halfwidth+\chordwidth-\radius}{+0pt}}%
            }%
            \pgfmathparse{sqrt((\radius+\outerxsep)^2-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}^2)}
            \pgfpointadd{\arccenter}{\pgfpoint{\pgfmathresult pt}{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}
            %\pgfpathlineto{\pgfpoint{-\halfwidth-\chordwidth+\arcwidth}{+-\halfheight}}%
            %\pgfpatharc{180+\halfarcangle}{180-\halfarcangle}{+\radius}%
        \else%
            \pgfpointadd{\centerpoint}{\pgfpoint{\halfwidth}{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}%
        \fi%
    \fi%
	}
	\anchor{lendone}{%
	\roundedrectanglepoints%
    \ifx\eastarc\pgf@lib@sh@misc@rr@text@concave%
    %not sure!
        % \pgfpathlineto{\pgfpoint{-\halfwidth-\arcwidth}{+-\halfheight}}%
        % \pgfpatharc{+-\halfarcangle}{+\halfarcangle}{+\radius}%
    \else%
        \ifx\eastarc\pgf@lib@sh@misc@rr@text@convex%
        		\pgfextract@process\arccenter{%
               	\pgfpointadd{\centerpoint}{\pgfpoint{\halfwidth+\chordwidth-\radius}{+0pt}}%
            }%
            \pgfmathparse{sqrt((\radius+\outerxsep)^2-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}^2)}
            \pgfpointadd{\arccenter}{\pgfpoint{\pgfmathresult pt}{-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}
            %\pgfpathlineto{\pgfpoint{-\halfwidth-\chordwidth+\arcwidth}{+-\halfheight}}%
            %\pgfpatharc{180+\halfarcangle}{180-\halfarcangle}{+\radius}%
        \else%
            \pgfpointadd{\centerpoint}{\pgfpoint{\halfwidth}{-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}%
        \fi%
    \fi%
	}
	}
\pgfdeclareanchoralias{rounded rectangle}{dendtwo}{ustarttwo}
\pgfdeclareanchoralias{rounded rectangle}{dendone}{ustartone}
\pgfdeclareanchoralias{rounded rectangle}{dstarttwo}{uendtwo}
\pgfdeclareanchoralias{rounded rectangle}{dstartone}{uendone}
\pgfdeclareanchoralias{rounded rectangle}{lendtwo}{rstarttwo}
\pgfdeclareanchoralias{rounded rectangle}{lendone}{rstartone}
\pgfdeclareanchoralias{rounded rectangle}{lstarttwo}{rendtwo}
\pgfdeclareanchoralias{rounded rectangle}{lstartone}{rendone}

\pgfaddtoshape{signal}{%
	\anchor{lstarttwo}{%
		\installsignalparameters
		\let\firstpoint\anchornorthwest
		\let\secondpoint\anchorwest
    \pgfpointintersectionoflines%
      {\firstpoint}%
      {\secondpoint}%
      {\pgfpointadd{\secondpoint}{\pgfpoint{0cm}{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}}%
      {\pgfpointadd{\secondpoint}{\pgfpoint{0.5cm}{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}}%
	}
	\anchor{lstartone}{%
		\installsignalparameters
		\let\firstpoint\anchorsouthwest
		\let\secondpoint\anchorwest
		\pgfpointintersectionoflines%
      {\firstpoint}%
      {\secondpoint}%
      {\pgfpointadd{\secondpoint}{\pgfpoint{0cm}{-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}}%
      {\pgfpointadd{\secondpoint}{\pgfpoint{0.5cm}{-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}}%
	}
	\anchor{lendtwo}{%
		\installsignalparameters
		\let\firstpoint\anchornortheast
		\let\secondpoint\anchoreast
    \pgfpointintersectionoflines%
      {\firstpoint}%
      {\secondpoint}%
      {\pgfpointadd{\secondpoint}{\pgfpoint{0cm}{-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}}%
      {\pgfpointadd{\secondpoint}{\pgfpoint{0.5cm}{-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}}%
	}
	\anchor{lendone}{%
		\installsignalparameters
		\let\firstpoint\anchorsoutheast
		\let\secondpoint\anchoreast
    \pgfpointintersectionoflines%
      {\firstpoint}%
      {\secondpoint}%
      {\pgfpointadd{\secondpoint}{\pgfpoint{0cm}{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}}%
      {\pgfpointadd{\secondpoint}{\pgfpoint{0.5cm}{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}}}%
	}
  \anchor{dstarttwo}{%
  	\installsignalparameters
    \pgf@process{\southanchor}%
    \advance\pgf@x by \pgfkeysvalueof{/tikz/commutative diagrams/classical gap}%
  }%
  \anchor{dstartone}{%
  	\installsignalparameters
    \pgf@process{\southanchor}%
    \advance\pgf@x by -\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}%
  }%
  \anchor{dendtwo}{%
  	\installsignalparameters
    \pgf@process{\northanchor}%
    \advance\pgf@x by \pgfkeysvalueof{/tikz/commutative diagrams/classical gap}%
  }%
  \anchor{dendone}{%
  	\installsignalparameters
    \pgf@process{\northanchor}%
    \advance\pgf@x by -\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}%
  }%}
 }
\pgfdeclareanchoralias{signal}{dendtwo}{ustarttwo}
\pgfdeclareanchoralias{signal}{dendone}{ustartone}
\pgfdeclareanchoralias{signal}{dstarttwo}{uendtwo}
\pgfdeclareanchoralias{signal}{dstartone}{uendone}
\pgfdeclareanchoralias{signal}{lendtwo}{rstarttwo}
\pgfdeclareanchoralias{signal}{lendone}{rstartone}
\pgfdeclareanchoralias{signal}{lstarttwo}{rendtwo}
\pgfdeclareanchoralias{signal}{lstartone}{rendone}

% if these base shapes won't do, you'll have to create your own definition, either of a whole shape or take an existing one and add extra anchors, as above.
% you need to make sure that the anchor border works correctly for lines approaching from the 4 compass points, as these are where the quantum wires attach.
% classical wires instead attach to points that are displaced by a horizontal/vertical amount \pgfkeysvalueof{/tikz/commutative diagrams/classical gap} relative to these positions. These are called:
% dstartone,dstarttwo,dendone,dendtwo
% ustartone,ustarttwo,uendone,uendtwo
% lstartone,lstarttwo,lendone,lendtwo
% rstartone,rstarttwo,rendone,rendtwo
%The idea, for example, is if you have an "l" type classical wire, there will be two wires, one going from lstartone (the left-hand edge on your shape, \pgfkeysvalueof{/tikz/commutative diagrams/classical gap} vertically above the west anchor) and going to lendone (l end one) on the cell one to the left. Typically, you expect lendone and rstartone to be the same points. There is also a line from lstarttwo to lendtwo.

% often the shape you want can just be a modification of an existing shape. Critically, the border should be the same. Then we don't need to define a whole new shape, we can just do it with styles. Much easier!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% gate definitions
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%single qubit operations
%\tikzset{linecont/.style={line}}
\newcommand{\phantomgate}[1]{|[line,thickness, inner ysep=3pt]| \phantom{#1}}
\newcommand{\hphantomgate}[1]{|[line,minimum size=1.5em,thickness]| \hphantom{#1}}
\newcommand{\linethrough}{|[line,thickness, inner ysep=3pt]| }
\newcommand{\push}[1]{#1}
%\newcommand{\alias}[1]{|[alias=#1]|}

\tikzset{
circle phase/.style={fill,shape=circle,minimum size=0.12cm,draw},
rrectangle phase/.style={fill,shape=rectangle,rounded corners=1.5pt,minimum width=3pt,minimum height=2.5*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}+3pt,draw},
phase/.code={%
  \pgfkeys{/quantikz/gates/.cd,style=,label style=,#1}%
  \pgfkeysgetvalue{/quantikz/gates/style}{\style}
  \ifcsundef{wire@type@\the\pgfmatrixcurrentrow}{%type not defined globally. assume quantum.
    \edef\wiretype{q}
  }{%
    \edef\wiretype{\csname wire@type@\the\pgfmatrixcurrentrow\endcsname}
  }
  \ifcsstring{wiretype}{b}{\ifdimless{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}{0.04cm}{\tikzset{circle phase}}{\tikzset{rrectangle phase}}}{%
    \ifcsstring{wiretype}{c}{\ifdimless{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}{0.04cm}{\tikzset{circle phase}}{\tikzset{rrectangle phase}}}{\tikzset{circle phase}}
  }
  \expandafter\tikzset\expandafter{\style}
  \pgfkeys{/quantikz/gates/.cd,style=,label style=,#1}%run again so that "open" can take priority
  },
%ophase/.style={fill=\pgfkeysvalueof{/tikz/commutative diagrams/background color},draw,shape=circle,minimum size=3*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}
phase label/.code={\tikzset{label distance=2mm,anchor=mid,label position=45}
  \pgfkeys{/quantikz/gates/.cd,style=,label style=,#1}%
  \pgfkeysgetvalue{/quantikz/gates/style}{\tstyle}
  \pgfkeysgetvalue{/quantikz/gates/label style}{\lstyle}
  \edef\style{\tstyle,\lstyle}
  \expandafter\tikzset\expandafter{\style}
},
}

\DeclareExpandableDocumentCommand{\phase}{O{}m}{|[phase={#1},label={[phase label={#1}]#2}]| {}}
\DeclareExpandableDocumentCommand{\control}{O{}m}{|[phase={#1}]| {}}
\DeclareExpandableDocumentCommand{\ocontrol}{O{}m}{|[phase={#1,open}]| {}}
\DeclareExpandableDocumentCommand{\targ}{O{}m}{|[circlewc={#1}]| {}}
\DeclareExpandableDocumentCommand{\targX}{O{}m}{|[crossx2={#1}]| {}}

\tikzset{
	cross/.style={path picture={ 
		\draw[internal](path picture bounding box.north) -- (path picture bounding box.south) (path picture bounding box.west) -- (path picture bounding box.east);
	}},
  circlewc/.code={
  \tikzset{draw,circle,cross,minimum width=4pt,inner sep=3pt}
    \pgfkeys{/quantikz/gates/.cd,style=,#1}%
    \pgfkeysgetvalue{/quantikz/gates/style}{\style}
    \expandafter\tikzset\expandafter{\style}
  },
  crossx/.style={path picture={ 
		\draw[internal,inner sep=0pt]
		(path picture bounding box.south east) -- (path picture bounding box.north west) (path picture bounding box.south west) -- (path picture bounding box.north east); %(path picture bounding box.west) -- (path picture bounding box.east);
	}},
  crossdraw/.pic = {
    \begin{pgfinterruptboundingbox}
      \node[cross out,draw,minimum size=0.7em,#1] {};
    \end{pgfinterruptboundingbox}
  },
  crossx2/.code={
    \pgfkeys{/quantikz/gates/.cd,style=,#1}%
    \pgfkeysgetvalue{/quantikz/gates/style}{\style}
    \edef\styling{crossx3=\style}
    \expandafter\tikzset\expandafter{\styling}
  },
  crossx3/.style={
    append after command={
      (\tikzlastnode.center) pic{crossdraw={#1}}
    }
  }
}

%%%
%
%measuring
%
%%%

%standard meter device
%first, define the styles
\tikzset{
  meter/.style={draw,
    %fill=\pgfkeysvalueof{/tikz/commutative diagrams/background color},
    filling,
    minimum width=2em,
    minimum height=1.5em,
    rectangle, 
    font=\vphantom{A}, 
    thickness,
    path picture={
        \draw ([shift={(.1,-.06)}]path picture bounding box.west) to[bend left=50] ([shift={(-.1,-.06)}]path picture bounding box.east);
        \draw[-{Latex[scale=0.6]}] ([shift={(0,-.1)}]path picture bounding box.center) -- ([shift={(-.1,.2)}]path picture bounding box.east);
    },
    },
    my label/.style={yshift=0.1cm,above,align=center},
}
%\DeclareExpandableDocumentCommand{\meter}{O{}{m}}{|[meter,label={[my label]#2},#1]| {}}
% \DeclareExpandableDocumentCommand{\meter}{O{}O{1.5pt}O{1.5pt}m}{%
% \gate[priority label={above},priority style={meter},#1][#2][#3]{#4}
% }
\DeclareExpandableDocumentCommand{\meter}{O{}O{2em}O{1.5em}m}{%
\gate[#1,priority label=above,ps=meter,disable auto height][#2][#3]{#4}
}
%code not working here :( Either I can get my predefined label style to apply, or the user's custom style. Not both.

%gate variant with classical result wire
\tikzset{
    metercw/.style={draw=none,
    yshift=0.375em,
        fill=none,
        minimum width=2em,
        minimum height=2.25em,
        font=\vphantom{A}, 
        thickness,
        path picture={
        %if you draw the rectangle to be the full width of the box, you cut off half the line, so have to bring it in a little.
        \node[draw,thickness,filling,#1,inner sep=0pt, minimum height=0pt,minimum width=0pt,fit={([shift={(.5\pgflinewidth,.5\pgflinewidth)}]path picture bounding box.south west) ([shift={(-.5\pgflinewidth,-0.75em)}]path picture bounding box.north east)}] (rect) {};
        %  \draw [#1]([xshift={0.5\pgflinewidth}]path picture bounding box.south west) rectangle ([yshift=-0.75em,xshift={-0.5\pgflinewidth}]path picture bounding box.north east);
          %draw the two classical wires
          \draw ([xshift=\pgfkeysvalueof{/tikz/commutative diagrams/classical gap},yshift=-0.75em]path picture bounding box.north) -- ([xshift=\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}]path picture bounding box.north);
          \draw ([xshift=-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap},yshift=-0.75em]path picture bounding box.north) -- ([xshift=-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}]path picture bounding box.north);
          %draw the image in the middle of the box
            \draw ([shift={(.1,-.06)}]rect.west) to[bend left=50] ([shift={(-.1,-.06)}]rect.east);
        \draw[-{Latex[scale=0.6]}] ([shift={(0,-.1)}]rect.center) -- ([shift={(-.1,.2)}]rect.east);
        }
    }
}
%\DeclareExpandableDocumentCommand{\metercw}{O{}{m}}{|[metercw={#1},label={[my labelcw]#2}]| {}}
\DeclareExpandableDocumentCommand{\metercw}{O{}O{2em}O{2.25em}m}{%
\gate[#1,priority label=above,ps=metercw,disable auto height][#2][#3]{#4}
}

\tikzset{measuretab/.style={draw,signal,signal to=west,filling,minimum width=2em, minimum height=1em,inner sep=4pt}}
\DeclareExpandableDocumentCommand{\measuretab}{O{}{m}}{|[measuretab,#1]| {#2}}
%considered making this a multiqubit gate, but any non-straight edge works badly with incoming wires and transparency.
%it might be that your use case is tolerable.
% \DeclareExpandableDocumentCommand{\measuretab}{O{}O{2em}O{1.5pt}m}{%
% \gate[#1,ps=measuretab][#2][#3]{#4}
% }

\tikzset{
  meterD/.style={
        draw,
        shape=rounded rectangle,
        rounded rectangle west arc=none,
        inner sep=4pt,
        filling
    },
  inputD/.style={
        draw,
        shape=rounded rectangle,
        rounded rectangle east arc=none,
        inner sep=4pt,
        filling
    }
}
%should these have a multi-qubit option?
\DeclareExpandableDocumentCommand{\meterD}{O{}{m}}{|[meterD,#1]| {#2}}
\DeclareExpandableDocumentCommand{\inputD}{O{}{m}}{|[inputD,#1]| {#2}\wireoverride{n}}
% \DeclareExpandableDocumentCommand{\meterD}{O{}O{1.5pt}O{1.5pt}m}{%
% \gate[#1,ps=meterD][#2][#3]{#4}
% }
\tikzset{measure/.style={draw=black,rounded rectangle,filling, minimum width=2em, minimum height=1em, inner sep=4pt}}

% \DeclareExpandableDocumentCommand{\measure}{O{}O{2em}O{1.5pt}m}{%
% \gate[#1,ps=measure][#2][#3]{#4}
% }

\DeclareExpandableDocumentCommand{\measure}{O{}{m}}{|[measure,#1]| {#2}}

\tikzset{trash/.style={path picture={
    \edef\yshift{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}
    \ifcsstring{wire@type@\the\pgfmatrixcurrentrow}{c}{%
      \draw[internal,inner sep=0pt,-stealth] ([yshift={\yshift}]path picture bounding box.west) -- ([yshift={\yshift}]path picture bounding box.center) -- (path picture bounding box.south);
      \draw[internal,inner sep=0pt] ([yshift={-\yshift}]path picture bounding box.west) -- ([yshift={-\yshift}]path picture bounding box.center);
    }{%
      \draw[internal,inner sep=0pt,-stealth] (path picture bounding box.west) -- (path picture bounding box.center) -- (path picture bounding box.south);
      \ifcsstring{wire@type@\the\pgfmatrixcurrentrow}{b}{%
        \draw[internal,inner sep=0pt] ([yshift={\yshift}]path picture bounding box.west) -- ([yshift={\yshift}]path picture bounding box.center) -- (path picture bounding box.center);
        \draw[internal,inner sep=0pt] ([yshift={-\yshift}]path picture bounding box.west) -- ([yshift={-\yshift}]path picture bounding box.center);
      }{}
    }
    %\edef\yshift{\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}
    },
    minimum height=2.5em,
    minimum width=2em}}

\DeclareExpandableDocumentCommand{\trash}{O{}{m}}{|[trash,label={below:#2},#1]| {}}

\tikzset{ground/.style={path picture={
    \draw[internal,inner sep=0pt]([xshift={0.5\pgflinewidth}]path picture bounding box.south west) -- ([xshift={0.5\pgflinewidth}]path picture bounding box.north west);
    \draw[internal,inner sep=0pt]([xshift={0.5\pgflinewidth+2*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}},yshift={\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}]path picture bounding box.south west) -- ([xshift={0.5\pgflinewidth+2*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}},yshift={-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}]path picture bounding box.north west);
    \draw[internal,inner sep=0pt]([xshift={0.5\pgflinewidth+4*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}},yshift={2*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}]path picture bounding box.south west) -- ([xshift={0.5\pgflinewidth+4*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}},yshift={-2*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}}]path picture bounding box.north west);
  },
  minimum height=8*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap},
  minimum width=5*\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}
  }}
\DeclareExpandableDocumentCommand{\ground}{O{}{m}}{|[ground,label={below:#2},#1]| {}}
%\DeclareExpandableDocumentCommand{\bin}{O{}{m}}{|[bin,label={below:#2},#1]| {}}

% \def\bin{\begin{tikzpicture}[thickness,scale=0.2]
%\draw (0,0) -- (1,0) -- (1,-0.2) -- (2,-0.8) -- (1.4,-3) -- (-0.4,-3) -- (-1,-0.8) -- (0,-0.2) -- cycle;
% \draw (2,-0.8) arc (360:180:1.5 and 0.2);
% \draw (-0.2,-1.1) -- (0.3,-2.8);
% \draw (1.2,-1.1) -- (0.7,-2.8);
% \end{tikzpicture}}

%%%
%
%controlled gates
%
%%%

\NewExpandableDocumentCommand{\ctrl}{O{}m}{\control[#1]{}%
  \pgfkeys{/quantikz/gates/.cd,style=,label style=,wire style=,vertical wire=q,#1}%
  \pgfkeysgetvalue{/quantikz/gates/style}{\tstyle}
  \pgfkeysgetvalue{/quantikz/gates/wire style}{\wstyle}
  \edef\style{\tstyle,\wstyle}
  \pgfkeysgetvalue{/quantikz/gates/vertical wire}{\wtype}
\ifnumcomp{#2}{>}{0}{%
   \expandafter\expandafter\expandafter\expandedwire\expandafter\expandafter\expandafter{\expandafter\style\expandafter}\expandafter{\wtype}{d}{#2}
% %  \wire[d][#2][\style]{\wtype}
}{}
\ifnumcomp{#2}{<}{0}{%
  \expandafter\expandafter\expandafter\expandedwire\expandafter\expandafter\expandafter{\expandafter\style\expandafter}\expandafter{\wtype}{u}{-#2}
%  \wire[u][-#3][#2]{#1}
}{}
}
\NewExpandableDocumentCommand{\octrl}{O{}m}{\ctrl[#1,open]{#2}}

\NewDocumentCommand\expandedwire{mmmm}{\wire[#3][#4][#1]{#2}}

\DeclareExpandableDocumentCommand{\swap}{O{}m}{%styling,label of partial swap, displacement of partial swap, distance
|[crossx2={#1}]| {}
\pgfkeys{/quantikz/gates/.cd,partial swap=,style=,partial position=0.5,label style=,vertical wire=q,#1}%
\pgfkeysgetvalue{/quantikz/gates/partial swap}{\partial}
\pgfkeysgetvalue{/quantikz/gates/vertical wire}{\wtype}
\pgfkeysgetvalue{/quantikz/gates/style}{\tstyle}
\ifdefempty{\partial}{%
  \edef\tempstyle{\tstyle}
%   \expandafter\vqw\expandafter[\opts]{#2}
  }{%
%   %\pgfkeysgetvalue{/quantikz/gates/label style}{\labstyle}
  \pgfkeysgetvalue{/quantikz/gates/partial position}{\pos}
  \pgfkeysgetvalue{/quantikz/gates/label style}{\lstyle}
  \ifdefstring{\wtype}{c}{%
\edef\tempstyle{"{\partial}"{grade,pos=\pos,\lstyle,xshift=-\pgfkeysvalueof{/tikz/commutative diagrams/classical gap}},\tstyle}
  }{%
  \edef\tempstyle{"{\partial}"{grade,pos=\pos,\lstyle},\tstyle}
  }
%   \expandafter\expandedwire\expandafter{\tempstyle}{q}{d}{#2}
%   %\wire[d][#3][\tempstyle]{q}
  }
 \expandafter\expandafter\expandafter\expandedwire\expandafter\expandafter\expandafter{\expandafter\tempstyle\expandafter}\expandafter{\wtype}{d}{#2}
}

%misc
\DeclareDocumentCommand{\makeebit}{O{}m}{
  \pgfkeys{/quantikz/gates/.cd,style=,label style=,angle=-45,#1}%
  \pgfkeysgetvalue{/quantikz/gates/angle}{\angle}
  \pgfkeysgetvalue{/quantikz/gates/style}{\style}
  \pgfkeysgetvalue{/quantikz/gates/label style}{\lstyle}
  \expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\make@ebit\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{\expandafter\expandafter\expandafter\style\expandafter\expandafter\expandafter}\expandafter\expandafter\expandafter{\expandafter\lstyle\expandafter}\expandafter{\angle}{#2}
	%\arrow[arrows,line cap=round,\style,to path={(\tikztostart) -- ($(\tikztostart)!{0.5/cos(\angle)}!\angle:(\tikztotarget)$) node [anchor=east,style={\lstyle}]{#2} -- (\tikztotarget) }]{d}
}
\DeclareDocumentCommand{\make@ebit}{mmmm}{%
  \arrow[arrows,line cap=round,#1,to path={(\tikztostart) --  ($(\tikztostart)!{0.5/cos(#3)}!#3:(\tikztotarget)$) node [anchor=east,style={#2}]{#4} --(\tikztotarget) }]{d}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% helpers
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newlength{\myl}
\newlength{\myh}
\newlength{\myd}

%\makeatletter
\newcounter{aaa}
\tikzset{
  apply/.style args={#1 except on segments #2}{postaction={
      /utils/exec={
        \@for\mattempa:=#2\do{\csdef{aaa@\mattempa}{}}
        \setcounter{aaa}{0}
      },
      decorate,decoration={show path construction,
        moveto code={},
        lineto code={
          \stepcounter{aaa}
          \ifcsdef{aaa@\theaaa}{}{
            \path[#1] (\tikzinputsegmentfirst) -- (\tikzinputsegmentlast);
          }
        },
        curveto code={
          \stepcounter{aaa}
          \ifcsdef{aaa@\theaaa}{}{
            \path [#1] (\tikzinputsegmentfirst) .. controls
            (\tikzinputsegmentsupporta) and (\tikzinputsegmentsupportb)
            ..(\tikzinputsegmentlast);
          }
        },
        closepath code={
          \stepcounter{aaa}
          \ifcsdef{aaa@\theaaa}{}{
            \path [#1] (\tikzinputsegmentfirst) -- (\tikzinputsegmentlast);
          }
        },
      },
    },
  },
}

%
%commands for putting in text vertically (e.g. for slices)
\protected\def\verticaltext#1{\leavevmode\bgroup\vbox\bgroup\xvvv#1\relax}
%
\def\xvvv{\afterassignment\xxvvv\let\tmp= }
%
\def\xxvvv{%
% \ifx\tmp\@sptoken\egroup\ \vbox\bgroup\let\next\xvvv
% \else
\ifx\tmp\relax\egroup\egroup\let\next\relax
 \else
\hbox to 1.1em{\hfill\tmp\hfill}% centred
\let\next\xvvv\fi%\fi
\next}
%end of commands for putting text vertically
%
\long\def\ifnodedefined#1#2#3{%
    \@ifundefined{pgf@sh@ns@#1}{#3}{#2}%
}

%find the vertical position of the middle of an equals sign
%https://tex.stackexchange.com/questions/355680/how-can-i-vertically-align-an-equals-sign-in-a-tikz-node/355686
\pgfmathsetmacro\MathAxis{height("$\vcenter{}$")}

\newcounter{wirenumberpermute}

\newcommand{\permute}[1]{%
\hphantom{Wide}%
\def\firstlist{#1}
 	\edef\n{\the\pgfmatrixcurrentrow} %the row
 	\edef\m{\the\pgfmatrixcurrentcolumn} %the column
 	\edef\mn{\the\numexpr\m-1\relax}
 	\edef\mp{\the\numexpr\m+1\relax}
 	\settowidth{\myl}{$Wide$}
 	\setcounter{wirenumberpermute}{0}
 	\foreach \x [count=\c] in \firstlist {%
 		\edef\start{\the\numexpr\c+\n-1\relax}%
 		\edef\endy{\the\numexpr\x+\n-1\relax}%
 		%apply auto width to the cell, and make sure we unset the setting so that it doesn't apply to later circuits.
    \csxdef{cell@width@\start-\m}{\the\myl} %save the cell width for every row in a global variable
 		\stepcounter{wirenumberpermute}
 	 	}
 	 	\expandafter\expandafter\expandafter\pgfutil@g@addto@macro\expandafter\expandafter\expandafter\tikzcd@atendsavedpaths\expandafter\expandafter\expandafter{%
 	 	\expandafter\expandafter\expandafter\wirepair@end\expandafter\expandafter\expandafter{\expandafter\n\expandafter}\expandafter{\m}{#1}%
 		}
 	\edef\lim{\the\numexpr\arabic{wirenumberpermute}+\n-1\relax}
 	 	\foreach \i in {\n,...,\lim} {%
 	     \edef\newcom{\noexpand\vqwexplicit{\i-\m}{\i-\mn}}
 	 		 \newcom%
 	 	}
}

\newcommand{\wirepair@end}[3]{%#row,col of left-most site. #row of right-most site.
	\xdef\LoopGG{}
	\edef\i{#1}
	\def\firstlist{#3}
	%\show\i
	%\show\j
	%create a list of cell names to be included in this grouped gate
	\foreach \n in \firstlist {%
	\ifnodedefined{\tikzcdmatrixname-\the\numexpr\n+\i-1\relax-#2}{%
		\xdef\LoopGG{\LoopGG(\tikzcdmatrixname-\the\numexpr\n+\i-1\relax-#2)}
		}{}
	}
	\ifnodedefined{\tikzcdmatrixname-\i-#2}{%
		\xdef\LoopGG{\LoopGG(\tikzcdmatrixname-\i-#2)}
		}{}
	\node (group\tikzcdmatrixname-#1-#2) [fit=\LoopGG,transparent,inner sep=0pt] {\phantom{Wide}};
		\foreach \n [count=\c] in \firstlist{%
			\draw [line width=3pt,\pgfkeysvalueof{/tikz/commutative diagrams/background color},shorten >=0.9pt,shorten <=0.9pt] (group\tikzcdmatrixname-#1-#2.west|-\tikzcdmatrixname-\the\numexpr\i+\c-1\relax-#2.center) to[out=0,in=180] (group\tikzcdmatrixname-#1-#2.east|-\tikzcdmatrixname-\the\numexpr\i+\n-1\relax-#2.center);
			\draw [thickness] (group\tikzcdmatrixname-#1-#2.west|-\tikzcdmatrixname-\the\numexpr\i+\c-1\relax-#2.center) to[out=0,in=180] (group\tikzcdmatrixname-#1-#2.east|-\tikzcdmatrixname-\the\numexpr\i+\n-1\relax-#2.center);
		}
}

%%%
%
%the main gate command
%
%%%

\DeclareExpandableDocumentCommand{\gate}{O{}O{1.5pt}O{1.5pt}m}{%optional parameter contains styling info. compulsory is gate text.
	|[inner sep=4pt,minimum width=#2,minimum height=#3]|%
 	\edef\n{\the\pgfmatrixcurrentrow} %the row
 	\edef\m{\the\pgfmatrixcurrentcolumn} %the column
 	%reset macros that are going to be set by the options
 	\edef\options{row=\n,col=\m,#1}
 	\def\toswap{0}%
 	\def\DisableMinSize{0}%
 	%\pgfkeys{/quantikz,wires=1,style=,label style=,braces=}%
 	%import options passed as parameters
  	\pgfkeys{/quantikz/gates/.cd,wires=1,style=,label style=,braces=,ps=,#1}%
 	\pgfkeysgetvalue{/quantikz/gates/wires}{\quantwires}%
  \ifnumless{\quantwires}{0}{%
    \PackageError{quantikz}{You cannot have a gate command with a negative number of wires. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
    }{%
      \ifnumequal{\quantwires}{0}{%
        \PackageError{quantikz}{You cannot have a gate command with 0 wires. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
      }{}
      }
  \pgfkeyssetevalue{/quantikz/gates/style}{\pgfkeysvalueof{/quantikz/gates/ps},\pgfkeysvalueof{/quantikz/gates/style}}
 	\pgfkeysgetvalue{/quantikz/gates/style}{\a}%
 	\pgfkeysgetvalue{/quantikz/gates/label style}{\b}%
 	\ifthenelse{\toswap=1}{%if it's a swap gate...
  \ifnumequal{\quantwires}{2}{%good!
  }{%
  \PackageWarning{quantikz}{You have asked for a swap gate in cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn. This required the number of wires that the gate acts on to be overridden. Check this is your intended behaviour}
 		\pgfkeys{/quantikz/gates/wires=2}
 		\def\quantwires{2}
    }
 		\phantom{wide}
 		\settowidth{\myl}{$wide$}
 		\settoheight{\myh}{$wide$}
 		\settodepth{\myd}{$wide$}
 	}{%not a swap gate
  %figure out how large the per-cell box should be
 		\settowidth{\myl}{$#4$}
 		\ifthenelse{\DisableMinSize=1}{%disable automatic size detection. Use $U$ instead.
 			\phantom{U}
 			\settoheight{\myh}{$U$}
 			\settodepth{\myd}{$U$}
 		}{%automatically get width and height of label
 			\phantom{#4}
 			\settoheight{\myh}{$#4$}
 			\settodepth{\myd}{$#4$}
 		}
 	}
%	communicate per-cell sizes to the other cells
 	\edef\k{\the\numexpr\n+\quantwires-1\relax}
% 	\edef\mn{\the\numexpr\m-1\relax}
  \ifnumgreater{\quantwires}{1}{%
 	\foreach \i in {\the\numexpr\n+1\relax,...,\k} {
    \csxdef{cell@width@\i-\m}{max(\the\myl+8pt,#2)} %save the cell width for every row in a global variable
 	}
  \csxdef{cell@height@\k-\m}{max(\the\myh+\the\myd+8pt,#3)} %apply auto height to last row only.
%		
 	}{}
 	%call deferred gate command. to be executed after the tikzcd matrix stuff is completed
	\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\pgfutil@g@addto@macro\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\tikzcd@atendsavedpaths\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{%
		\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\gate@end\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{\expandafter\expandafter\expandafter\a\expandafter\expandafter\expandafter}\expandafter\expandafter\expandafter{\expandafter\b\expandafter}\expandafter{\options}{#4}
	}
}

%deferred gate command. draws a box around all included cells. this is not part of the matrix, but comes afterwards.
\newcommand{\gate@end}[4]{
	\pgfkeys{/quantikz/gates/.cd,wires=1,priority label={center}}
	\def\toswap{0}
	\def\DisableMinSize{0}
 	\pgfkeys{/quantikz/gates/.cd,#3}%import options
	\pgfkeysgetvalue{/quantikz/gates/wires}{\quantwires}
	\pgfkeysgetvalue{/quantikz/gates/row}{\row}
	\pgfkeysgetvalue{/quantikz/gates/col}{\col}
  \pgfkeysgetvalue{/quantikz/gates/priority label}{\priority}
	\ifthenelse{\toswap=1}{\def\quantwires{2}}{}
	\xdef\LoopGG{}
	%create a list of cell names to be included in this grouped gate
	\foreach \n in  {\row,...,\the\numexpr\row+\quantwires-1\relax} {
	\ifnodedefined{\tikzcdmatrixname-\n-\col}{
		\xdef\LoopGG{\LoopGG(\tikzcdmatrixname-\n-\col)}
		}{}
	}
	\ifthenelse{\toswap=1}{%
		\node (group\tikzcdmatrixname-\row-\col) [fit=\LoopGG,operator,inner sep=0pt,#1] {\hphantom{Wide}};
		\draw [thickness] (group\tikzcdmatrixname-\row-\col.west|-\tikzcdmatrixname-\row-\col.center) to[out=0,in=180] (group\tikzcdmatrixname-\row-\col.east|-\tikzcdmatrixname-\the\numexpr\row+1\relax-\col.center);
		\draw [line width=3pt,\pgfkeysvalueof{/tikz/commutative diagrams/background color},shorten >=0.9pt,shorten <=0.9pt] (group\tikzcdmatrixname-\row-\col.east|-\tikzcdmatrixname-\row-\col.center) to[out=180,in=0] (group\tikzcdmatrixname-\row-\col.west|-\tikzcdmatrixname-\the\numexpr\row+1\relax-\col.center);
		\draw [thickness] (group\tikzcdmatrixname-\row-\col.east|-\tikzcdmatrixname-\row-\col.center) to[out=180,in=0] (group\tikzcdmatrixname-\row-\col.west|-\tikzcdmatrixname-\the\numexpr\row+1\relax-\col.center);
	}{%
	%the actual gate drawing command
	  \node (group\tikzcdmatrixname-\row-\col) [fit=\LoopGG,operator,inner sep=0pt,label={[gg label,#2]\priority:$#4$},#1] {\hphantom{$#4$}};
	}
}

%ghost will get height correct if can't be automatically assigned.
\DeclareExpandableDocumentCommand{\ghost}{O{}O{0pt}O{1.5pt}m}{%optional parameter contains styling info. compulsory is gate text.
	|[inner ysep=4pt,minimum width=#2,minimum height=#3]| \vphantom{#4}
}

%%%
%
%slicing
%
%%%

%single slice
\newcommand\slice[2][]{%
	%\edef\currcol{\the\pgfmatrixcurrentcolumn}
	\pgfkeys{/quantikz/gates/.cd,wires=1,style=,label style=,braces=}
	\pgfkeys{/quantikz/gates/.cd,#1}%
 	\edef\options{\pgfkeysvalueof{/quantikz/gates/style}}
 	\edef\opts{\pgfkeysvalueof{/quantikz/gates/label style}}
	\edef\n{\the\pgfmatrixcurrentcolumn}
	%\expandafter\show\n
	\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\pgfutil@g@addto@macro\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\tikzcd@atendslices\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{%
		\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\slice@end\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{\expandafter\expandafter\expandafter\n\expandafter\expandafter\expandafter}\expandafter\expandafter\expandafter{\expandafter\options\expandafter}\expandafter{\opts}{#2}%
	}}
%deferred slice command
\newcommand{\slice@end}[4]{
	\edef\top{($1/2*(\tikzcdmatrixname-col#1.east |- \tikzcdmatrixname-row1.north)+1/2*(\tikzcdmatrixname-col\the\numexpr#1+1\relax.west |- \tikzcdmatrixname-row1.north)$)}
	\edef\bottom{($1/2*(\tikzcdmatrixname-col#1.east |- \tikzcdmatrixname-row\the\pgfmatrixcurrentrow.south)+1/2*(\tikzcdmatrixname-col\the\numexpr#1+1\relax.west |- \tikzcdmatrixname-row\the\pgfmatrixcurrentrow.south)+(0,-3pt)$)}
	\expandafter\expandafter\expandafter\make@slice\expandafter\expandafter\expandafter{\expandafter\top\expandafter}\expandafter{\bottom}{#4}{#2}{#3}
}
\newcommand{\make@slice}[5]{
	\draw[slice,#4] #1 to node[pos=0,inner sep=4pt,anchor=south,color=black,#5] {#3} #2;
}
%deferred command which will slice everything
\newcommand{\sliceallr}{
	\edef\sstyle{\pgfkeysvalueof{/tikz/commutative diagrams/slice style}}
	\edef\slstyle{\pgfkeysvalueof{/tikz/commutative diagrams/slice label style}}
	\foreach \n in  {2,...,\the\numexpr\pgfmatrixcurrentcolumn-1-\pgfkeysvalueof{/tikz/commutative diagrams/remove end slices}\relax} {
		\edef\col{\the\numexpr\n-1\relax}
		\edef\title{\pgfkeysvalueof{/tikz/commutative diagrams/slice titles}}
		\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\slice@end\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{\expandafter\expandafter\expandafter\n\expandafter\expandafter\expandafter}\expandafter\expandafter\expandafter{\expandafter\sstyle\expandafter}\expandafter{\slstyle}{\title}
	}
}
%deferred slice command with vertical text
\newcommand{\sliceallvr}{
	\edef\sstyle{\pgfkeysvalueof{/tikz/commutative diagrams/slice style}}
	\edef\slstyle{\pgfkeysvalueof{/tikz/commutative diagrams/slice label style}}
	\foreach \n in  {2,...,\the\numexpr\pgfmatrixcurrentcolumn-1-\pgfkeysvalueof{/tikz/commutative diagrams/remove end slices}\relax} {
		\edef\col{\the\numexpr\n-1\relax}
		\edef\title{\verticaltext{\pgfkeysvalueof{/tikz/commutative diagrams/slice titles}}}
		\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\slice@end\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{\expandafter\expandafter\expandafter\n\expandafter\expandafter\expandafter}\expandafter\expandafter\expandafter{\expandafter\sstyle\expandafter}\expandafter{\slstyle}{\title}
	}
}

%labelling of inputs
\newcommand\lstick[2][]{%
	\pgfkeys{/quantikz/gates/.cd,wires=1,style=,label style=,braces=}
	\pgfkeys{/quantikz/gates/.cd,#1}%
	\edef\newoptions{row=\the\pgfmatrixcurrentrow,col=\the\pgfmatrixcurrentcolumn,#1}
	\pgfkeysgetvalue{/quantikz/gates/label style}{\options}
	\pgfkeysgetvalue{/quantikz/gates/braces}{\opts}
  \pgfkeysgetvalue{/quantikz/gates/wires}{\quantwires}
   \ifnumless{\quantwires}{0}{%
    \PackageError{quantikz}{You cannot have an lstick command with a negative number of wires. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
    }{%
      \ifnumequal{\quantwires}{0}{%
        \PackageError{quantikz}{You cannot have an lstick command with 0 wires. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
      }{}
      }
	%\edef\n{\the\pgfmatrixcurrentrow}
	%\edef\m{\the\pgfmatrixcurrentcolumn}
	\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\pgfutil@g@addto@macro\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\tikzcd@atendsavedpaths\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{%
		\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\groupinput@end\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{\expandafter\expandafter\expandafter\newoptions\expandafter\expandafter\expandafter}\expandafter\expandafter\expandafter{\expandafter\options\expandafter}\expandafter{\opts}{#2}%
	}
}
%labelling of outputs
\newcommand\rstick[2][]{%
	\pgfkeys{/quantikz/gates/.cd,wires=1,style=,label style=,braces=}
	\pgfkeys{/quantikz/gates/.cd,#1}%
	\edef\newoptions{row=\the\pgfmatrixcurrentrow,col=\the\pgfmatrixcurrentcolumn,#1}
	\pgfkeysgetvalue{/quantikz/gates/label style}{\options}
	\pgfkeysgetvalue{/quantikz/gates/braces}{\opts}
    \pgfkeysgetvalue{/quantikz/gates/wires}{\quantwires}
   \ifnumless{\quantwires}{0}{%
    \PackageError{quantikz}{You cannot have an rstick command with a negative number of wires. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
    }{%
      \ifnumequal{\quantwires}{0}{%
        \PackageError{quantikz}{You cannot have an rstick command with 0 wires. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
      }{}
      }
	%\edef\n{\the\pgfmatrixcurrentrow}
	%\edef\m{\the\pgfmatrixcurrentcolumn}
	\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\pgfutil@g@addto@macro\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\tikzcd@atendsavedpaths\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{%
		\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\groupoutput@end\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{\expandafter\expandafter\expandafter\newoptions\expandafter\expandafter\expandafter}\expandafter\expandafter\expandafter{\expandafter\options\expandafter}\expandafter{\opts}{#2}%
	}
}

\newcommand\midstick[2][]{%
	\hphantom{\text{g#2g}}\ %leave enough space for whatever text we've inserted
	\pgfkeys{/quantikz/gates/.cd,wires=1,style=,label style=,braces=}
	\pgfkeys{/quantikz/gates/.cd,#1}%
	\edef\newoptions{row=\the\pgfmatrixcurrentrow,col=\the\pgfmatrixcurrentcolumn,#1}
	\pgfkeysgetvalue{/quantikz/gates/wires}{\quantwires}
	\pgfkeysgetvalue{/quantikz/gates/label style}{\options}
	\pgfkeysgetvalue{/quantikz/gates/braces}{\opts}
   \ifnumless{\quantwires}{0}{%
    \PackageError{quantikz}{You cannot have a midstick command with a negative number of wires. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
    }{%
      \ifnumequal{\quantwires}{0}{%
        \PackageError{quantikz}{You cannot have a midstick command with 0 wires. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
      }{}
      }
	 \edef\n{\the\pgfmatrixcurrentrow} %the row
 	\edef\m{\the\pgfmatrixcurrentcolumn} %the column
	\edef\k{\the\numexpr\n+\quantwires-1\relax}
	\settowidth{\myl}{g#2g}
	%if more than 1 wire, need to reserve space for each wire
	\ifthenelse{\quantwires=1}{}{
	 	\foreach \i in {\the\numexpr\n+1\relax,...,\k} {
 		%apply auto width to the cell, and make sure we unset the setting so that it doesn't apply to later circuits.
    \csxdef{cell@width@\i-\m}{\the\myl} %save the cell width for every row in a global variable
 	}
%		
 	}
	%\edef\n{\the\pgfmatrixcurrentrow}
	%\edef\m{\the\pgfmatrixcurrentcolumn}
	\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\pgfutil@g@addto@macro\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\tikzcd@atendsavedpaths\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{%
		\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\groupoutput@mid\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{\expandafter\expandafter\expandafter\newoptions\expandafter\expandafter\expandafter}\expandafter\expandafter\expandafter{\expandafter\options\expandafter}\expandafter{\opts}{#2}%
	}
}
%deferred labelling of inputs
\newcommand{\groupinput@end}[4]{%basic data as keys, lable options, brace options, text
	\pgfkeys{/quantikz/gates/.cd,wires=1}
	\def\rightbrace{1}
 	\pgfkeys{/quantikz/gates/.cd,#1}%
	\pgfkeysgetvalue{/quantikz/gates/wires}{\quantwires}
	\pgfkeysgetvalue{/quantikz/gates/row}{\row}
	\pgfkeysgetvalue{/quantikz/gates/col}{\col}
	\xdef\LoopGI{}
	\foreach \n in  {\row,...,\the\numexpr\row+\quantwires-1\relax} {
	\ifnodedefined{\tikzcdmatrixname-\n-\col}{
		\xdef\LoopGI{\LoopGI(\tikzcdmatrixname-\n-\col)} 
		}{}
		}
	\ifthenelse{\quantwires=1} {
		\node (ingr-\row) [fit=\LoopGI, inner sep=0pt,label={[align=center,#2]left:#4}] {};
	}{
	\node (ingr-\row) [fit=\LoopGI, inner sep=0pt,label={[align=center,anchor=east,xshift=-0.2cm,#2]left:#4}] {};
	\ifthenelse{\rightbrace=1}{
	\draw[dm,#3] ($(ingr-\row.north west)+(-0.1cm,0.1cm)$) to ($(ingr-\row.south west)+(-0.1cm,-0.1cm)$);
	}{}
	}
} %
%deferred labelling of outputs
\newcommand{\groupoutput@end}[4]{%basic data as keys, label options, brace options, text
	\pgfkeys{/quantikz/gates/.cd,wires=1}
	\def\leftbrace{1}
 	\pgfkeys{/quantikz/gates/.cd,#1}%
	\pgfkeysgetvalue{/quantikz/gates/wires}{\quantwires}
	\pgfkeysgetvalue{/quantikz/gates/row}{\row}
	\pgfkeysgetvalue{/quantikz/gates/col}{\col}
	\xdef\LoopGO{}
	\foreach \n in  {\row,...,\the\numexpr\row+\quantwires-1\relax} {
		\ifnodedefined{\tikzcdmatrixname-\n-\col}{
			\xdef\LoopGO{\LoopGO(\tikzcdmatrixname-\n-\col)} 
		}}
		\ifthenelse{\quantwires=1} {
		\node (outgr-\row) [fit=\LoopGO, inner sep=0pt,label={[align=center,#2]right:#4}] {};
	}{
	\node (outgr-\row) [fit=\LoopGO, inner sep=0pt,label={[align=center,anchor=west,xshift=0.2cm,#2]left:#4}] {};
	\ifthenelse{\leftbrace=1}{
	\draw[dd,#3] ($(outgr-\row.north east)+(0.1cm,0.1cm)$) to ($(outgr-\row.south east)+(0.1cm,-0.1cm)$);
	}{}
	}
} %
%deferred labelling in the middle of circuits
\newcommand{\groupoutput@mid}[4]{%basic data as keys, label options, brace options, text
	\pgfkeys{/quantikz/gates/.cd,wires=1}
	\def\leftbrace{1}\def\rightbrace{1}
 	\pgfkeys{/quantikz/gates/.cd,#1}%
	\pgfkeysgetvalue{/quantikz/gates/wires}{\quantwires}
	\pgfkeysgetvalue{/quantikz/gates/row}{\row}
	\pgfkeysgetvalue{/quantikz/gates/col}{\col}
	\xdef\LoopGO{}
	\foreach \n in  {\row,...,\the\numexpr\row+\quantwires-1\relax} {
		\ifnodedefined{\tikzcdmatrixname-\n-\col}{
			\xdef\LoopGO{\LoopGO(\tikzcdmatrixname-\n-\col)} 
		}}
		\ifthenelse{\quantwires=1} {
		%\node (midgr-\row-\col) [fit=\LoopGO, inner sep=0pt,label={[align=center,#2]#4}] {};
		\node (midgr-\row-\col) [fit=\LoopGO, inner sep=0pt,label={[align=center,anchor=mid,#2]center:#4}] {};
	}{
	\node (midgr-\row-\col) [fit=\LoopGO, inner sep=0pt,label={[align=center,anchor=mid,#2]center:#4}] {};
	\ifthenelse{\rightbrace=1}{
	\draw[dm,#3] ($(midgr-\row-\col.north east)+(-0.1cm,0.05cm)$) to ($(midgr-\row-\col.south east)+(-0.1cm,-0.05cm)$);
	}{}
	\ifthenelse{\leftbrace=1}{
	\draw[dd,#3] ($(midgr-\row-\col.north west)+(0.1cm,0.05cm)$) to ($(midgr-\row-\col.south west)+(0.1cm,-0.05cm)$);
	}{}
	}
} %
%inputs and outputs within a multi-wire gate
\newcommand\gateinput[2][]{%
	\pgfkeys{/quantikz/gates/.cd,wires=1,style=,label style=,braces=}%
	\pgfkeys{/quantikz/gates/.cd,#1}%
	\edef\newoptions{row=\the\pgfmatrixcurrentrow,col=\the\pgfmatrixcurrentcolumn,#1}
 	\pgfkeysgetvalue{/quantikz/gates/label style}{\options}
 	\pgfkeysgetvalue{/quantikz/gates/braces}{\opts}%
    \pgfkeysgetvalue{/quantikz/gates/wires}{\quantwires}
   \ifnumless{\quantwires}{0}{%
    \PackageError{quantikz}{You cannot have a gate input command with a negative number of wires. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
    }{%
      \ifnumequal{\quantwires}{0}{%
        \PackageError{quantikz}{You cannot have a gate input command with 0 wires. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
      }{}
      }
	\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\pgfutil@g@addto@macro\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\tikzcd@atendlabels\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{%
		\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\mginput@end\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{\expandafter\expandafter\expandafter\newoptions\expandafter\expandafter\expandafter}\expandafter\expandafter\expandafter{\expandafter\options\expandafter}\expandafter{\opts}{#2}%
	}
}
\newcommand\gateoutput[2][]{%
	\pgfkeys{/quantikz/gates/.cd,wires=1,style=,label style=,braces=}
	\pgfkeys{/quantikz/gates/.cd,#1}%
	\edef\newoptions{row=\the\pgfmatrixcurrentrow,col=\the\pgfmatrixcurrentcolumn,#1}
 	\pgfkeysgetvalue{/quantikz/gates/label style}{\options}
 	\pgfkeysgetvalue{/quantikz/gates/braces}{\opts}
    \pgfkeysgetvalue{/quantikz/gates/wires}{\quantwires}
   \ifnumless{\quantwires}{0}{%
    \PackageError{quantikz}{You cannot have a gate output command with a negative number of wires. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
    }{%
      \ifnumequal{\quantwires}{0}{%
        \PackageError{quantikz}{You cannot have a gate output command with 0 wires. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
      }{}
      }
	\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\pgfutil@g@addto@macro\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\tikzcd@atendlabels\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{%
		\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\mgoutput@end\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{\expandafter\expandafter\expandafter\newoptions\expandafter\expandafter\expandafter}\expandafter\expandafter\expandafter{\expandafter\options\expandafter}\expandafter{\opts}{#2}%
	}
}
%deferred functions for the above
\newcommand{\mginput@end}[4]{%collected options,label style, brace style,text
	\pgfkeys{/quantikz/gates/.cd,wires=1}
 	\pgfkeys{/quantikz/gates/.cd,#1}%
 	\edef\quantwires{\pgfkeysvalueof{/quantikz/gates/wires}}
	%\pgfkeysgetvalue{/quantikz/wires}{\quantwires}
	\pgfkeysgetvalue{/quantikz/gates/row}{\row}
	\pgfkeysgetvalue{/quantikz/gates/col}{\col}
%can we find the gategroup node?
\xdef\cell{group\tikzcdmatrixname-1-\col}
\foreach \n in {\row,...,1} {%
	%test if node group-\n-#2 exists
	\ifnodedefined{group\tikzcdmatrixname-\n-\col}{%
    	\xdef\cell{group\tikzcdmatrixname-\n-\col}
    	\breakforeach
	}{}
}
\ifthenelse{\quantwires=1}{%
	\node at ($(\cell.west |- \tikzcdmatrixname-\row-\col.west)+(0,0cm)$)[leftinternal,#2]{#4};
}{%
%\show\quantwires
\draw[dd,#3] ($(\cell.west |- \tikzcdmatrixname-\row-\col.west)+(0.1cm,0.1cm)$) to node[leftinternal,midway,#2] {#4} ($(\cell.west |- \tikzcdmatrixname-\the\numexpr\row+\quantwires-1\relax-\col.west)+(0.1cm,-0.1cm)$);
}
} %
\newcommand{\mgoutput@end}[4]{%
	\pgfkeys{/quantikz/gates/.cd,wires=1}
 	\pgfkeys{/quantikz/gates/.cd,#1}%
 	\edef\quantwires{\pgfkeysvalueof{/quantikz/gates/wires}}
	%\pgfkeysgetvalue{/quantikz/wires}{\quantwires}
	\pgfkeysgetvalue{/quantikz/gates/row}{\row}
	\pgfkeysgetvalue{/quantikz/gates/col}{\col}
%can we find the gategroup node?
\xdef\cell{group\tikzcdmatrixname-1-\col}
\foreach \n in {\row,...,1} {%
	%test if node group-\n-#2 exists
	\ifnodedefined{group\tikzcdmatrixname-\n-\col}{%
    	\xdef\cell{group\tikzcdmatrixname-\n-\col}
    	\breakforeach
	}{}
}
\ifthenelse{\quantwires=1}{%
	\node at ($(\cell.east |- \tikzcdmatrixname-\row-\col.east)+(0,0cm)$)[rightinternal,#2]{#4};
}{%
\draw[dm,#3] ($(\cell.east |- \tikzcdmatrixname-\row-\col.east)+(-0.1cm,0.1cm)$) to node[rightinternal,midway,#2] {#4} ($(\cell.east |- \tikzcdmatrixname-\the\numexpr\row+\quantwires-1\relax-\col.east)+(-0.1cm,-0.1cm)$);
}
} %

%wave command
\newcommand\wave[1][]{%
\setwiretype{n}
	\edef\n{\the\pgfmatrixcurrentrow}
	\expandafter\pgfutil@g@addto@macro\expandafter\tikzcd@atendslices\expandafter{%
		\expandafter\wave@end\expandafter{\n}{#1}%
	}
}
%deferred wave
\newcommand{\wave@end}[2]{
	\node (wave-#1) [fit=(\tikzcdmatrixname-row#1),wave,#2] {};
}

%put a border around a group of gates
\newcommand\gategroup[2][]{%
	\pgfkeys{/quantikz/gates/.cd,wires=1,style=,label style=,braces=,steps=1}
	\pgfkeys{/quantikz/gates/.cd,#1}%
	\edef\newoptions{row=\the\pgfmatrixcurrentrow,col=\the\pgfmatrixcurrentcolumn,#1}
 	\pgfkeysgetvalue{/quantikz/gates/style}{\options}
 	\pgfkeysgetvalue{/quantikz/gates/label style}{\opts}
    \pgfkeysgetvalue{/quantikz/gates/wires}{\quantwires}
   \ifnumless{\quantwires}{0}{%
    \PackageError{quantikz}{You cannot have a gate group command with a negative number of wires. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
    }{%
      \ifnumequal{\quantwires}{0}{%
        \PackageError{quantikz}{You cannot have a gate group command with 0 wires. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
      }{}
      }
    \pgfkeysgetvalue{/quantikz/gates/steps}{\steps}
   \ifnumless{\steps}{0}{%
    \PackageError{quantikz}{You cannot have a gate group command with a negative number of steps. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
    }{%
      \ifnumequal{\steps}{0}{%
        \PackageError{quantikz}{You cannot have a gate group command with 0 steps. The culprit appears to be cell \the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
      }{}
      }
	\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\pgfutil@g@addto@macro\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\tikzcd@atendlabels\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{%
		\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\gategroup@end\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter\expandafter{\expandafter\expandafter\expandafter\newoptions\expandafter\expandafter\expandafter}\expandafter\expandafter\expandafter{\expandafter\options\expandafter}\expandafter{\opts}{#2}%
	}
}
%deferred gate group command
\newcommand{\gategroup@end}[4]{%options, gate style, text style, text
	\pgfkeys{/quantikz/gates/.cd,wires=1,style=,label style=,braces=,steps=1}%
	\edef\background{0}%
	\pgfkeys{/quantikz/gates/.cd,#1}%
	\pgfkeysgetvalue{/quantikz/gates/wires}{\quantwires}%
	\pgfkeysgetvalue{/quantikz/gates/row}{\row}%
	\pgfkeysgetvalue{/quantikz/gates/col}{\col}%
	\pgfkeysgetvalue{/quantikz/gates/steps}{\steps}%
	\edef\fit{(\tikzcdmatrixname-col\col.west |- \tikzcdmatrixname-row\row.north)(\tikzcdmatrixname-col\the\numexpr\col+\steps-1\relax.east |- \tikzcdmatrixname-row\the\numexpr\row+\quantwires-1\relax.south)}%
	\ifthenelse{\background=1}{%
		\begin{pgfonlayer}{background}\node (ggroup-\row-\col) [fit=\fit,ggroup,label={[group label,#3]:#4},#2] {};\end{pgfonlayer}
	}{%
		\node (ggroup-\row-\col) [fit=\fit,ggroup,label={[group label,#3]:#4},#2] {};
	}
}

% \newcommand{\latephase@end}[1]{
% 	\node [phase,inner sep=2pt] at (\tikzcdmatrixname-#1) {};
% }

%\makeatother

%this command runs after we've finished the matrix, and makes unified cells for each row and each column. This allows much nicer alignment of large boxes.
\newcommand{\DivideRowsCols}{
	\foreach \n in {1,...,\the\pgfmatrixcurrentrow} {%for each row, construct a master cell that contains all entries
	\xdef\LoopRow{}
		\foreach \m in {1,...,\the\pgfmatrixcurrentcolumn}{
			\ifnodedefined{\tikzcdmatrixname-\n-\m}{
				\xdef\LoopRow{\LoopRow(\tikzcdmatrixname-\n-\m)}
			}{}
			\ifnodedefined{group\tikzcdmatrixname-\n-\m}{
				\xdef\LoopRow{\LoopRow(group\tikzcdmatrixname-\n-\m)}
			}{}
	}
	\node (\tikzcdmatrixname-row\n) [fit=\LoopRow] {};
	}
	\foreach \n in {1,...,\the\pgfmatrixcurrentcolumn} {%for each column, construct a master cell that contains all entries
	\xdef\LoopCol{}
		\foreach \m in {1,...,\the\pgfmatrixcurrentrow}{
			\ifnodedefined{\tikzcdmatrixname-\m-\n}{
				\xdef\LoopCol{\LoopCol(\tikzcdmatrixname-\m-\n)}
			}{}
			\ifnodedefined{group\tikzcdmatrixname-\m-\n}{
				\xdef\LoopCol{\LoopCol(group\tikzcdmatrixname-\m-\n)}
			}{}
	}
	\node (\tikzcdmatrixname-col\n) [fit=\LoopCol] {};
	}
}

%this is the command that implements the align equals at key.
%take a parameter, row number, where we want to set the baseline. if not integer, use the two rows spanned
\providecommand{\setmiddle}[1]{%
\IfInteger{#1}{
\pgfmathtruncatemacro\wholepart{floor(#1)}
\edef\temp{\noexpand\tikzset{%
/tikz/baseline={([yshift=-\MathAxis]\noexpand\tikzcdmatrixname-\wholepart-1.center)}
}}
%\show\temp
\temp
}{%
\pgfmathtruncatemacro\wholepart{floor(#1)}
\pgfmathtruncatemacro\neighbour{floor(#1)+1}
\pgfmathsetmacro\fractionalpart{#1-floor(#1)}
\edef\temp{
%\noexpand\tikzset{every matrix/.append style={baseline=([yshift=-\MathAxis]$(\noexpand\tikzcdmatrixname-\wholepart-1.base)!\fractionalpart!(\noexpand\tikzcdmatrixname-\neighbour-1.base)$)}%
\noexpand\tikzset{%
/tikz/baseline={([yshift=-\MathAxis]$(\noexpand\tikzcdmatrixname-\wholepart-1.center)!\fractionalpart!(\noexpand\tikzcdmatrixname-\neighbour-1.center)$)}
}}
%\show\temp
\temp
}
}

% \providecommand{\setmiddle}[1]{%
% \IfInteger{#1}{
% \pgfmathtruncatemacro\wholepart{floor(#1)}
% \edef\temp{\noexpand\tikzset{%
% /tikz/baseline={(\noexpand\tikzcdmatrixname-\wholepart-1.base)}
% }}
% %\show\temp
% \temp
% }{%
% \pgfmathtruncatemacro\wholepart{floor(#1)}
% \pgfmathtruncatemacro\neighbour{floor(#1)+1}
% \pgfmathsetmacro\fractionalpart{#1-floor(#1)}
% \edef\temp{
% %\noexpand\tikzset{every matrix/.append style={baseline=([yshift=-\MathAxis]$(\noexpand\tikzcdmatrixname-\wholepart-1.base)!\fractionalpart!(\noexpand\tikzcdmatrixname-\neighbour-1.base)$)}%
% \noexpand\tikzset{%
% /tikz/baseline={($(\noexpand\tikzcdmatrixname-\wholepart-1.base)!\fractionalpart!(\noexpand\tikzcdmatrixname-\neighbour-1.base)$)}
% }}
% %\show\temp
% \temp
% }
% }

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Option parameter processing via key/value pairs
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

%initialise all the pgfkeys for key=value parameter passing in macro options
\tikzcdset{%
	slice all/.code={\gdef\toslice{1}},
	remove end slices/.initial=0,
	slice titles/.initial={\col},
	slice style/.initial={},
	slice label style/.initial={},
	thin lines/.code={\resetstyles},
	transparent/.code={\maketransparent},
	vertical slice labels/.code={\def\vert{1}},
	align equals at/.code={\setmiddle{#1}},
  wire types/.code={\importwiretypes{#1}},
  classical gap/.initial=0.03cm, % define separation of classical wires (can override)
 % wire style/.code={\gdef\quantikzopts{#1}},
}
\pgfkeys{/quantikz/gates/.cd,%
	.unknown/.style={%
		/quantikz/gates/wires=\pgfkeyscurrentname
	},%
	%wires/.store in=\quantwires,%
	wires/.initial=1,%
	style/.initial={},
	label style/.initial={},
	braces/.initial={},
	background/.code={\def\background{1}},
	%alternate/.default=1,
	%alternate/.code={\def\helper{#1}},
  alternate/.code={\PackageWarning{quantikz}{Use of alternate is deprecated.}},
	row/.initial=1,
	col/.initial=1,
	steps/.initial=1,
	Strike Width/.initial=0.08cm,
	Strike Height/.initial=0.12cm,
	swap/.code={\def\toswap{1}},
	disable auto height/.code={\def\DisableMinSize{1}},
  nwires/.code={\PackageWarning{quantikz}{Use of nwires is deprecated. Set wire types globally instead.}},
  cwires/.code={\PackageWarning{quantikz}{Use of cwires is deprecated. Set wire types globally instead.}},
	brackets/.is choice,
	brackets/.initial=both,
  priority label/.initial={},
  ps/.initial={},
  angle/.initial=-45,
  vertical wire/.initial=q,
  wire style/.initial={},
  open/.code={\tikzset{filling}},
  partial swap/.initial={},
  partial position/.initial={0.5},
}
\pgfkeys{/quantikz/gates/brackets/.cd,%define brackets options
	none/.code={\def\leftbrace{0}\def\rightbrace{0}},
	left/.code={\def\leftbrace{1}\def\rightbrace{0}},
	right/.code={\def\leftbrace{0}\def\rightbrace{1}},
	both/.code={\def\leftbrace{1}\def\rightbrace{1}}
}
% \pgfkeys{/quantikz/swap/.cd,%define options for swap gate
%   partial/.initial={},
%   position/.initial={0.5},
%   label style/.initial={}
% }

%my standard Dirac notation commands. can be overridden by user.
\providecommand{\ket}[1]{\ensuremath{\left|#1\right\rangle}}
\providecommand{\bra}[1]{\ensuremath{\left\langle#1\right |}}
\providecommand{\proj}[1]{\ensuremath{\ket{#1}\!\bra{#1}}}
\providecommand{\braket}[2]{\ensuremath{\left\langle#1\middle|#2\right\rangle}}
\newcommand{\forceredefine}{%
\renewcommand{\ket}[1]{\ensuremath{\left|##1\right\rangle}}
\renewcommand{\bra}[1]{\ensuremath{\left\langle##1\right |}}
\renewcommand{\proj}[1]{\ensuremath{\ket{##1}\!\bra{##1}}}
\renewcommand{\braket}[2]{\ensuremath{\left\langle##1\middle|##2\right\rangle}}
}

%\DeclareExpandableDocumentCommand{\ctrlbundle}{O{1}O{}m}{|[phase bundle,#2]| {} \vqw{#3}\qwbundle[alternate=#1]{}}

%wire commands with absolute positioning. Need updating.
\newcommand{\vqwexplicit}[2]{
	\arrow[from=#1,to=#2,arrows] {}
}
% \newcommand{\vqbundleexplicit}[2]{
% 	\arrow[from=#1,to=#2,arrows] {} \arrow[from=#1,to=#2,arrows,yshift=0.1cm] {}\arrow[from=#1,to=#2,arrows,yshift=-0.1cm] {}
% }
% %classical vertical wire, absolute positioning
% \newcommand{\vcwexplicit}[2]{
% 	\arrow[from=#1,to=#2,arrows,xshift=0.05cm] {}\arrow[from=#1,to=#2,arrows,xshift=-0.05cm] {}
% }
% %classical horizontal wire, absolute positioning
% \newcommand{\vcwhexplicit}[2]{
% 	\arrow[from=#1,to=#2,arrows,yshift=0.05cm] {}\arrow[from=#1,to=#2,arrows,yshift=-0.05cm] {}
% }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Style properties
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%configure some of the style properties.
%annoyingly, this first one will affect all tikzcd instances, not just quantum circuits. I should have only provided the quantikz environment as a modified version of tikzcd, and not allowed direct use of tikzcd. Probably too late now.
\tikzcdset{%
	row sep/normal=0.5cm,
	column sep/normal=0.5cm,
	thick,
	nodes in empty cells,
	every cell/.style={
        anchor=center,minimum size=0pt,inner sep=0pt,outer sep=0pt,thick,
        minimum height=\ifcsundef{cell@height@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}{0}{\csname cell@height@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn\endcsname},
        minimum width=\ifcsundef{cell@width@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}{0}{\csname cell@width@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn\endcsname},
        %append after command={\wire{a}}
        execute at end cell={\wire{a}%looks promising. does not work on empty cells.
        %be careful to unset "global" variables that really only apply to current diagram
        \csgundef{cell@width@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
      \csgundef{cell@height@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}
      \csgundef{wire@type@override@\the\pgfmatrixcurrentrow-\the\pgfmatrixcurrentcolumn}}
    },
  arrows/.style={dash,thick,line cap=round},
  %1-row diagram/.style={},
  1-row diagram/.style={/tikz/baseline={([yshift=-\MathAxis]\tikzcdmatrixname-1-1.center)}},%doesn't seem to be doing anything. Possibly activates too late?
  grade/.style={description,circle,draw,fill=white,inner sep=0pt, outer sep=0pt,font=\tiny}
}
\tikzset{
	thickness/.style={thick},
  filling/.style={fill=\pgfkeysvalueof{/tikz/commutative diagrams/background color}},
  operator/.style={draw,filling, inner sep=2pt,thickness,align=center},
  ggroup/.style={draw,minimum size=1.5em,thickness,align=center,inner sep=4pt},
  leftinternal/.style={anchor=mid west,font=\scriptsize,inner sep=4pt,align=center},
  rightinternal/.style={anchor=mid east,font=\scriptsize,inner sep=4pt,align=center},
  wave/.style={inner sep=-3pt,tape,filling,apply={draw=black} except on segments {5,6,1,2,9}},
  phase bundle/.style={fill,shape=rectangle,rounded corners=1.5pt,minimum width=4pt,minimum height=10pt},
  internal/.style={thickness},
 %  rectangle with rounded corners north west/.initial=0pt,
	% rectangle with rounded corners south west/.initial=0pt,
	% rectangle with rounded corners north east/.initial=8pt,
	% rectangle with rounded corners south east/.initial=8pt,
  line/.style={path picture={ 
		\draw[internal](path picture bounding box.west) -- (path picture bounding box.east);
	}},
	%hidden bend/.style={path picture={
%		\draw[internal,inner sep=0pt] (path picture bounding box.west) -- (path picture bounding box.center) -- (path picture bounding box.south);},
%		minimum height=1.5em,minimum width=1em},
  dd/.style={decoration={brace},decorate,thickness},
  dm/.style={decoration={brace,mirror},decorate,thickness},
  slice/.style={thickness,red,dash pattern=on 5pt off 3pt,align=center},
 	my labelcw/.style={yshift=0.04cm,above,align=center},
 	gg label/.style={label position=center,align=center},
 	group label/.style={label position=above,yshift=0.2cm,anchor=mid}
}

\def\resetstyles{
\tikzcdset{thin,every cell/.append style={thin},arrows/.append style={thin}
    }
\tikzset{
	thickness/.style={thin},
	%operator/.append style={thin},
	%internal/.append style={thin},
	%dd/.append style={thin},
	%dm/.append style={thin},
	%slice/.append style={thin},
	meter/.append style={thin},
	phase/.append style={minimum size=3pt},
%	ophase/.append style={minimum size=3pt},
	%circlewc/.append style={minimum size=3pt,inner sep=2pt}
}
}

\def\maketransparent{
\tikzset{
  filling/.append style={fill opacity=0,text opacity=1},
%	operator/.append style={fill opacity=0},
	% meter/.append style={fill opacity=0},
	% measuretab/.append style={fill opacity=0},
	% meterD/.append style={fill opacity=0},
	% measure/.append style={fill opacity=0},
	% wave/.append style={fill opacity=0},
%	ophase/.append style={fill opacity=0}
}
}

### 2023-06-05 paper/main.tex
example env

@@
 \usepackage{bigdelim}
+
+\usepackage{float}
+\usepackage{tcolorbox}
+\tcbuselibrary{theorems}
+
+\newtcbtheorem{tcbexample}{Example}{
+  colback=gray!15,
+  colbacktitle=gray!15,
+  coltitle=red!75!black,
+  fonttitle=\bfseries,
+  detach title,
+  before upper={\tcbtitle},
+  separator sign none,
+  description delimiters={(}{). }
+}{ex}
 
@@
 \label{sec:classic-sol}
-
 Assume that Alice and Bob decided to adopt a deterministic strategy.
 For that, they met before the beginning of the game, and prepared
-their answers for each possible row and column. For example, they
-might have agreed that, if given the first column, Bob shall fill it
+their answers for each possible row and column. In this scenario,
+what is the best strategy that they can come up with?
+
+\begin{tcbexample}{Classical, Deterministic Solution}{classic-sol}
+  Alice and Bob might have agreed that, if given the first column, Bob shall fill it
   with three \(-1\)'s. Then, whatever row Alice is given, she must fill
@@
   and column for which Alice and Bob lose, as illustrated in
-Figure~\ref{fig:classical} (b). It is not difficult to convince yourself that,
-no matter how Alice and Bob decide to fill in their entries, it is impossible
-for them to come up with predefined answers that always win. In fact,
-the best that they can do is to win with probability \(\nicefrac{8}{9}\).
+  Figure~\ref{fig:classical} (b).
 
   {\renewcommand{\arraystretch}{2}
-\begin{figure}
+    \begin{figure}[H]
       \centering
@@
         \[\begin{array}{|>{\quad\columncolor{gray!50}}c<{\quad}|*{2}{>{\quad}c<{\quad}|}}
-        \hhline{---}
+            \hhline{---}[
             -1 & -1 & +1 
@@
     \end{figure}}
+\end{tcbexample}
 
-What if Alice and Bob decide for a probabilistic strategy? That is,
-Alice and Bob each carry a coin. When assigned a row/column, they flip
-their coins and fill the entries of the row/column based on the
-outcomes of the coins. Can they do better? To randomly assign values
-to one row (equivalently, one column) is essentially the same as
-randomly selecting one of the \(2^{9}\) possible predefined
-\(3 \times 3\) grids (including those matrices that would lead to
-invalid answers). In other words, a probabilistic strategy for the
-Magic Square game is one in which Alice and Bob randomly select a
+Example~\ref{ex:classic-sol} illustrates one of the many deterministic
+strategies that Alice and Bob can adopt. It is not difficult to
+convince yourself that, no matter how they decide to fill in
+their entries, it is impossible for them to come up with predefined
+answers that always win. Any deterministic strategy is a pair of
+matrices, one for Alice and another for Bob. The only way that they could
+design a strategy that wins with certainty every round is to prepare two
+identical matrices satisfying the requirements for each row and for each
+column. That is, a single matrix for which the product of every row is
+\(+1\) and the product of every column is \(-1\). Such a matrix cannot
+possibly exist! It turns out that the best that they can do is to win
+with probability \(\nicefrac{8}{9}\).
+
+What if Alice and Bob decide for a probabilistic strategy? That is, Alice and
+Bob each carry a coin. When assigned a row/column, they flip their
+coins and fill the entries of the row/column based on the outcomes of
+the coins. Can they do better? To randomly assign values to one row
+(equivalently, one column) is essentially the same as randomly
+selecting one of the \(2^{9}\) possible predefined \(3 \times 3\)
+grids (including those matrices that would lead to invalid
+answers). In other words, a probabilistic strategy for the Magic
+Square game is one in which Alice and Bob randomly select a
 deterministic strategy. Hence, no matter how lucky Alice and Bob are,
 the probability of success of any strategy that they come up with is
-bounded by the winning probability of the best deterministic
-strategy, which is
-\(\nicefrac{8}{9}\). Theorem~\ref{thm:classical-success} formalizes
-this argument.
+bounded by the winning probability of the best deterministic strategy,
+which is \(\nicefrac{8}{9}\). Theorem~\ref{thm:classical-success}
+formalizes this argument.
 

### 2023-06-06 paper/main.tex
initial draft of quantum sol example

@@
 \newtcbtheorem{tcbexample}{Example}{
+  boxrule=0.15mm,
   colback=gray!15,
   colbacktitle=gray!15,
-  coltitle=red!75!black,
+  coltitle=red!50!black,
   fonttitle=\bfseries,
@@
         \[\begin{array}{|>{\quad\columncolor{gray!50}}c<{\quad}|*{2}{>{\quad}c<{\quad}|}}
-            \hhline{---}[
+            \hhline{---}
             -1 & -1 & +1 
@@
 
+\begin{tcbexample}{Quantum Solution}{quantum-sol}
+  Suppose that Charlie assigns the first row to Alice. To decide the
+  value of the first cell, she (based on the \(3 \times 3\) grid she
+  and Bob have prepared) measures the observable \(I \otimes Z\)
+  on her two qubits. The possible outcomes are
+  \begin{equation}
+    \label{eq:outcomes-1r}
+    \operatorname{Out}((I \otimes Z)_{A} \otimes (I \otimes I)_{B}) =
+    \begin{cases}
+      +1, \text{ proj. onto } \{\ket{i0jk} \mid i, j, k \in \{0, 1\}\}
+        \text{ with prob. } \frac{1}{2} \\
+      -1, \text{ proj. onto } \{\ket{i1jk} \mid i, j, k \in \{0, 1\}\}
+        \text{ with prob. } \frac{1}{2}, \\
+    \end{cases}
+  \end{equation}
+  where the subscript \(A1\) denotes the state after Alice's first
+  measurement. Suppose that Alice has observed \(+1\). Notice that
+  only two of the components of the \(+1\)-eigenspace are seen in the
+  initial state \(\ket{\psi}\): \(\ket{0000}\) and
+  \(\ket{1010}\). Therefore, \(\ket{\psi}\) collapses to
+  \begin{equation}
+    \ket{\psi}_{A1} =  \frac{1}{\sqrt{2}}(\ket{0000} + \ket{1010}).
+  \end{equation}
+  For the second cell, Alice measures the observable \(Z \otimes I\),
+  whose possible outcomes are
+    \begin{equation}
+    \label{eq:outcomes-1r}
+    \operatorname{Out}((Z \otimes I)_{A} \otimes (I \otimes I)_{B}) =
+    \begin{cases}
+      +1, \text{ proj. onto } \{\ket{0ijk} \mid i, j, k \in \{0, 1\}\}
+        \text{ with prob. } \frac{1}{2} \\
+      -1, \text{ proj. onto } \{\ket{1ijk} \mid i, j, k \in \{0, 1\}\}
+        \text{ with prob. } \frac{1}{2}. \\
+    \end{cases}
+  \end{equation}
+  Suppose, now, that Alice has observed the outcome \(-1\). Notice that
+  only one component of the \(-1\)-eigenspace is seen in the state
+  \(\ket{\psi}_{A1}\). Hence, the state collapses to
+  \begin{equation}
+    \ket{\psi}_{A2} =  \ket{1010}.
+  \end{equation}
+\end{tcbexample}
+
 \section{Quantum Unitaries (? research)}

### 2023-06-06 paper/main.tex
quantum sol example

@@
 observables at each cell are \(\pm 1\). Furthermore, the product of
-every row is \(+I\) and the product of every column is \(-I\). (The
-original observables did not have the negative \(X\) and \(Z\) in the
-last row, so these two properties are not mandatory~\cite{Mermin1990,
-  aravind:xxx}.  We have adapted the observables merely to be
-``consistent'' with the properties of the classical magic square, but
-what really matters for Alice and Bob are the outcomes of the
-measurements, which they will use to fill the entries asked by
-Charlie.)
+every row is \(+I\) and the product of every column is \(-I\).
 
@@
   \begin{equation}
-    \label{eq:outcomes-1r}
     \operatorname{Out}((I \otimes Z)_{A} \otimes (I \otimes I)_{B}) =
@@
       -1, \text{ proj. onto } \{\ket{i1jk} \mid i, j, k \in \{0, 1\}\}
-        \text{ with prob. } \frac{1}{2}, \\
+        \text{ with prob. } \frac{1}{2},
     \end{cases}
   \end{equation}
-  where the subscript \(A1\) denotes the state after Alice's first
-  measurement. Suppose that Alice has observed \(+1\). Notice that
+  Suppose that Alice has observed \(+1\). Notice that
   only two of the components of the \(+1\)-eigenspace are seen in the
@@
   \begin{equation}
-    \ket{\psi}_{A1} =  \frac{1}{\sqrt{2}}(\ket{0000} + \ket{1010}).
+    \ket{\psi}_{A1} =  \frac{1}{\sqrt{2}}(\ket{0000} + \ket{1010}),
   \end{equation}
-  For the second cell, Alice measures the observable \(Z \otimes I\),
-  whose possible outcomes are
+  where the subscript \(A1\) denotes the state after Alice's first
+  measurement.  For the second cell, Alice measures the observable
+  \(Z \otimes I\), whose possible outcomes are
   \begin{equation}
-    \label{eq:outcomes-1r}
     \operatorname{Out}((Z \otimes I)_{A} \otimes (I \otimes I)_{B}) =
@@
       -1, \text{ proj. onto } \{\ket{1ijk} \mid i, j, k \in \{0, 1\}\}
-        \text{ with prob. } \frac{1}{2}. \\
+        \text{ with prob. } \frac{1}{2}.
     \end{cases}
@@
   \end{equation}
+  Finally, Alice measures the observable \(Z \otimes Z\), whose
+  only possible outcomes is
+  \begin{equation}
+    \operatorname{Out}((Z \otimes Z)_{A} \otimes (I \otimes I)_{B}) =
+    \begin{cases}
+      -1, \text{ proj. onto } \{\ket{i\overline{i}jk} \mid i, j, k \in \{0, 1\}\}
+        \text{ with prob. } 1,
+    \end{cases}
+  \end{equation}
+  where \(\overline{i}\) is the \texttt{not} operator. Notice that,
+  because \(\ket{\psi}_{A2}\) falls exactly into the
+  \(-1\)-eigenspace, the only possible outcome is \(-1\), and the
+  state does not change, i.e. \(\ket{\psi}_{A3} = \ket{\psi}_{A2}\).
+  Alice, then, fills the first row with the values \(\{+1, -1, -1\}\),
+  whose product is, as required, \(+1\). Upon receiving Alice's
+  answer, Charlie goes to meet Bob. Suppose he assigns the second
+  column to Bob. To fill in the value of the first cell (which is the
+  intersection of the first row and second column), Bob measures the
+  observable \(Z \otimes I\). Notice that \(\ket{\psi}_{A3}\) is
+  entirely in the \(-1\)-eigenspace; thus, Bob will for sure observe
+  the outcome \(-1\) ---~which matches Alice's answer~--- and the
+  state will not change: \(\ket{\psi}_{B1} = \ket{\psi}_{A3}\). Moving
+  on to the second cell, Bob measures the observable \(I \otimes X\),
+  whose possible outcomes are (for readability, we are showing only
+  the components of the eigenspaces that are not orthogonal to
+  \(\ket{\psi}_{B1}\))
+  \begin{equation}
+    \operatorname{Out}((I \otimes I)_{A} \otimes (I \otimes X)_{B}) =
+    \begin{cases}
+      +1, \text{ proj. onto } \frac{1}{\sqrt{2}}(\ket{1010} + \ket{1011})
+        \text{ with prob. } \frac{1}{2} \\
+      -1, \text{ proj. onto } \frac{1}{\sqrt{2}}(\ket{1010} - \ket{1011})
+        \text{ with prob. } \frac{1}{2}.
+    \end{cases}
+  \end{equation}
+  Assume that Bob has observed the outcome \(+1\). Then, the state
+  collapses to
+  \begin{equation}
+    \ket{\psi}_{B2} =  \frac{1}{\sqrt{2}}(\ket{1010} + \ket{1011}).
+  \end{equation}
+  Finally, Bob measures \(-Z \otimes X\) on his two qubits.
+  The only possible outcome is
+  \begin{equation}
+    \operatorname{Out}((I \otimes I)_{A} \otimes (-Z \otimes X)_{B}) =
+    \begin{cases}
+      +1, \text{ proj. onto } \frac{1}{\sqrt{2}}(\ket{1010} + \ket{1011})
+      \text{ with prob. } 1,
+    \end{cases}
+  \end{equation}
+  and the state does not change, i.e.
+  \(\ket{\psi}_{B3} = \ket{\psi}_{B2}\). Alice's answer satisfies the
+  property of the rows (that the product of the entries is equal to
+  \(+1\)) and Bob's answer satisfies the property of the columns
+  (product is equal to \(-1\)).  Moreover, Alice and Bob agreed in the
+  intersection of the row and the column.  Hence, they won this round!
 \end{tcbexample}
-
 \section{Quantum Unitaries (? research)}

### 2023-06-07 paper/main.tex
Summary quantum strat

@@
 observables at each cell are \(\pm 1\). Furthermore, the product of
-every row is \(+I\) and the product of every column is \(-I\).
+every row is \(+I\) and the product of every column is \(-I\).  The
+quantum strategy works as follows: Alice measures all the observables
+from the \(i\)-th row of the predefined matrix. She fills each cell
+with the result of each measurement. Similarly, Bob measures all the
+observables in the \(j\)-th column that was assigned to him, and fills
+each cell of his column with the outcomes of each
+measurement. Example~\ref{ex:quantum-sol} depicts a round of the game.
 

### 2023-06-07 paper/main.tex
Simplifying quantum example

@@
     \begin{cases}
-      +1, \text{ proj. onto } \{\ket{i0jk} \mid i, j, k \in \{0, 1\}\}
-        \text{ with prob. } \frac{1}{2} \\
-      -1, \text{ proj. onto } \{\ket{i1jk} \mid i, j, k \in \{0, 1\}\}
-        \text{ with prob. } \frac{1}{2},
+      +1 \left(I \otimes \ketbra{0}{0} \otimes I \otimes I\right)
+        &\text{with probability } \frac{1}{2} \\
+      -1 \left(I \otimes \ketbra{1}{1} \otimes I \otimes I\right)
+        &\text{with probability } \frac{1}{2},
     \end{cases}
   \end{equation}
-  Suppose that Alice has observed \(+1\). Notice that
-  only two of the components of the \(+1\)-eigenspace are seen in the
-  initial state \(\ket{\psi}\): \(\ket{0000}\) and
-  \(\ket{1010}\). Therefore, \(\ket{\psi}\) collapses to
+  Suppose that Alice has observed \(+1\). In this case, the initial
+  state \(\ket{\psi}\) collapses to
   \begin{equation}
@@
     \begin{cases}
-      +1, \text{ proj. onto } \{\ket{0ijk} \mid i, j, k \in \{0, 1\}\}
-        \text{ with prob. } \frac{1}{2} \\
-      -1, \text{ proj. onto } \{\ket{1ijk} \mid i, j, k \in \{0, 1\}\}
-        \text{ with prob. } \frac{1}{2}.
+      +1 \left(\ketbra{0}{0} \otimes I \otimes I \otimes I\right)
+        &\text{with probability } \frac{1}{2} \\
+      -1 \left(\ketbra{1}{1} \otimes I \otimes I \otimes I\right)
+        &\text{with probability } \frac{1}{2}.
     \end{cases}
   \end{equation}
-  Suppose, now, that Alice has observed the outcome \(-1\). Notice that
-  only one component of the \(-1\)-eigenspace is seen in the state
-  \(\ket{\psi}_{A1}\). Hence, the state collapses to
+  Suppose, now, that Alice has observed the outcome \(-1\). The state
+  collapses to
   \begin{equation}
@@
   Finally, Alice measures the observable \(Z \otimes Z\), whose
-  only possible outcomes is
+  possible outcomes are
   \begin{equation}
@@
     \begin{cases}
-      -1, \text{ proj. onto } \{\ket{i\overline{i}jk} \mid i, j, k \in \{0, 1\}\}
-        \text{ with prob. } 1,
+      +1 \left(\left(\ketbra{00}{00} + \ketbra{11}{11}\right) \otimes I \otimes I\right)
+      &\text{with probability } 0 \\
+      -1 \left(\left(\ketbra{01}{01} + \ketbra{10}{10}\right) \otimes I \otimes I\right)
+      &\text{with probability } 1.
     \end{cases}
   \end{equation}
-  where \(\overline{i}\) is the \texttt{not} operator. Notice that,
-  because \(\ket{\psi}_{A2}\) falls exactly into the
-  \(-1\)-eigenspace, the only possible outcome is \(-1\), and the
-  state does not change, i.e. \(\ket{\psi}_{A3} = \ket{\psi}_{A2}\).
-  Alice, then, fills the first row with the values \(\{+1, -1, -1\}\),
-  whose product is, as required, \(+1\). Upon receiving Alice's
-  answer, Charlie goes to meet Bob. Suppose he assigns the second
-  column to Bob. To fill in the value of the first cell (which is the
-  intersection of the first row and second column), Bob measures the
-  observable \(Z \otimes I\). Notice that \(\ket{\psi}_{A3}\) is
-  entirely in the \(-1\)-eigenspace; thus, Bob will for sure observe
-  the outcome \(-1\) ---~which matches Alice's answer~--- and the
-  state will not change: \(\ket{\psi}_{B1} = \ket{\psi}_{A3}\). Moving
-  on to the second cell, Bob measures the observable \(I \otimes X\),
-  whose possible outcomes are (for readability, we are showing only
-  the components of the eigenspaces that are not orthogonal to
-  \(\ket{\psi}_{B1}\))
+  Notice that the only possible outcome that Alice can observe is
+  \(-1\), and the state does not change, i.e.
+  \(\ket{\psi}_{A3} = \ket{\psi}_{A2}\).  Alice, then, fills the first
+  row with the values \(\{+1, -1, -1\}\), whose product is, as
+  required, \(+1\). Upon receiving Alice's answer, Charlie goes to
+  meet Bob. Suppose he assigns the second column to Bob. To fill in
+  the value of the first cell (which is the intersection of the first
+  row and second column), Bob measures the observable \(Z \otimes
+  I\). The only possible outcome, considering the state
+  \(\ket{\psi}_{A3}\), is \(-1\) ---~which matches Alice's answer~---
+  and the state will not change again:
+  \(\ket{\psi}_{B1} = \ket{\psi}_{A3}\). Moving on to the second cell,
+  Bob measures the observable \(I \otimes X\), whose possible outcomes
+  are
   \begin{equation}
@@
     \begin{cases}
-      +1, \text{ proj. onto } \frac{1}{\sqrt{2}}(\ket{1010} + \ket{1011})
-        \text{ with prob. } \frac{1}{2} \\
-      -1, \text{ proj. onto } \frac{1}{\sqrt{2}}(\ket{1010} - \ket{1011})
-        \text{ with prob. } \frac{1}{2}.
+      +1 \left(I \otimes I \otimes I \otimes \ketbra{+}{+}\right)
+      &\text{with probability } \frac{1}{2} \\
+      -1 \left(I \otimes I \otimes I \otimes \ketbra{-}{-}\right)
+      &\text{with probability } \frac{1}{2}.
     \end{cases}
@@
   Finally, Bob measures \(-Z \otimes X\) on his two qubits.
-  The only possible outcome is
+  The possible outcomes are
   \begin{equation}
@@
     \begin{cases}
-      +1, \text{ proj. onto } \frac{1}{\sqrt{2}}(\ket{1010} + \ket{1011})
-      \text{ with prob. } 1,
+      +1 \left(I \otimes I \otimes \left(\ketbra{1+}{1\!+\!} + \ketbra{0-}{0\!-\!}\right)\right)
+      &\text{with prob. } 1 \\
+      -1 \left(I \otimes I \otimes \left(\ketbra{1-}{1\!-\!} + \ketbra{0+}{0\!+\!}\right)\right)
+      &\text{with prob. } 0.
     \end{cases}
   \end{equation}
-  and the state does not change, i.e.
-  \(\ket{\psi}_{B3} = \ket{\psi}_{B2}\). Alice's answer satisfies the
-  property of the rows (that the product of the entries is equal to
-  \(+1\)) and Bob's answer satisfies the property of the columns
-  (product is equal to \(-1\)).  Moreover, Alice and Bob agreed in the
-  intersection of the row and the column.  Hence, they won this round!
+  Bob will for sure observe the outcome \(+1\) and the state does not
+  change, i.e.  \(\ket{\psi}_{B3} = \ket{\psi}_{B2}\). Therefore, Bob
+  answers \(\{-1, +1, +1\}\). Alice's answer satisfies the property of
+  the rows (that the product of the entries is equal to \(+1\)) and
+  Bob's answer satisfies the property of the columns (product is equal
+  to \(-1\)).  Moreover, Alice and Bob agreed in the intersection of
+  the row and the column.  Hence, they won this round!
 \end{tcbexample}

### 2023-06-22 paper/main.tex
Proof product rows and columns (without figure)

@@
 \paragraph{Outline of this paper.}
-\section{Contextuality}
-\label{sec:local-context}
 
@@
       \\ \hhline{---~}
-      -X \otimes Z & -Z \otimes X & +Y \otimes Y & \prod = -\ci{}I \otimes \ci{}I = I
+      -X \otimes Z & -Z \otimes X & +Y \otimes Y & \prod = \ci{}I \otimes -\ci{}I = I
       \\ \hhline{---~}
@@
       & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -I \otimes I = -I}
-      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = \ci{}I \otimes \ci{}I = -I}
+      & \multicolumn{1}{>{\quad}c<{\quad}}{\prod = -\ci{}I \otimes -\ci{}I = -I}
     \end{array}\]
@@
 \end{tcbexample}
+
+\subsection{Formal Proof}
+To prove that the quantum solution indeed works, we must demonstrate
+two fundamental properties. First, the product of the outcomes of the
+three measurements on each row (equivalently, column) is equal to 1
+(equiv. -1). Second, the outcome of Alice's measurements on the
+intersection is always equal to the outcome of Bob's
+measurement. Lemma~\ref{lem:product} formalizes the product property.
+
+\begin{lemma}[The Product Property of the Quantum Solution]
+  \label{lem:product}
+  Let \(M_{i, j}\) be the observable at the cell \((i, j)\) of the
+  \(3 \times 3\) grid shown in Figure~\ref{fig:quantum}. Then,
+  it follows that
+
+  \begin{align}
+    \textit{for every }i, \prod_{j} \operatorname{Out}(M_{i, j}) &= +1  \textit{, and} \\
+    \textit{for every }j, \prod_{i} \operatorname{Out}(M_{i, j}) &= -1.
+  \end{align}
+\end{lemma}
+
+\begin{proof}
+  \label{proof:product}
+  First, notice that \(X^{2} = Z^{2} = Y^{2} = I\), \(XZ = \ci{}Y\) and
+  \(ZX = -\ci{}Y\) (i.e. \(X\) and \(Z\) anticommute), and, similarly,
+  \(XY = \ci{}Z\) and \(YX = -\ci{}Z\). Using these properties, we can see
+  that the product of every row (equiv. column) is the identity \(I\)
+  (equiv. \(-I\)), regardless of the order of the three observables.
+  That is, the three observables of every row and every column
+  mutually commute (or, in other words, they are compatible).
+  Consequently, for every row and every column, it is possible to find
+  a basis of eigenvectors that are common to the three observables,
+  meaning that they can be simultaneous
+  diagonalized. Figure~\ref{fig:eigenv} shows these common
+  eigenvectors. Let  \(M_{i, j}\) be the observables at each cell.
+  Then, for every row \(i\) (equiv. column \(j\)), we have
+  \begin{align}
+    M_{i, 0} M_{i, 1} M_{i, 2}
+    &= (P_{i} \Lambda_{i, 0} P_{i}^{-1}) (P_{i}\Lambda_{i, 1}P_{i}^{-1}) (P_{i}\Lambda_{i, 2}P_{i}^{-1})
+      \nonumber \\
+    &= P_{i}(\Lambda_{i, 0} \Lambda_{i, 1} \Lambda_{i, 2})P_{i}^{-1} \nonumber \\
+    &= P_{i}\Lambda_{i}P_{i}^{-1},
+  \end{align}
+  where \(P_{i}\) is the matrix whose columns are the common
+  eigenvectors and \(\Lambda_{i}\) is the matrix whose diagonal is
+  formed by the products of the eigenvalues of the observables,
+  associated with the same eigenvector. What this essentially means is
+  that any measurement \(M_{i, j}\) yields one of the eigenvalues
+  \(\lambda\) in the diagonal of \(\Lambda_{i, j}\) and collapses the
+  state to a linear combination of one of the two shared eigenvectors
+  \(\ket{\lambda}_{1}\) and \(\ket{\lambda}_{2}\) in the
+  \(\lambda\)-eigenspace. Then, the second measurement will collapse
+  the state to either \(\ket{\lambda}_{1}\) or \(\ket{\lambda}_{2}\).
+  Consequently, the third measurement will not change the state any
+  further. Therefore, the product of the three outcomes will be the
+  product of the eigenvalues associated with either
+  \(\ket{\lambda}_{1}\) or \(\ket{\lambda}_{2}\), which is one of the
+  entries in the diagonal of \(\Lambda_{i}\). But, notice that
+  \(P_{i}\Lambda_{i}P_{i}^{-1} = I\); thus, \(\Lambda_{i} = I\) and
+  the only possible value for the product is \(1\) (equiv. \(-1\) for
+  columns).
+\end{proof}
+
 \section{Quantum Unitaries (? research)}
@@
 
+\section{Contextuality}
+\label{sec:context}
+
 \printbibliography{}

### 2023-06-23 paper/main.tex
Tables shared eigenvectors

@@
 \usepackage{bigdelim}
+\usepackage{booktabs}
 
@@
   \label{proof:product}
-  First, notice that \(X^{2} = Z^{2} = Y^{2} = I\), \(XZ = \ci{}Y\) and
-  \(ZX = -\ci{}Y\) (i.e. \(X\) and \(Z\) anticommute), and, similarly,
-  \(XY = \ci{}Z\) and \(YX = -\ci{}Z\). Using these properties, we can see
-  that the product of every row (equiv. column) is the identity \(I\)
-  (equiv. \(-I\)), regardless of the order of the three observables.
-  That is, the three observables of every row and every column
-  mutually commute (or, in other words, they are compatible).
-  Consequently, for every row and every column, it is possible to find
-  a basis of eigenvectors that are common to the three observables,
-  meaning that they can be simultaneous
-  diagonalized. Figure~\ref{fig:eigenv} shows these common
-  eigenvectors. Let  \(M_{i, j}\) be the observables at each cell.
-  Then, for every row \(i\) (equiv. column \(j\)), we have
+  First, notice that \(X^{2} = Z^{2} = Y^{2} = I\), \(XZ = \ci{}Y\)
+  and \(ZX = -\ci{}Y\) (i.e. \(X\) and \(Z\) anticommute), and,
+  similarly, \(XY = \ci{}Z\) and \(YX = -\ci{}Z\). Using these
+  properties, we can see that the product of every row (equiv. column)
+  is the identity \(I\) (equiv. \(-I\)), regardless of the order of
+  the three observables.  That is, the three observables of every row
+  and every column mutually commute (or, in other words, they are
+  compatible).  Consequently, for every row and every column, it is
+  possible to find a basis of eigenvectors that are common to the
+  three observables, meaning that they can be diagonalized
+  simultaneously. Tables~\ref{tab:eigenv-rows} and \ref{tab:eigenv-cols} show
+  these common eigenvectors. Let \(M_{i, j}\) be the observables at
+  each cell.  Then, for every row \(i\) (equiv. column \(j\)), we have
   \begin{align}
@@
   that any measurement \(M_{i, j}\) yields one of the eigenvalues
-  \(\lambda\) in the diagonal of \(\Lambda_{i, j}\) and collapses the
-  state to a linear combination of one of the two shared eigenvectors
+  \(\lambda\) in the diagonal of \(\Lambda_{i, j}\) and projects the
+  state onto the \(\lambda\)-eigenspace. That is, it collapses the
+  state to a linear combination of the two shared eigenvectors
   \(\ket{\lambda}_{1}\) and \(\ket{\lambda}_{2}\) in the
   \(\lambda\)-eigenspace. Then, the second measurement will collapse
-  the state to either \(\ket{\lambda}_{1}\) or \(\ket{\lambda}_{2}\).
-  Consequently, the third measurement will not change the state any
-  further. Therefore, the product of the three outcomes will be the
-  product of the eigenvalues associated with either
-  \(\ket{\lambda}_{1}\) or \(\ket{\lambda}_{2}\), which is one of the
-  entries in the diagonal of \(\Lambda_{i}\). But, notice that
+  the state to either \(\ket{\lambda}_{1}\) or \(\ket{\lambda}_{2}\),
+  eigenvectors common to the three observables.  Consequently, the
+  third measurement will not change the state any further. Therefore,
+  the product of the three outcomes will be the product of the
+  eigenvalues associated with either \(\ket{\lambda}_{1}\) or
+  \(\ket{\lambda}_{2}\), which is one of the entries in the diagonal
+  of \(\Lambda_{i}\). But, notice that
   \(P_{i}\Lambda_{i}P_{i}^{-1} = I\); thus, \(\Lambda_{i} = I\) and
-  the only possible value for the product is \(1\) (equiv. \(-1\) for
-  columns).
+  the only possible value for the product is \(1\) (equivalently
+  \(-1\) for columns). \qed
 \end{proof}
+
+\begin{table}[htbp]
+  \centering
+  \caption{Eigenvectors shared by the observables at each row of the quantum magic square.
+    The eigenvectors were taken from~\ref{xxx}, adapting to the correct eigenvalues.}
+  \label{tab:eigenv-rows}
+  \begin{tabular}{c*{4}{>{\;\;}c}}
+    \toprule
+    & & Column 1 & Column 2 & Column 3 \\
+    \midrule
+    \multirow{2}{*}{Row 1} & \(+1\)
+      & \ket{00}, \ket{10} & \ket{00}, \ket{01} & \ket{00}, \ket{11} \\
+    & \(-1\)
+      & \ket{01}, \ket{11} & \ket{10}, \ket{11} & \ket{01}, \ket{10} \\
+    \midrule
+    \multirow{4}{*}{Row 2} & \multirow{2}{*}{\(+1\)}
+      & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} + \ket{11})\),
+                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} + \ket{11})\),
+                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} + \ket{11})\), \\ 
+    & & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} - \ket{11})\)\phantom{,} 
+                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} - \ket{11})\)\phantom{,} 
+                            & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\)\phantom{,} \\[1.5mm]
+    & \multirow{2}{*}{\(-1\)}
+      & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\),
+                 & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\),
+                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} - \ket{11})\), \\ 
+    & & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} - \ket{11})\)\phantom{,} 
+                 & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} - \ket{11})\)\phantom{,} 
+                            & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} - \ket{11})\)\phantom{,} \\
+    \midrule
+    \multirow{4}{*}{Row 3} & \multirow{2}{*}{\(+1\)}
+      & \((\nicefrac{1}{2}) (\ket{01} - \ket{00} + \ket{10} + \ket{11})\),
+                 & \((\nicefrac{1}{2}) (\ket{01} - \ket{00} + \ket{10} + \ket{11})\),
+                            & \((\nicefrac{1}{2}) (\ket{01} - \ket{00} + \ket{10} + \ket{11})\), \\ 
+    & & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} + \ket{11})\),
+                 & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} + \ket{11})\),
+                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} - \ket{11})\), \\[1.5mm]
+    & \multirow{2}{*}{\(-1\)}
+      & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} + \ket{11})\),
+                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} + \ket{11})\),
+                            & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} + \ket{11})\), \\
+    & & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} - \ket{11})\),
+                 & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} - \ket{11})\),
+                            & \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} + \ket{11})\), \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{table}[htbp]
+  \centering
+  \caption{Eigenvectors shared by the observables at each column of the quantum magic square.
+    The eigenvectors were taken from~\ref{xxx}, adapting to the correct eigenvalues.}
+  \label{tab:eigenv-cols}
+  \begin{tabular}{c*{4}{>{\;\;}c}}
+    \toprule
+    & & Row 1 & Row 2 & Row 3 \\
+    \midrule
+    \multirow{4}{*}{Column 1} & \multirow{2}{*}{\(+1\)}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{10})\),
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{10})\), 
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{10})\), \\
+    & &  \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{10})\)\phantom{,}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{11})\)\phantom{,}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{11})\)\phantom{,} \\[1.5mm]
+    & \multirow{2}{*}{\(-1\)}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{11})\), 
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{10})\), 
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{10})\), \\
+    & & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{11})\)\phantom{,}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{11})\)\phantom{,}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{11})\)\phantom{,} \\
+    \midrule
+    \multirow{4}{*}{Column 2} & \multirow{2}{*}{\(+1\)}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{01})\),
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{01})\), 
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{01})\), \\
+    & &  \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{01})\)\phantom{,}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} + \ket{11})\)\phantom{,}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} + \ket{11})\)\phantom{,} \\[1.5mm]
+    & \multirow{2}{*}{\(-1\)}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} + \ket{11})\), 
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{01})\), 
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{01})\), \\
+    & & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} - \ket{11})\)\phantom{,}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} - \ket{11})\)\phantom{,}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{10} - \ket{11})\)\phantom{,} \\
+    \midrule
+        \multirow{4}{*}{Column 3} & \multirow{2}{*}{\(+1\)}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{11})\),
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{11})\), 
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{10})\), \\
+    & &  \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{11})\)\phantom{,}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{10})\)\phantom{,}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{11})\)\phantom{,} \\[1.5mm]
+    & \multirow{2}{*}{\(-1\)}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} + \ket{10})\), 
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{11})\), 
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{11})\), \\
+    & & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{10})\)\phantom{,}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{10})\)\phantom{,}
+      & \((\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{10})\)\phantom{,} \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 

### 2023-06-24 paper/main.tex
Proof for intersection

@@
 
+Lemma~\ref{lem:product} shows that the quantum solution satisfies the
+requirements of the game for every row and column. Now, we move on to
+show that Alice and Bob always agree in the value that they assign
+to the intersection of the row and column.
+
+\begin{lemma}[The Intersection Property of the Quantum Solution]
+  \label{lem:intersection}
+  For any row \(i\) assigned to Alice and column \(j\) assigned to
+  Bob, the value ascribed to the cell \((i, j)\) by Alice and Bob,
+  after they have performed their measurements, is always the same.
+\end{lemma}
+
+\begin{proof}
+  To prove that Alice and Bob agree at the intersection, it suffices
+  to look to the eigenvectors shared by each set of mutually commuting
+  operators, shown in Tables~\ref{tab:eigenv-rows} and
+  \ref{tab:eigenv-cols}.  Notice that, regardless of the row assigned
+  to Alice, the state of her subsystem after her measurements is
+  always one of the eigenvectors in that row. This state is always a
+  linear combination of one of Bob's eigenspaces for the cell in the
+  intersection (the same applies if we consider first Bob than Alice).
+  Take, for instance, the second row and first column. Suppose that
+  Alice's measurements collapsed her qubits to
+  \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\).
+  This state can be written as
+  \((\nicefrac{1}{\sqrt{2}}) (\ket{00} - \ket{10}) -
+  (\nicefrac{1}{\sqrt{2}}) (\ket{01} - \ket{11})\), a linear
+  combination of the \(-1\)-eigenspace depicted in
+  Table~\ref{tab:eigenv-cols} (column 1, row 2).  What is left is to
+  show that Bob's state will be exactly the same as Alice's, implying
+  that Bob shall observe the same result. This follows from the fact
+  that the initial state is already symmetric (the first qubit of
+  Alice is equal to the first qubit of Bob; the same is true for their
+  second qubits) and the symmetry is preserved by any measurement
+  performed by Alice and Bob. For the first row, it is easy to see.
+  The others are trickier, but it all boils down to doing the
+  calculations.  Consider, for instance, the second row, and suppose
+  that the outcomes were \(-1\), \(-1\) and \(+1\), so that Alice's
+  state collapsed to
+  \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} +
+  \ket{11})\). The state after the first measurement is
+  \begin{align}
+    &\frac{1}{2\sqrt{2}} \Bigl(
+    (\ket{00} - \ket{10}) \ket{00} +
+    (\ket{01} - \ket{11}) \ket{01} +
+    (\ket{10} - \ket{00}) \ket{10} +
+    (\ket{11} - \ket{01}) \ket{11}
+    \Bigr) \nonumber \\
+    \equiv\;
+    & \frac{1}{2\sqrt{2}} \Bigl(
+      \ket{00} (\ket{00} - \ket{10}) +
+      \ket{01} (\ket{01} - \ket{11}) +
+      \ket{10} (\ket{10} - \ket{00}) +
+      \ket{11} (\ket{11} - \ket{01})
+    \Bigr).
+  \end{align}
+  And, the state after the three measurements is
+  \begin{alignat}{2}
+    &\frac{1}{4} \Bigl(
+      &&(\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{00} -
+        (\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{01} - \nonumber \\
+    & &&(\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{10} +
+      (\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{11}
+    \Bigr) \nonumber \\
+    \equiv\;
+    & \frac{1}{4} \Bigl(
+      &&\ket{00} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) -
+        \ket{01} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) - \nonumber \\
+    & &&\ket{10} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) +
+        \ket{11} (\ket{00} - \ket{01} - \ket{10} + \ket{11})
+    \Bigr).
+  \end{alignat}
+  The calculations for the other rows and columns are similar, so we omitted them.
+  \qed
+\end{proof}
 \section{Quantum Unitaries (? research)}

### 2023-06-29 paper/main.tex
circuits row

@@
 \DeclareMathOperator{\tr}{tr}
+\newcommand{\cnot}{\mathit{CNOT}}
 
@@
   \end{quantikz}
-  \caption{\label{fig:circuit-psi}}
+  \caption{Quantum circuit for preparing the initial joint state
+    of Alice and Bob.\label{fig:circuit-psi}}
 \end{figure}
@@
 observables in the \(j\)-th column that was assigned to him, and fills
-each cell of his column with the outcomes of each
+each cell of his cells with the outcomes of each
 measurement. Example~\ref{ex:quantum-sol} depicts a round of the game.
@@
     \end{array}\]
-  \caption{\label{fig:quantum}}
+  \caption{Observables used by Alice and Bob to win the Magic Square game.\label{fig:quantum}}
 \end{figure}}
@@
 three measurements on each row (equivalently, column) is equal to 1
-(equiv. -1). Second, the outcome of Alice's measurements on the
+(equiv. -1). Second, the outcome of Alice's measurement on the
 intersection is always equal to the outcome of Bob's
@@
   \end{align}
-  And, the state after the three measurements is
+  And, the state after the second measurement is
   \begin{alignat}{2}
@@
 \end{proof}
-\section{Quantum Unitaries (? research)}
-\label{sec:quantum-unitaries}
+
+\subsection{Implementing with Circuits}
+In this section, we show the circuits used to implement the quantum
+strategy. We implemented the solution using the \texttt{Qiskit}
+library. \texttt{Qiskit} only allows measurements in the computational
+basis. For any other basis \(B\), we must find an unitary
+transformation \(U\) such that \(B = U^{*} (Z \otimes I) U\) (where
+\(U^{*}\) denotes the Hermitian adjoint of \(U\)). For example,
+\(Z \otimes Z = \cnot{} (I \otimes Z) \cnot{}\) and
+\(X \otimes X = (H \otimes H) (Z \otimes Z) (H \otimes H)\). Figure~\ref{fig:change-basis}
+shows the unitaries for each of the nine observables.
+
+{\renewcommand{\arraystretch}{2}
+\begin{figure}
+  \centering
+  \[\begin{array}{|*{2}{>{\quad}c<{\quad}|}>{\quad}l<{\quad}|}
+      \hhline{---}
+      (I \otimes I) (Z \otimes I) (I \otimes I) & (I \otimes I) (I \otimes Z) (I \otimes I) & \cnot (I \otimes Z) \cnot
+      \\ \hhline{---}
+      (H \otimes I) (Z \otimes I) (H \otimes I) & (I \otimes H) (I \otimes Z) (I \otimes H) & (H \otimes H) (Z \otimes Z) (H \otimes H)
+      \\ \hhline{---}
+      (H \otimes Y) (Z \otimes Z) (H \otimes Y) & (Y \otimes H) (Z \otimes Z) (Y \otimes H) &
+       (S \otimes S) (X \otimes X) (S^{*} \otimes S^{*}) 
+      \\ \hhline{---}
+    \end{array}\]
+  \caption{Unitary transformations required for measuring in the
+    different basis. The actual basis measured is the middle
+    term of each cell, which, after expanding, is either
+    \(Z \otimes I\) or \(I \otimes Z\). For example, in the last
+    cell, \(X \otimes X\) evaluates to
+    \((H \otimes H) (Z \otimes Z) (H \otimes H)\).
+    \(Z \otimes Z\), in turn, becomes \(\cnot (I \otimes Z) \cnot\), meaning that
+    we measure the second qubit in the computational basis.\label{fig:change-basis}}
+\end{figure}}
+
+We now show the quantum circuits for each row and each column:
+
+\begin{description}
+\item[Row 0:] When assigned the first row, Alice performs the measurements
+  \(I \otimes Z, Z \otimes I\) and \(Z \otimes Z\), which the circuit
+  in Figure~\ref{fig:circ-row0} implements.
+
+  \begin{figure}[htbp]
+    \centering
+    \begin{quantikz}
+      \lstick{\(A_{0}\)}
+      & \metercw[label style={inner sep=1pt}]{a_{1}}
+      & \targ{}
+      &
+      & \targ{}
+      &
+      \\
+      \lstick{\(A_{1}\)}
+      & \metercw[label style={inner sep=1pt}]{a_{0}}
+      & \ctrl{-1}
+      & \metercw[label style={inner sep=1pt}]{a_{2}}
+      & \ctrl{-1}
+      &
+    \end{quantikz}
+    \caption{Quantum circuit for measuring the first row.\label{fig:circ-row0}}
+  \end{figure}
+
+  \item[Row 1:] When assigned the second row, Alice performs the measurements
+  \(X \otimes I, I \otimes X\) and \(X \otimes X\), which the circuit
+  in Figure~\ref{fig:circ-row1} implements.
+
+  \begin{figure}[htbp]
+    \centering
+    \begin{quantikz}
+      \lstick{\(A_{0}\)}
+      & \gate{H}
+      & \metercw[label style={inner sep=1pt}]{a_{0}}
+      & \ctrl{1}
+      &
+      & \ctrl{1}
+      & \gate{H}
+      &
+      \\
+      \lstick{\(A_{1}\)}
+      & \gate{H}
+      & \metercw[label style={inner sep=1pt}]{a_{1}}
+      & \targ{}
+      &  \metercw[label style={inner sep=1pt}]{a_{2}}
+      & \targ{}
+      & \gate{H}
+      &
+    \end{quantikz}
+    \caption{Quantum circuit for measuring the second row.\label{fig:circ-row1}}
+  \end{figure}
+
+    \item[Row 2:] When assigned the third row, Alice performs the measurements
+  \(-X \otimes Z, -Z \otimes X\) and \(Y \otimes Y\), which the circuit
+  in Figure~\ref{fig:circ-row2} implements.
+
+  \begin{figure}[htbp]
+    \centering
+    \begin{quantikz}[column sep=0.25cm]
+      \lstick{\(A_{0}\)}
+      & \gate{H}
+      & \ctrl{1}
+      &
+      & \ctrl{1}
+      & \gate{H}
+      & \gate{Y}
+      & \ctrl{1}
+      &
+      & \ctrl{1}
+      & \gate{S}
+      & \gate{H}
+      & \ctrl{1}
+      &
+      & \ctrl{1}
+      & \gate{H}
+      & \gate{S^*}
+      \\
+      \lstick{\(A_{1}\)}
+      & \gate{Y}
+      & \targ{}
+      & \metercw[label style={inner sep=1pt}]{a_{0}}
+      & \targ{}
+      & \gate{Y}
+      & \gate{H}
+      & \targ{}
+      & \metercw[label style={inner sep=1pt}]{a_{1}}
+      & \targ{}
+      & \gate{S}
+      & \gate{H}
+      & \targ{}
+      & \metercw[label style={inner sep=1pt}]{a_{2}}
+      & \targ{}
+      & \gate{H}
+      & \gate{S^*}
+    \end{quantikz}
+    \caption{Quantum circuit for measuring the third row.\label{fig:circ-row2}}
+  \end{figure}
+\end{description}
 
@@
 
+\section{Quantum Unitaries (? research)}
+\label{sec:quantum-unitaries}
+
 \printbibliography{}

### 2023-06-29 paper/main.tex
column circuits

@@
         \hhline{---}
-      (I \otimes I) (Z \otimes I) (I \otimes I) & (I \otimes I) (I \otimes Z) (I \otimes I) & \cnot (I \otimes Z) \cnot
+        (I \otimes I) (I \otimes Z) (I \otimes I) & (I \otimes I) (Z \otimes I) (I \otimes I) & \cnot (I \otimes Z) \cnot
         \\ \hhline{---}
@@
   \end{figure}
+
+\item[Column 0:] When assigned the first column, Bob performs the measurements
+  \(I \otimes Z, X \otimes I\) and \(-X \otimes Z\), which the circuit
+  in Figure~\ref{fig:circ-col0} implements.
+
+  \begin{figure}[htbp]
+    \centering
+    \begin{quantikz}
+      \lstick{\(B_{0}\)}
+      & \gate{H}
+      & \metercw[label style={inner sep=1pt}]{b_{1}}
+      &
+      & \ctrl{1}
+      &
+      & \ctrl{1}
+      & \gate{H}
+      &
+      \\
+      \lstick{\(B_{1}\)}
+      &
+      & \metercw[label style={inner sep=1pt}]{b_{0}}
+      & \gate{Y}
+      & \targ{}
+      & \metercw[label style={inner sep=1pt}]{b_{1}}
+      & \targ{}
+      & \gate{Y}
+      &
+    \end{quantikz}
+    \caption{Quantum circuit for measuring the first column.\label{fig:circ-col0}}
+  \end{figure}
+
+\item[Column 1:] When assigned the second column, Bob performs the measurements
+  \(Z \otimes I, I \otimes X\) and \(-Z \otimes X\), which the circuit
+  in Figure~\ref{fig:circ-col1} implements.
+
+  \begin{figure}[htbp]
+    \centering
+    \begin{quantikz}
+      \lstick{\(B_{0}\)}
+      & 
+      & \metercw[label style={inner sep=1pt}]{b_{0}}
+      & \gate{Y}
+      & \ctrl{1}
+      &
+      & \ctrl{1}
+      & \gate{Y}
+      &
+      \\
+      \lstick{\(B_{1}\)}
+      & \gate{H}
+      & \metercw[label style={inner sep=1pt}]{b_{1}}
+      & 
+      & \targ{}
+      & \metercw[label style={inner sep=1pt}]{b_{2}}
+      & \targ{}
+      & \gate{H}
+      &
+    \end{quantikz}
+    \caption{Quantum circuit for measuring the second column.\label{fig:circ-col1}}
+  \end{figure}
+
+\item[Column 2:] When assigned the third column, Bob performs the measurements
+  \(Z \otimes Z, X \otimes X\) and \(Y \otimes X\), which the circuit
+  in Figure~\ref{fig:circ-col2} implements.
+
+  \begin{figure}[htbp]
+    \centering
+    \begin{quantikz}[column sep=0.25cm]
+      \lstick{\(B_{0}\)}
+      & \ctrl{1}
+      &
+      & \ctrl{1}
+      & \gate{H}
+      & \ctrl{1}
+      &
+      & \ctrl{1}
+      & \gate{H}
+      & \gate{S}
+      & \gate{H}
+      & \ctrl{1}
+      &
+      & \ctrl{1}
+      & \gate{H}
+      & \gate{S^*}
+      &
+      \\
+      \lstick{\(B_{1}\)}
+      & \targ{}
+      & \metercw[label style={inner sep=1pt}]{b_{0}}
+      & \targ{}
+      & \gate{H}
+      & \targ{}
+      & \metercw[label style={inner sep=1pt}]{b_{1}}
+      & \targ{}
+      & \gate{H}
+      & \gate{S}
+      & \gate{H}
+      & \targ{}
+      & \metercw[label style={inner sep=1pt}]{b_{2}}
+      & \targ{}
+      & \gate{H}
+      & \gate{S^*}
+      &
+    \end{quantikz}
+    \caption{Quantum circuit for measuring the third column.\label{fig:circ-col2}}
+  \end{figure}
 \end{description}

### 2023-06-29 paper/main.tex
theorem quantum strategy

@@
   \qed
+
+  With Lemmas~\ref{lem:product} and~\ref{lem:intersection}, we can prove
+  Theorem~\ref{theo:quantum-wins}, which states that there is a quantum strategy
+  for the Mermin-Peres magic square game that always win.
+
+  \begin{theorem}[The Mermin-Peres Magic Square Game Is Winnable]
+    \label{theo:quantum-wins}
+    There exists a quantum strategy for the Mermin-Peres magic square
+    game, which consists of allowing Alice and Bob to exchange
+    entangled qubits \emph{before} the game begins, that wins with
+    certainty every round.
+  \end{theorem}
 \end{proof}

### 2023-06-30 slides/main.tex
Slides - intro

\documentclass[t, aspectratio=169, table]{beamer}

%%%%%%%%%%
%%% Packages
%%%%%%%%%%

\usepackage{xcolor}
\usepackage{hhline}

%%%%%%%%%%
%%% Sections
%%%%%%%%%%

\newif{\ifsectionPage}
\newcommand{\sectionPageDefault}{\global\sectionPagetrue}
\newcommand{\disableNextSectionPage}{\global\sectionPagefalse}
\sectionPageDefault{}
\AtBeginSection[]{%
  \ifsectionPage{}
    \frame{\sectionpage}
  \fi
  \sectionPageDefault{}}

%%%%%%%%%%
%%% Doc Info
%%%%%%%%%%

\newcommand{\email}[1]{\href{mailto:#1}{#1}}
\author[Luigi Soares \& Roberto Rosmaninho]{%
  Luigi Soares (\email{luigi.domenico@dcc.ufmg.br}) \\
  Roberto Rosmaninho (\email{TODO})}
\institute[DCC/UFMG]{}
\date{03/07/2023}
\title[Pseudotelepatia Quântica]{Pseudotelepatia Quântica (TODO)}

\usetheme{ufmg}

\begin{document}
\maketitle

\section{Quadrado Mágico}

\begin{frame}{Introdução ao Jogo}
  \begin{itemize}[<+->]
  \item Jogo cooperativo não-local
  \item Dois jogadores: Alice e Bob
  \item Um árbitro: Charlie
  \item Alice e Bob não podem se comunicar após o início
  \item A cada rodada:
    \begin{enumerate}[<+->]
    \item Charlie sorteia uma linha 0, 1 ou 2 de uma matriz \(3 \times 3\) e atribui à Alice
    \item Alice preenche as três células com \(+1\) ou \(-1\), de forma que o produto seja \(+1\)
    \item Charlie sorteia uma coluna 0, 1 ou 2 da matriz e atribui ao Bob
    \item Bob preenche as três células com \(+1\) ou \(-1\), de forma que o produto seja \(-1\)
    \item Alice e Bob vencem se respeitaram  e concordaram
      no valor da interseção
    \end{enumerate}
  \end{itemize}
\end{frame}

\begin{frame}{Exemplo 1 (Vitória)}
  \renewcommand{\arraystretch}{2}
  \vfill{}
  \begin{minipage}{0.45\textwidth}
    \begin{center}
      Alice \(\leftarrow 0\)
    \end{center}
    \[\begin{array}{|>{\quad}c<{\quad}|*{2}{>{\quad}c<{\quad}|}c}
        \hhline{---}
        +1 & \cellcolor{gray!50} -1 & -1 & \prod = +1
        \\ \hhline{---}
           & & &
        \\ \hhline{---}
           & & &
        \\ \hhline{---}
        \multicolumn{1}{c}{}
        & \multicolumn{1}{c}{}
        & \multicolumn{1}{c}{}
      \end{array}\]
  \end{minipage}
  \hfill{}
  \begin{minipage}{0.45\textwidth}
    \begin{center}
      Bob \(\leftarrow 1\)
    \end{center}
    \[\begin{array}{|>{\quad}c<{\quad}|*{2}{>{\quad}c<{\quad}|}}
        \hhline{---}
        \phantom{+1} & \cellcolor{gray!50}-1 & \phantom{-1}
        \\ \hhline{---}
           & +1 &
        \\ \hhline{---}
           & +1 &
        \\ \hhline{---}
        \multicolumn{1}{c}{}
        & \multicolumn{1}{c}{\prod = -1}
        & \multicolumn{1}{c}{}
      \end{array}\]
  \end{minipage}  
  \vfill{}
\end{frame}

\begin{frame}{Exemplo 2 (Derrota, Interseção)}
  \renewcommand{\arraystretch}{2}
  \vfill{}
  \begin{minipage}{0.45\textwidth}
    \begin{center}
      Alice \(\leftarrow 1\)
    \end{center}
    \[\begin{array}{|>{\quad}c<{\quad}|*{2}{>{\quad}c<{\quad}|}c}
        \hhline{---}
           & & &
        \\ \hhline{---}
        +1 & \cellcolor{red!80!black!55} -1 & -1 & \prod = +1
        \\ \hhline{---}
           & & &
        \\ \hhline{---}
        \multicolumn{1}{c}{}
        & \multicolumn{1}{c}{}
        & \multicolumn{1}{c}{}
      \end{array}\]
  \end{minipage}
  \hfill{}
  \begin{minipage}{0.45\textwidth}
    \begin{center}
      Bob \(\leftarrow 1\)
    \end{center}
    \[\begin{array}{|>{\quad}c<{\quad}|*{2}{>{\quad}c<{\quad}|}}
        \hhline{---}
        \phantom{+1} & -1 & \phantom{-1}
        \\ \hhline{---}
           & \cellcolor{red!80!black!55} +1 &
        \\ \hhline{---}
           & +1 &
        \\ \hhline{---}
        \multicolumn{1}{c}{}
        & \multicolumn{1}{c}{\prod = -1}
        & \multicolumn{1}{c}{}
      \end{array}\]
  \end{minipage}  
  \vfill{}
\end{frame}

\begin{frame}{Exemplo 3 (Derrota, Produto)}
  \renewcommand{\arraystretch}{2}
  \vfill{}
  \begin{minipage}{0.45\textwidth}
    \begin{center}
      Alice \(\leftarrow 1\)
    \end{center}
    \[\begin{array}{|>{\quad}c<{\quad}|*{2}{>{\quad}c<{\quad}|}c}
        \hhline{---}
           & & &
        \\ \hhline{---}
        +1 & \cellcolor{gray!50} +1 & -1 & \cellcolor{red!80!black!55}\prod = -1
        \\ \hhline{---}
           & & &
        \\ \hhline{---}
        \multicolumn{1}{c}{}
        & \multicolumn{1}{c}{}
        & \multicolumn{1}{c}{}
      \end{array}\]
  \end{minipage}
  \hfill{}
  \begin{minipage}{0.45\textwidth}
    \begin{center}
      Bob \(\leftarrow 1\)
    \end{center}
    \[\begin{array}{|>{\quad}c<{\quad}|*{2}{>{\quad}c<{\quad}|}}
        \hhline{---}
        \phantom{+1} & -1 & \phantom{-1}
        \\ \hhline{---}
           & \cellcolor{gray!50} +1 &
        \\ \hhline{---}
           & +1 &
        \\ \hhline{---}
        \multicolumn{1}{c}{}
        & \multicolumn{1}{c}{\prod = -1}
        & \multicolumn{1}{c}{}
      \end{array}\]
  \end{minipage}  
  \vfill{}
\end{frame}

\begin{frame}{Estratégia Clássica (Determinística)}
  \begin{itemize}[<+->]
  \item Alice e Bob não podem se comunicar \emph{durante} o jogo, mas
    podem \emph{antes}
  \item Uma estratégia determinística consiste em 
    preparem matrizes pré-definidas
  \end{itemize}

  \only<+->{
    \renewcommand{\arraystretch}{2}
    \vfill{}
    \begin{minipage}{0.45\textwidth}
      \begin{center}
        Alice
        \[\begin{array}{|>{\quad\columncolor{gray!50}}c<{\quad}|*{2}{>{\quad}c<{\quad}|}}
            \hhline{---}
            -1 & \onslide<+->{\only<.(1)->{\cellcolor{gray!50}}-1} & \onslide<.->{\only<.(2)->{\cellcolor{red!80!black!55}}+1}
            \\ \hhline{---}
            -1 & \onslide<.->{\only<.(1)->{\cellcolor{gray!50}}-1} & \onslide<.->{\only<.(2)->{\cellcolor{gray!50}}+1}
            \\ \hhline{---}
            -1 & \onslide<.->{\only<.(1)->{\cellcolor{gray!50}}-1} & \onslide<.->{\only<.(2)->{\cellcolor{gray!50}}+1}
            \\ \hhline{---}
          \end{array}\]
      \end{center}
    \end{minipage}
    \hfill{}
    \begin{minipage}{0.45\textwidth}
      \begin{center}
        Bob
        \[\begin{array}{|>{\quad\columncolor{gray!50}}c<{\quad}|*{2}{>{\quad}c<{\quad}|}}
            \hhline{---}
            -1 & \onslide<+->{\only<.->{\cellcolor{gray!50}}-1} & \onslide<.(1)->{\only<.(1)->{\cellcolor{red!80!black!55}}-1}
            \\ \hhline{---}
            -1 & \only<.->{\cellcolor{gray!50}-1} & \only<.(1)->{\cellcolor{gray!50}+1}
            \\ \hhline{---}
            -1 & \only<.->{\cellcolor{gray!50}-1} & \only<.(1)->{\cellcolor{gray!50}+1}
            \\ \hhline{---}
          \end{array}\]
      \end{center}
    \end{minipage}  
    \vfill{}
  }
\end{frame}
\end{document}

### 2023-06-30 slides/main.tex
up to lemma 1

@@
 \usepackage{hhline}
+\usepackage{booktabs}
+\usepackage{nicefrac}
+\usepackage{tikz}
+\usetikzlibrary{quantikz2}
+\usepackage{tcolorbox}
+\tcbuselibrary{theorems}
+
+\newtcbtheorem{tcblemma}{Lema}{
+  boxrule=0.15mm,
+  colback=gray!15,
+  % colbacktitle=gray!15,
+  % coltitle=red!50!black,
+  % fonttitle=\bfseries,
+  coltext=red!40!black,
+  detach title,
+  % before upper={\tcbtitle},
+  % separator sign none,
+  % description delimiters={(}{). }
+}{lem}
+
+\newcommand{\ketbra}[2]{\ensuremath{| #1 \rangle \langle #2 |}}
+\newcommand{\ci}{\mathrm{i}}
+\DeclarePairedDelimiter{\card}{\lvert}{\rvert}
+\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
+\DeclareMathOperator{\tr}{tr}
+\newcommand{\cnot}{\mathit{CNOT}}
 
@@
     podem \emph{antes}
+
   \item Uma estratégia determinística consiste em 
-    preparem matrizes pré-definidas
+    prepar matrizes pré-definidas
+
+  \item<only@7-> É impossível vencer com 100\% de chance toda rodada
+
+  \item<only@9-> A melhor estratégia determinística vence com probabilidade \(\nicefrac{8}{9}\)
   \end{itemize}
 
-  \only<+->{
+  \only<3-6>{
     \renewcommand{\arraystretch}{2}
@@
             \hhline{---}
-            -1 & \onslide<+->{\only<.(1)->{\cellcolor{gray!50}}-1} & \onslide<.->{\only<.(2)->{\cellcolor{red!80!black!55}}+1}
+            -1 & \onslide<4->{\only<5->{\cellcolor{gray!50}}-1} & \onslide<4->{\only<6->{\cellcolor{red!80!black!55}}+1}
             \\ \hhline{---}
-            -1 & \onslide<.->{\only<.(1)->{\cellcolor{gray!50}}-1} & \onslide<.->{\only<.(2)->{\cellcolor{gray!50}}+1}
+            -1 & \onslide<4->{\only<5->{\cellcolor{gray!50}}-1} & \onslide<4->{\only<6->{\cellcolor{gray!50}}+1}
             \\ \hhline{---}
-            -1 & \onslide<.->{\only<.(1)->{\cellcolor{gray!50}}-1} & \onslide<.->{\only<.(2)->{\cellcolor{gray!50}}+1}
+            -1 & \onslide<4->{\only<5->{\cellcolor{gray!50}}-1} & \onslide<4->{\only<6->{\cellcolor{gray!50}}+1}
             \\ \hhline{---}
@@
             \hhline{---}
-            -1 & \onslide<+->{\only<.->{\cellcolor{gray!50}}-1} & \onslide<.(1)->{\only<.(1)->{\cellcolor{red!80!black!55}}-1}
+            -1 & \onslide<5->{\only<5->{\cellcolor{gray!50}}-1} & \onslide<6->{\only<6->{\cellcolor{red!80!black!55}}-1}
             \\ \hhline{---}
-            -1 & \only<.->{\cellcolor{gray!50}-1} & \only<.(1)->{\cellcolor{gray!50}+1}
+            -1 & \only<5->{\cellcolor{gray!50}-1} & \only<6->{\cellcolor{gray!50}+1}
             \\ \hhline{---}
-            -1 & \only<.->{\cellcolor{gray!50}-1} & \only<.(1)->{\cellcolor{gray!50}+1}
+            -1 & \only<5->{\cellcolor{gray!50}-1} & \only<6->{\cellcolor{gray!50}+1}
             \\ \hhline{---}
@@
   }
+
+  \only<8>{
+    \[\begin{aligned}
+        m_{0,0}\, m_{0,1}\, m_{0,2} &= +1 \\
+        m_{1,0}\, m_{1,1}\, m_{1,2} &= +1 \\
+        m_{2,0}\, m_{2,1}\, m_{2,2} &= +1 \\
+        m_{0,0}\, m_{1,0}\, m_{2,0} &= -1 \\
+        m_{0,1}\, m_{1,1}\, m_{2,1} &= -1 \\
+        m_{0,2}\, m_{1,2}\, m_{2,2} &= -1 \\
+        \midrule
+        +1 &= -1
+      \end{aligned}\]
+  }
 \end{frame}
+
+\begin{frame}{Estratégia Clássica (Probabilística)}
+  \begin{itemize}[<+->]
+  \item Alice e Bob jogam uma moeda para decidir o valor de cada célula
+
+  \item Isto é equivalente a cada um deles sortear uma
+    dentre todas as possíveis matrizes
+
+  \item A combinação das duas matrizes sorteadas é uma estratégia determinística
+
+  \item Ou seja, qualquer estratégia probabilística é limitada pela
+    melhor estratégia determinística. Logo, a chance de sucesso
+    clássico é no máximo \(\nicefrac{8}{9}\)
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Estratégia Quântica}
+  \begin{itemize}[<only@+-5>]
+  \item E se Alice e Bob puderem carregar qubits?
+
+  \item Existe uma estratégia quântica que os permite vencer qualquer
+    rodada
+
+  \item Alice e Bob compartilham qubits emaranhados (um par para cada rodada):
+    \[
+      \ket{\psi} = \frac{1}{2}\left(
+        \ket{00}_{A} \otimes \ket{00}_{B} + \ket{01}_{A} \otimes \ket{01}_{B} +
+        \ket{10}_{A} \otimes \ket{10}_{B} + \ket{11}_{A} \otimes \ket{11}_{B}
+      \right)
+    \]
+
+  \item Ao receber uma linha/coluna, eles medem seus qubits
+
+  \item  O resultado de cada medição é o valor de cada célula
+  \end{itemize}
+
+  \only<+->{
+    \renewcommand{\arraystretch}{2}
+    \centering
+    \[\begin{array}{|*{3}{>{\quad}c<{\quad}|}c}
+        \hhline{---~}
+        +I \otimes Z & +Z \otimes I & +Z \otimes Z & \onslide<.(1)->{\color{green!50!black}+I}
+        \\ \hhline{---~}
+        +X \otimes I & +I \otimes X & +X \otimes X & \onslide<.(1)->{\color{green!50!black}+I}
+        \\ \hhline{---~}
+        -X \otimes Z & -Z \otimes X & +Y \otimes Y & \onslide<.(1)->{\color{green!50!black}+I}
+        \\ \hhline{---~}
+        \multicolumn{1}{c}{\onslide<.(1)->{\color{red!50!black}-I}} &
+        \multicolumn{1}{c}{\onslide<.(1)->{\color{red!50!black}-I}} &
+        \multicolumn{1}{c}{\onslide<.(1)->{\color{red!50!black}-I}} &
+      \end{array}\]
+  }
+\end{frame}
+
+\begin{frame}{Exemplo 4}
+  \begin{enumerate}[<only@+->]
+  \item Alice recebe a linha 0 e mede seu segundo qubit com
+    \(Z\). Suponha que ela tenha observado \(+1\). Ela atribui \(+1\)
+    à primeira celula e o estado inicial \(\ket{\psi}\) colapsa para
+    \[
+      \ket{\psi_{A1}} = \frac{1}{\sqrt{2}} (\ket{0000} + \ket{1010})
+    \]
+  \item Em seguida, Alice mede seu primeiro qubit com \(Z\). Suponha que
+    ela tenha observado \(-1\). Ela atribui \(-1\) à segunda célula e o estado
+    colapsa para
+    \[
+      \ket{\psi_{A2}} = \ket{1010}
+    \]
+  \item Para a terceira célula, ela mede seus dois qubits com \(Z \otimes Z\).
+    O único resultado possível é \(-1\) e o estado não se altera:
+    \(
+      \ket{\psi_{A3}} = \ket{\psi_{A2}}.
+    \)
+  \end{enumerate}
+\end{frame}
+
+\begin{frame}{Exemplo 4}
+  \begin{enumerate}[<only@+->]
+  \item Suponha que Bob tenha recebido a coluna 1. Para a primeira
+    célula, ele mede seu primeiro qubit com \(Z\). Ele observa \(-1\) com
+    (igual Alice) com probabilidade 1, e
+    \[
+      \ket{\psi_{B1}} = \ket{\psi_{A3}} = \ket{1010}
+    \]
+
+  \item Em seguida, Bob mede seu segundo qubit com \(X\).
+    Suponha que ele observe \(+1\). Então, o estado colapsa para
+    \[
+      \ket{\psi_{B2}} = \frac{1}{\sqrt{2}} (\ket{1010} + \ket{1011})
+    \]
+
+  \item Para a terceira célula, ele mede ambos os qubits com
+    \(-Z \otimes X\).  O único resultado possível é \(+1\), o que
+    satisfaz a restrição sobre o produto da coluna.
+  \end{enumerate}
+\end{frame}
+
+\begin{frame}{Lema 1: Produto das Linhas e Colunas}
+  \begin{tcblemma}{}{msquare-quantum-prod}
+    Seja \(M_{i, j}\) o observável na célula \((i, j)\) da estratégia
+    quântica, segue que, para toda linha \(i\),
+    \(\prod_{j} \operatorname{Out}(M_{i, j}) = +1\), e, para toda
+    coluna \(j\), \(\prod_{i} \operatorname{Out}(M_{i, j}) = -1\).
+  \end{tcblemma}
+
+  \begin{itemize}[<+(1)->]
+  \item Note que, em qualquer linha e coluna, os três
+    observáveis comutam entre si.
+
+  \item Ou seja, é possível encontrar uma base de autovetores em comum, que
+    diagonaliza os três. Para toda linha \(i\) (equiv. coluna \(j\)),
+    \begin{align*}
+      M_{i,0} M_{i,1} M_{i,2} &= (P_{i} \Lambda_{i, 0}P^{-1}) (P_{i} \Lambda_{i, 1}P^{-1}) (P_{i} \Lambda_{i, 2}P_{i}^{-1}) \\
+      &= P_{i} (\Lambda_{i, 0} \Lambda_{i, 1} \Lambda_{i, 2})P_{i}^{-1} \\
+      &= P_{i} \Lambda_{i} P_{i}^{-1}
+    \end{align*}
+
+  \item Cada entrada de \(\Lambda_{i}\) é o produto dos autovalores p/ mesmo autovetor
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Lema 1: Produto das Linhas e Colunas}
+  \begin{itemize}[<+->]
+  \item Os autovalores são sempre \(+1\) e \(-1\)
+
+  \item Tem sempre dois autovetores em comum para cada autoespaço
+
+  \item O que isso significa é que a primeira medição de qualquer
+    linha/coluna resulta em um autovalor \(\lambda\) colapsa para uma
+    combinação de dois autovetores \(\ket{\lambda}_{0}\) e
+    \(\ket{\lambda}_{1}\)
+
+  \item A segunda medição, então, colapsa para \(\ket{\lambda}_{0}\)
+    ou \(\ket{\lambda_{1}}\), e fixa o estado.
+
+  \item Logo, as medições irão resultar nos autovalores correspondentes
+    a \(\ket{\lambda}_{0}\)  ou \(\ket{\lambda}_{1}\)
+
+  \item O produto das três medições é uma das entradas de \(\Lambda_{i}\)
+
+  \item Mas, para toda linha \(i\), temos
+    \(P_{i} \Lambda_{i} P_{i}^{-1} = I\). Logo, \(\Lambda_{i} = I\) e o
+    produto das três medições é \(+1\) sempre. Para toda coluna \(j\),
+    \(P_{j} \Lambda_{j} P_{j}^{-1} = -I\) e \(\Lambda_{j} = -I\)
+  \end{itemize}
+\end{frame}
+% \begin{center}
+    %   \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
+    %     \node (phantom) [
+    %     vertex, label=above right:{\phantom{\(-X \otimes Z\)}},
+    %     label=below right:{\phantom{\(-X \otimes Z\)}}
+    %     ] at (2, -4) {};
+
+    %     \node (00) [vertex, label=above left:{\(I \otimes Z\)},] at (-2, 0) {};
+    %     \node (01) [vertex, label=above left:{\(Z \otimes I\)}] at (0,  0) {};
+    %     \node (02) [vertex, label=above left:{\(Z \otimes X\)}] at (2,  0) {};
+
+    %     \node (10) [vertex, label=above left:{\(X \otimes I\)}] at (-2, -2) {};
+    %     \node (11) [vertex, label=above left:{\(I \otimes X\)}] at (0,  -2) {};
+    %     \node (12) [vertex, label=above left:{\(X \otimes X\)}] at (2,  -2) {};
+
+    %     \node (20) [vertex, label=above left:{\(-X \otimes Z\)}] at (-2, -4) {};
+    %     \node (21) [vertex, label=above left:{\(-Z \otimes X\)}] at (0,  -4) {};
+    %     \node (22) [vertex, label=above left:{\(Y \otimes Y\)}] at (2,  -4) {};
+
+    %     \only<.(1)->{\node (r0) [text=green!50!black!80] at (2.5, 0) {\(+I\)};}
+    %     \only<.(1)->{\node (r1) [text=green!50!black!80] at (2.5, -2) {\(+I\)};}
+    %     \only<.(1)->{\node (r2) [text=green!50!black!80] at (2.5, -4) {\(+I\)};}
+
+    %     \only<.(1)->{\node (c0) [text=red!50!black!80] at (-2, -4.5) {\(-I\)};}
+    %     \only<.(1)->{\node (c1) [text=red!50!black!80] at (0, -4.5) {\(-I\)};}
+    %     \only<.(1)->{\node (c2) [text=red!50!black!80] at (2, -4.5) {\(-I\)};}
+
+    %     \path[]
+    %     (00) edge (01) edge (10)
+    %     (01) edge (02) edge (11)
+    %     (02) edge (12)
+
+    %     (10) edge (11) edge (20)
+    %     (11) edge (12) edge (21)
+    %     (12) edge (22)
+
+    %     (20) edge (21)
+    %     (21) edge (22)
+    %     ;
+    %   \end{tikzpicture}
+    % \end{center}
 \end{document}

### 2023-06-30 paper/main.tex
paper => fix indices

@@
   state to a linear combination of the two shared eigenvectors
-  \(\ket{\lambda}_{1}\) and \(\ket{\lambda}_{2}\) in the
+  \(\ket{\lambda}_{0}\) and \(\ket{\lambda}_{1}\) in the
   \(\lambda\)-eigenspace. Then, the second measurement will collapse
-  the state to either \(\ket{\lambda}_{1}\) or \(\ket{\lambda}_{2}\),
+  the state to either \(\ket{\lambda}_{0}\) or \(\ket{\lambda}_{1}\),
   eigenvectors common to the three observables.  Consequently, the
@@
   the product of the three outcomes will be the product of the
-  eigenvalues associated with either \(\ket{\lambda}_{1}\) or
-  \(\ket{\lambda}_{2}\), which is one of the entries in the diagonal
+  eigenvalues associated with either \(\ket{\lambda}_{0}\) or
+  \(\ket{\lambda}_{1}\), which is one of the entries in the diagonal
   of \(\Lambda_{i}\). But, notice that
@@
       & \metercw[label style={inner sep=1pt}]{a_{1}}
-      & \targ{}
+      & \ctrl{1}
       &
-      & \targ{}
+      & \ctrl{1}
       &
@@
       & \metercw[label style={inner sep=1pt}]{a_{0}}
-      & \ctrl{-1}
+      & \targ{}
       & \metercw[label style={inner sep=1pt}]{a_{2}}
-      & \ctrl{-1}
+      & \targ{}
       &

### 2023-06-30 slides/main.tex
fix neq constraints
slide => lema 1 completo

@@
         \midrule
-        +1 &= -1
+        +1 &\neq -1
       \end{aligned}\]
@@
   \item Note que, em qualquer linha e coluna, os três
-    observáveis comutam entre si.
+    observáveis comutam entre si
 
@@
   \item O que isso significa é que a primeira medição de qualquer
-    linha/coluna resulta em um autovalor \(\lambda\) colapsa para uma
+    linha/coluna resulta em um autovalor \(\lambda\) e colapsa para uma
     combinação de dois autovetores \(\ket{\lambda}_{0}\) e
@@
   \item A segunda medição, então, colapsa para \(\ket{\lambda}_{0}\)
-    ou \(\ket{\lambda_{1}}\), e fixa o estado.
+    ou \(\ket{\lambda_{1}}\), e fixa o estado
 
@@
   \end{itemize}
+
+  \only<.->{\qed}
 \end{frame}
+
+\begin{frame}{Lema 1: Produto das Linhas e Colunas}
+  \begin{itemize}[<+->]
+  \item Para a primeira linha, os autovetores em comum são
+    \(\ket{00}, \ket{01}, \ket{10}\) e \(\ket{11}\)
+
+  \item Para a primeira célula \(I \otimes Z\), temos \(\ket{00}\) e
+    \(\ket{10}\) no autoespaço do \(+1\)
+
+  \item Ao observar \(+1\), o estado colapsa para uma combinação dos dois, vide Exemplo 4:
+    \[
+      \frac{1}{2} (\ket{0000} + \ket{0101} + \ket{1010} + \ket{1111})
+      \mapsto
+      \frac{1}{\sqrt{2}} (\ket{0000} + \ket{1010})
+    \]
+
+  \item Para a segunda célula \(Z \otimes I\), o autovalor de \(\ket{00}\) é
+    \(+1\) e o de \(\ket{10}\) é \(-1\)
+
+  \item Ao observar \(-1\), o estado colapsa para o autovetor \(\ket{10}\),
+    vide Exemplo 4:
+    \[
+      \frac{1}{\sqrt{2}} (\ket{0000} + \ket{1010})
+      \mapsto
+      \ket{1010}
+    \]  \end{itemize}
+\end{frame}
+
 % \begin{center}

### 2023-06-30 paper/main.tex
Paper => fix circuits

@@
       & \ctrl{1}
+      & \gate{Y}
       & \gate{S}
@@
       & \targ{}
+      & \gate{H}
       & \gate{S}

### 2023-06-30 slides/main.tex
slide => lema 2 (50%)

@@
 
+\begin{frame}{Lema 2: Interseção}
+  \begin{tcblemma}{}{msquare-quantum-inters}
+    Para qualquer linha \(i\) atribuída a Alice e
+    coluna \(j\) atribuída ao Bob, o valor assinalado
+    por ambos à célula \((i, j)\) é sempre o mesmo.
+  \end{tcblemma}
+
+  \begin{itemize}[<+(1)->]
+  \item Independente da linha atribuída a Alice, o estado final dos qubits dela
+    é sempre um dos autovetores em comum para aquela linha
+
+  \item Este estado é uma combinação de um dos autoespaços de
+    Bob na interseção
+
+  \item O estado inicial é simétrico e, a cada medição, a simetria se mantém
+  \end{itemize}
+\end{frame}
 % \begin{center}

### 2023-07-01 slides/main.tex
slides => Part 1, Magic Square

@@
   \item Uma estratégia determinística consiste em 
-    prepar matrizes pré-definidas
+    preparar matrizes pré-definidas
 
@@
   \item Suponha que Bob tenha recebido a coluna 1. Para a primeira
-    célula, ele mede seu primeiro qubit com \(Z\). Ele observa \(-1\) com
+    célula, ele mede seu primeiro qubit com \(Z\). Ele observa \(-1\)
     (igual Alice) com probabilidade 1, e
@@
   \item A segunda medição, então, colapsa para \(\ket{\lambda}_{0}\)
-    ou \(\ket{\lambda_{1}}\), e fixa o estado
+    ou \(\ket{\lambda}_{1}\), e fixa o estado
 
@@
 
-  \item Este estado é uma combinação de um dos autoespaços de
+  \item Se Alice repetir qualquer medição, o resultado é o mesmo que o anterior
+
+  \item Mas, este estado é uma combinação de um dos autoespaços de
     Bob na interseção
 
-  \item O estado inicial é simétrico e, a cada medição, a simetria se mantém
+  \item Além disso, o estado inicial é simétrico e, a cada medição, a simetria se mantém
+
+  \item Logo, se Bob mede os qubits dele com os mesmos observáveis que Alice, ele
+    observa o mesmo resultado
+  \end{itemize}
+
+  \only<.(1)->{\qed}
+\end{frame}
+
+\begin{frame}{Lema 2: Interseção}
+  \begin{itemize}[<+->]
+  \item Para a segunda linha, o estado de Alice colapsa para
+    \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} + \ket{11})\),
+    \((\nicefrac{1}{2}) (\ket{00} - \ket{01} + \ket{10} - \ket{11})\),
+    \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\) ou
+    \((\nicefrac{1}{2}) (\ket{00} + \ket{01} - \ket{10} - \ket{11})\)
+
+  \item Suponha que tenha sido \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} + \ket{11})\)
+
+  \item Então, Alice recebeu \(-1\), \(-1\) e \(+1\)
+
+  \item Após a primeira medição, o estado colapsa para
+    {
+      \small
+      \begin{align*}
+        &\frac{1}{2\sqrt{2}} \Bigl(
+          (\ket{00} - \ket{10}) \ket{00} +
+          (\ket{01} - \ket{11}) \ket{01} +
+          (\ket{10} - \ket{00}) \ket{10} +
+          (\ket{11} - \ket{01}) \ket{11}
+          \Bigr) \\
+        \equiv\;
+        & \frac{1}{2\sqrt{2}} \Bigl(
+          \ket{00} (\ket{00} - \ket{10}) +
+          \ket{01} (\ket{01} - \ket{11}) +
+          \ket{10} (\ket{10} - \ket{00}) +
+          \ket{11} (\ket{11} - \ket{01})
+          \Bigr)
+      \end{align*}
+    }
   \end{itemize}
 \end{frame}
+
+\begin{frame}{Lema 2: Interseção}
+  \begin{itemize}[<+->]
+  \item Após a segunda medição, o estado colapsa (e fixa) para
+    {
+      \small
+      \begin{alignat*}{2}
+        &\frac{1}{4} \Bigl(
+        &&(\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{00} -
+           (\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{01} - \nonumber \\
+        & &&(\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{10} +
+             (\ket{00} - \ket{01} - \ket{10} + \ket{11}) \ket{11}
+             \Bigr) \nonumber \\
+        \equiv\;
+        & \frac{1}{4} \Bigl(
+        &&\ket{00} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) -
+           \ket{01} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) - \nonumber \\
+        & &&\ket{10} (\ket{00} - \ket{01} - \ket{10} + \ket{11}) +
+             \ket{11} (\ket{00} - \ket{01} - \ket{10} + \ket{11})
+             \Bigr)
+      \end{alignat*}
+    }
+
+  \item Logo, para qualquer coluna que Bob receba, ao fazer uma
+    medição igual a que Alice fez na interseção, ele obterá a mesma
+    resposta que Alice
+  \end{itemize}
+\end{frame}
+
 % \begin{center}

### 2023-07-01 slides/main.tex
slides => arranjo e realização clássica

@@
 
-\newtcbtheorem{tcblemma}{Lema}{
+\newtcbtheorem{cbox}{}{
   boxrule=0.15mm,
@@
   % description delimiters={(}{). }
-}{lem}
+}{cbox}
 
@@
 
-  \item Alice e Bob compartilham qubits emaranhados (um par para cada rodada):
+  \item Alice e Bob compartilham qubits emaranhados
     \[
@@
 \begin{frame}{Lema 1: Produto das Linhas e Colunas}
-  \begin{tcblemma}{}{msquare-quantum-prod}
+  \begin{cbox}{}{msquare-quantum-prod}
     Seja \(M_{i, j}\) o observável na célula \((i, j)\) da estratégia
@@
     coluna \(j\), \(\prod_{i} \operatorname{Out}(M_{i, j}) = -1\).
-  \end{tcblemma}
+  \end{cbox}
 
@@
 \begin{frame}{Lema 2: Interseção}
-  \begin{tcblemma}{}{msquare-quantum-inters}
+  \begin{cbox}{}{msquare-quantum-inters}
     Para qualquer linha \(i\) atribuída a Alice e
@@
     por ambos à célula \((i, j)\) é sempre o mesmo.
-  \end{tcblemma}
+  \end{cbox}
 
@@
 
-% \begin{center}
-    %   \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
+\section{Caracterizando Jogos Mágicos}
+
+\begin{frame}{Modificando o Formato}
+  \begin{itemize} [<+->]
+  \item O que será que acontece se mudarmos o formato do jogo?
+  \item E se, ao invés de um quadrado, fosse um pentagrama?
+  \item<only@3-> Note que a representação foi em formato de grafo
+  \item<only@4-> Podemos redesenhar o quadrado mágico como um grafo também
+  \item<only@6-> Será que existe alguma caracterização deste tipo de jogo?
+  \end{itemize}
+
+  \only<2>{
+    \vfill{}
+    \begin{center}
+      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
+        % Triângulo de cima
+        \node (0) [vertex] at (0, +1) {};
+        \node (1) [vertex] at (-0.9, -1) {};
+        \node (2) [vertex] at (+0.9, -1) {};
+        \node (label0) [text=red!50!black!80] at (0, -1.25) {\(-I\)};
+
+        % Triângulo da esquerda
+        \node (3) [vertex] at (-2.75, -1) {};
+        \node (4) [vertex] at (-1.3, -2) {};
+        \node (label1) [text=green!50!black!80] at (-0.8, -1.5) {\(+I\)};
+
+        % Triângulo da direita
+        \node (5) [vertex] at (+2.75, -1) {};
+        \node (6) [vertex] at (+1.3, -2) {};
+        \node (label1) [text=green!50!black!80] at (+0.8, -1.5) {\(+I\)};
+
+        % Fechar pentágono
+        \node (7) [vertex] at (0, -2.75) {};
+        \node (label2) [text=green!50!black!80] at (+0.5, -2.1) {\(+I\)};
+        \node (label3) [text=green!50!black!80] at (-0.5, -2.1) {\(+I\)};
+
+        % Triângulo baixo esquerda
+        \node (8) [vertex] at (-1.9, -3.5) {};
+
+        % Triângulo baixo direita
+        \node (9) [vertex] at (+1.9, -3.5) {};
+
+        \path[]
+        (0) edge (1) edge (2)
+        (1) edge (2) edge (3) edge (4)
+        (2) edge (5) edge (6)
+        (3) edge (4)
+        (4) edge (7) edge (8)
+        (5) edge (6)
+        (6) edge (7) edge (9)
+        (7) edge (8) edge (9)
+        ;
+      \end{tikzpicture}
+    \end{center}
+    \vfill{}
+  }
+
+  \only<5>{
+    \vfill{}
+    \begin{center}
+      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
         % \node (phantom) [
-    %     vertex, label=above right:{\phantom{\(-X \otimes Z\)}},
+        % label=above right:{\phantom{\(-X \otimes Z\)}},
         % label=below right:{\phantom{\(-X \otimes Z\)}}
-    %     ] at (2, -4) {};
+        % ] at (1.5, -3) {};
 
-    %     \node (00) [vertex, label=above left:{\(I \otimes Z\)},] at (-2, 0) {};
-    %     \node (01) [vertex, label=above left:{\(Z \otimes I\)}] at (0,  0) {};
-    %     \node (02) [vertex, label=above left:{\(Z \otimes X\)}] at (2,  0) {};
+        \node (00) [vertex,
+        % label=above left:{\(I \otimes Z\)}
+        ] at (-1.25, 0) {};
+        \node (01) [vertex,
+        % label=above left:{\(Z \otimes I\)}
+        ] at (0,  0) {};
+        \node (02) [vertex,
+        % label=above left:{\(Z \otimes X\)}
+        ] at (1.25,  0) {};
 
-    %     \node (10) [vertex, label=above left:{\(X \otimes I\)}] at (-2, -2) {};
-    %     \node (11) [vertex, label=above left:{\(I \otimes X\)}] at (0,  -2) {};
-    %     \node (12) [vertex, label=above left:{\(X \otimes X\)}] at (2,  -2) {};
+        \node (10) [vertex,
+        % label=above left:{\(X \otimes I\)}
+        ] at (-1.25, -1.25) {};
+        \node (11) [vertex,
+        % label=above left:{\(I \otimes X\)}
+        ] at (0,  -1.25) {};
+        \node (12) [vertex,
+        % label=above left:{\(X \otimes X\)}
+        ] at (1.25,  -1.25) {};
 
-    %     \node (20) [vertex, label=above left:{\(-X \otimes Z\)}] at (-2, -4) {};
-    %     \node (21) [vertex, label=above left:{\(-Z \otimes X\)}] at (0,  -4) {};
-    %     \node (22) [vertex, label=above left:{\(Y \otimes Y\)}] at (2,  -4) {};
+        \node (20) [vertex,
+        % label=above left:{\(-X \otimes Z\)}
+        ] at (-1.25, -2.5) {};
+        \node (21) [vertex,
+        % label=above left:{\(-Z \otimes X\)}
+        ] at (0,  -2.5) {};
+        \node (22) [vertex,
+        % label=above left:{\(Y \otimes Y\)}
+        ] at (1.25, -2.5) {};
 
-    %     \only<.(1)->{\node (r0) [text=green!50!black!80] at (2.5, 0) {\(+I\)};}
-    %     \only<.(1)->{\node (r1) [text=green!50!black!80] at (2.5, -2) {\(+I\)};}
-    %     \only<.(1)->{\node (r2) [text=green!50!black!80] at (2.5, -4) {\(+I\)};}
+        \only<.(1)->{\node (r0) [text=green!50!black!80] at (1.65, -0.05) {\(+I\)};}
+        \only<.(1)->{\node (r1) [text=green!50!black!80] at (1.65, -1.20) {\(+I\)};}
+        \only<.(1)->{\node (r2) [text=green!50!black!80] at (1.65, -2.45) {\(+I\)};}
 
-    %     \only<.(1)->{\node (c0) [text=red!50!black!80] at (-2, -4.5) {\(-I\)};}
-    %     \only<.(1)->{\node (c1) [text=red!50!black!80] at (0, -4.5) {\(-I\)};}
-    %     \only<.(1)->{\node (c2) [text=red!50!black!80] at (2, -4.5) {\(-I\)};}
+        \only<.(1)->{\node (c0) [text=red!50!black!80] at (-1.2, -2.8) {\(-I\)};}
+        \only<.(1)->{\node (c1) [text=red!50!black!80] at (-0.05, -2.8) {\(-I\)};}
+        \only<.(1)->{\node (c2) [text=red!50!black!80] at (1.2, -2.8) {\(-I\)};}
 
-    %     \path[]
-    %     (00) edge (01) edge (10)
-    %     (01) edge (02) edge (11)
-    %     (02) edge (12)
+        \path[]
+        (00) edge (01) edge (10)
+        (01) edge (02) edge (11)
+        (02) edge (12)
 
-    %     (10) edge (11) edge (20)
-    %     (11) edge (12) edge (21)
-    %     (12) edge (22)
+        (10) edge (11) edge (20)
+        (11) edge (12) edge (21)
+        (12) edge (22)
 
-    %     (20) edge (21)
-    %     (21) edge (22)
-    %     ;
-    %   \end{tikzpicture}
-    % \end{center}
+        (20) edge (21)
+        (21) edge (22)
+        ;
+      \end{tikzpicture}
+    \end{center}
+    \vfill{}
+  }
+\end{frame}
+
+\begin{frame}{Definição 1 (Arranjo)}
+  \begin{cbox}{}{arranjo}
+    Um arranjo \(A = (V, E, \ell)\) é um hipergrafo conexo tal que
+    cada vértice do conjunto \(V\) está exatamente em duas
+    hiperarestas do conjunto \(E\) (\emph{conexo} significa que o
+    hipergrafo não pode ser dividido em dois sub-hipergrafos
+    disjuntos). O arranjo também inclui uma rotulação
+    \(\ell\colon E \mapsto \{+1, -1\}\). 
+  \end{cbox}
+
+  \stepcounter{beamerpauses}
+  \begin{itemize}[<+->]
+  \item O quadrado mágico e o pentagrama são exemplos de arranjos
+  \item Cada linha que passa por 3 vértices do quadrado é uma hiperaresta
+  \item Cada linha que passa por 4 vértices do pentragrama é uma hiperaresta
+  \end{itemize}
+\end{frame}
+\begin{frame}{Definição 2 (Realização Clássica)}
+  \begin{cbox}{}{real-class}
+    Uma realização clássica de um arranjo \(A = (V, E, \ell)\) é
+    uma rotulação dos vértices \(c\colon V \mapsto \{+1, -1\}\)
+    tal que, para cada \(e \in E\),
+    % o produto dos rótulos de cada vértice em uma hiperaresta
+    % é igual ao rótulo daquela hiperaresta:
+    \(
+      \prod_{v \in e} c(v) = \ell(e).
+      % , \text{ para cada } e \in E.
+    \)
+  \end{cbox}
+
+  \stepcounter{beamerpauses}
+  \begin{itemize}[<+->]
+  \item Por exemplo, considere uma versão \(2 \times 2\) do quadrado mágico, com
+    \begin{align*}
+      \ell(e_{t}) = \ell(e_{r}) &= +1 \text{ e } \\
+      \ell(e_{b}) = \ell(e_{l}) &= -1 
+    \end{align*}
+
+  \item Uma realização clássica válida é
+    \begin{align*}
+      c(v_{00}) &= c(v_{01}) = c(v_{11}) = +1 \text{ e} \\
+      c(v_{10}) &= -1
+    \end{align*}
+  \end{itemize}
+
+  \onslide<2->{
+    \begin{center}
+      \begin{tikzpicture}[
+        overlay, xshift=5.5cm, yshift=3.5cm,
+        vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}
+        ]
+        \node (00) [vertex] at (0, 0) {};
+        \node (01) [vertex] at (1, 0) {};
+        \node (10) [vertex] at (0, -1) {};
+        \node (11) [vertex] at (1, -1) {};
+
+        \node (et) [text=green!50!black!80] at (1.35, 0) {\(+1\)};
+        \node (et) [text=green!50!black!80] at (0.9, -1.35) {\(+1\)};
+        \node (et) [text=red!50!black!80] at (1.35, -0.9) {\(-1\)};
+        \node (et) [text=red!50!black!80] at (-0.1, -1.35) {\(-1\)};
+
+        \path[]
+        (00) edge (01) edge (10)
+        (01) edge (11)
+        (10) edge (11)
+        ;
+      \end{tikzpicture}
+    \end{center}
+  }
+\end{frame}
+
 \end{document}

### 2023-07-01 slides/main.tex
slides => up to parity

@@
 \end{frame}
+
 \begin{frame}{Definição 2 (Realização Clássica)}
@@
       \begin{tikzpicture}[
-        overlay, xshift=5.5cm, yshift=3.5cm,
+        overlay, xshift=5cm, yshift=3.5cm,
         vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}
@@
 
+\begin{frame}{Definição 3 (Realização Quântica)}
+  \begin{cbox}{}{real-quant}
+    Uma realização quântica de um arranjo \(A = (V, E, \ell)\) é
+    uma rotulação de vértices
+    \(c\colon V \mapsto \operatorname{GL}(\mathcal{H})\), que
+    mapeia cada vértice para um observável \(M\), tal que
+
+    \begin{itemize}[<+(1)->]
+    \color{red!40!black}
+    \item \(M = M^{*}\) e \(M^{2} = I\), ou equivalentemente,
+      \(M\) possui autovalores \(+1\) e \(-1\)
+
+    \item Observáveis assinalados aos vértices de uma hiperaresta
+      comutam entre si
+
+    \item Para cada hiperaresta \(e \in E\), \(\prod_{v \in e} c(v) = \ell(e) I\)
+    \end{itemize}
+  \end{cbox}
+
+  \begin{itemize}[<+(1)->]
+  \item Uma realização clássica é simplesmente uma realização quântica com \(\mathcal{H} = \mathbb{R}\)
+
+  \item A solução que vimos para o jogo do quadrado mágico é uma realização quântica
+
+  \item Se existe uma realização quântica em que todos os observáveis
+    comutam, então existe uma realização clássica
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Definição 3 (Paridade)}
+  \begin{cbox}{}{parity}
+    A paridade \(p(\ell)\) de uma rotulação \(\ell\) de um arranjo \(A = (V, E, \ell)\) é
+    \[
+      p(\ell) = \prod_{e \in E} \ell(E).
+    \]
+  \end{cbox}
+
+  \begin{itemize}[<+->]
+  \item A paridade é \(-1\) se o número de rótulos \(-1\) é ímpar ou \(-1\) caso contrário
+
+  \item A realização de um arranjo \(A = (V, E, \ell)\) depende apenas
+    de \(p(\ell)\).  Isto é, para um outro arranjo
+    \(A' = (V, E, \ell')\), se \(p(\ell) = p(\ell')\), é possível
+    construir uma realização para \(A'\) a partir da realização de
+    \(A\)
+
+  \item Um arranjo \(A = (V, E, \ell)\) é realizável classicamente se, e somente se,
+    \(p(\ell) = +1\)
+  \end{itemize}
+\end{frame}
+
 \end{document}

### 2023-07-02 slides/main.tex
slides => up to intersection graph

@@
 \date{03/07/2023}
-\title[Pseudotelepatia Quântica]{Pseudotelepatia Quântica (TODO)}
+\title[Pseudotelepatia Quântica]{Jogos Mágicos}
 
@@
 
+\begin{frame}{Teorema 1: O Jogo do Quadrado Mágico É Vencível}
+  \begin{cbox}{}{thm:msquare}
+    Existe uma estratégia quântica para o jogo do quadrado mágico de Mermin-Peres,
+    que consiste em Alice e Bob compartilharem qubits emaranhados \emph{antes} do
+    início do jogo, que vence sistematicamente todos as rodadas.
+  \end{cbox}
+\end{frame}
+
 \section{Caracterizando Jogos Mágicos}
@@
 
-  \begin{itemize}[<+->]
+  \begin{itemize}[<+(1)->]
   \item A paridade é \(-1\) se o número de rótulos \(-1\) é ímpar ou \(-1\) caso contrário
@@
 
+\begin{frame}{Definição 4 (Arranjo Mágico)}
+  \begin{cbox}{}{magic-arrang}
+    Um arranjo \(A = (V, E, \ell)\) é mágico se 
+    \(p(\ell) = -1\) e é realizável quanticamente.
+  \end{cbox}
+
+  \begin{itemize}[<+(1)->]
+  \item Arranjos mágicos não são realizáveis classicamente
+  \item O quadrado \(3 \times 3\) e o pentagrama são arranjos mágicos
+  \item O quadrado \(2 \times 2\), com \(p(\ell) = -1\),
+    não é realizável de nenhuma forma
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Definição 5 (Jogos de Paridade Pseudotelepáticos)}
+  \begin{cbox}{}{parity}
+    Um jogo de paridade pseudotelepático em um arranjo
+    \(A = (V, E, \ell)\) é um jogo cooperativo de dois jogadores
+    (Alice e Bob) e um árbitro (Charlie). Alice e Bob podem se
+    comunicar antes do jogo, mas não após o início. A cada rodada,
+
+    \begin{enumerate}[<+(1)->]
+    \color{red!40!black}
+    \item Charlie seleciona \(u \in V\) e uma das duas
+      hiperarestas \(e\) que contém \(u\)
+
+    \item Charlie envia \(u\) para Alice e \(e\) para Bob
+
+    \item Alice rotula \(a(u) = \pm{}1\) e envia para Charlie
+
+    \item Bob rotula cada vértice \(v \in e\) com \(b(v) = \pm{}1\) e envia para Charlie
+
+    \item Alice e Bob vencem se \(a(u) = b(u)\) e \(\prod_{v \in e} b(v) = \ell(e)\)
+    \end{enumerate}
+  \end{cbox}
+\end{frame}
+
+\begin{frame}{Teorema 2 (Existência de Estratégia Vencedora)}
+  \begin{cbox}{}{parity}
+    Em qualquer arranjo que possui uma realização quântica em que
+    todos os observáveis possuem autovalores reais, se Alice e Bob
+    podem compartilhar emaranhamento, então existe uma estratégia
+    vencedora.
+  \end{cbox}
+
+  \begin{itemize}[<+(1)->]
+  \item Seja \(c\) a realização quântica em um espaço \(\mathcal{H}\) de
+    dimensão \(n\)
+
+  \item Para uma base \ket{1}, \ldots, \ket{n}, Alice e Bob compartilham o estado
+    \[
+      \ket{\psi}_{AB} = \sum_{i = 1}^{n} \ket{i} \ket{i}
+    \]
+
+  \item A prova segue pela diagonalização simultânea dos observáveis e simetria
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Definição 6 (Grafo de Interseção)}
+  \begin{cbox}{}{intersection-graph}
+    O grafo de interseção de um arranjo \(A = (V, E, \ell)\) é o grafo
+    não-direcionado \(G = (V', E', \ell')\) tal que \(V' = E\) e
+    existe uma aresta entre \(e_{0}, e_{1} \in V'\) para cada vértice
+    na interseção \(e_{0} \cap e_{1}\) das hiperarestas. A rotulação
+    \(\ell'\colon V' \mapsto \{+1, -1\}\) é a mesma do arranjo \(A\),
+    isto é, \(\ell(e) = \ell'(e)\).
+  \end{cbox}
+
+  \begin{itemize}[<+(1)->]
+  \item O grafo de interseção do quadrado \(3 \times 3\) é o \(K_{3, 3}\)
+
+  \item O grafo de interseção do pentagrama é o \(K_{5}\)
+  \end{itemize}
+\end{frame}
+
 \end{document}

### 2023-07-02 slides/main.tex
slides 100%

@@
 \usepackage{tikz}
+\usetikzlibrary{intersections}
+\usetikzlibrary{calc}
 \usetikzlibrary{quantikz2}
@@
   Luigi Soares (\email{luigi.domenico@dcc.ufmg.br}) \\
-  Roberto Rosmaninho (\email{TODO})}
+  Roberto Rosmaninho (\email{robertogomes@dcc.ufmg.br})}
 \institute[DCC/UFMG]{}
 \date{03/07/2023}
-\title[Pseudotelepatia Quântica]{Jogos Mágicos}
+\title[Jogos Mágicos]{Jogos Mágicos}
 
@@
 \begin{frame}{Exemplo 4}
-  \begin{enumerate}[<only@+->]
-  \item Alice recebe a linha 0 e mede seu segundo qubit com
+  \begin{enumerate}
+  \item<only@1-3> Alice recebe a linha 0 e mede seu segundo qubit com
     \(Z\). Suponha que ela tenha observado \(+1\). Ela atribui \(+1\)
@@
     \]
-  \item Em seguida, Alice mede seu primeiro qubit com \(Z\). Suponha que
+  \item<only@2-3> Em seguida, Alice mede seu primeiro qubit com \(Z\). Suponha que
     ela tenha observado \(-1\). Ela atribui \(-1\) à segunda célula e o estado
@@
     \]
-  \item Para a terceira célula, ela mede seus dois qubits com \(Z \otimes Z\).
+  \item<only@3> Para a terceira célula, ela mede seus dois qubits com \(Z \otimes Z\).
     O único resultado possível é \(-1\) e o estado não se altera:
@@
     \)
-  \end{enumerate}
-\end{frame}
 
-\begin{frame}{Exemplo 4}
-  \begin{enumerate}[<only@+->]
-  \item Suponha que Bob tenha recebido a coluna 1. Para a primeira
+  \item<only@4-> Suponha que Bob tenha recebido a coluna 1. Para a primeira
     célula, ele mede seu primeiro qubit com \(Z\). Ele observa \(-1\)
@@
 
-  \item Em seguida, Bob mede seu segundo qubit com \(X\).
+  \item<only@5-> Em seguida, Bob mede seu segundo qubit com \(X\).
     Suponha que ele observe \(+1\). Então, o estado colapsa para
@@
 
-  \item Para a terceira célula, ele mede ambos os qubits com
+  \item<only@6-> Para a terceira célula, ele mede ambos os qubits com
     \(-Z \otimes X\).  O único resultado possível é \(+1\), o que
@@
       \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
-        % Triângulo de cima
-        \node (0) [vertex] at (0, +1) {};
-        \node (1) [vertex] at (-0.9, -1) {};
-        \node (2) [vertex] at (+0.9, -1) {};
-        \node (label0) [text=red!50!black!80] at (0, -1.25) {\(-I\)};
+        \foreach \c [evaluate=\c as \ang using {18 + 72*\c}] in {0, 1, 2, 3, 4} {
+          \node [vertex] (\c) at (\ang:25mm) {};
+        }
 
-        % Triângulo da esquerda
-        \node (3) [vertex] at (-2.75, -1) {};
-        \node (4) [vertex] at (-1.3, -2) {};
-        \node (label1) [text=green!50!black!80] at (-0.8, -1.5) {\(+I\)};
+        \draw [name path=0--2] (0) -- (2);
+        \draw [name path=0--3] (0) -- (3);
+        \draw [name path=1--3] (1) -- (3);
+        \draw [name path=1--4] (1) -- (4);
+        \draw [name path=2--4] (2) -- (4);
 
-        % Triângulo da direita
-        \node (5) [vertex] at (+2.75, -1) {};
-        \node (6) [vertex] at (+1.3, -2) {};
-        \node (label1) [text=green!50!black!80] at (+0.8, -1.5) {\(+I\)};
+        \node [vertex] (01) at (intersection of 0--2 and 1--4) {};
+        \node [vertex] (04) at (intersection of 0--3 and 1--4) {};
+        \node [vertex] (12) at (intersection of 1--3 and 0--2) {};
+        \node [vertex] (23) at (intersection of 1--3 and 2--4) {};
+        \node [vertex] (34) at (intersection of 0--3 and 2--4) {};
 
-        % Fechar pentágono
-        \node (7) [vertex] at (0, -2.75) {};
-        \node (label2) [text=green!50!black!80] at (+0.5, -2.1) {\(+I\)};
-        \node (label3) [text=green!50!black!80] at (-0.5, -2.1) {\(+I\)};
+        \node [text=red!50!black!80] (label0--2) at ($(01)!0.5!(12) - (0, 0.25)$) {\(-I\)};
+        \node [text=green!50!black!80] (label1--4) at ($(01)!0.5!(04) + (-0.3, -0.1)$) {\(+I\)};
+        \node [text=green!50!black!80] (label0--3) at ($(04)!0.5!(34) + (-0.1, 0.25)$) {\(+I\)};
+        \node [text=green!50!black!80] (label2--4) at ($(23)!0.5!(34) + (+0.1, 0.25)$) {\(+I\)};
+        \node [text=green!50!black!80] (label1--3) at ($(12)!0.5!(23) + (+0.3, -0.1)$) {\(+I\)};
 
-        % Triângulo baixo esquerda
-        \node (8) [vertex] at (-1.9, -3.5) {};
+        % (intersection cs:first line={(0) -- (2)}, second line={(1) -- (4)})
+        % \node [vertex] (01) {}
+        % (0) edge (2) edge (3)
+        % (1) edge (3) edge (4)
+        % (2) edge (4)
+        % ;
+        % % Triângulo de cima
+        % \node (0) [vertex] at (0, +1) {};
+        % \node (1) [vertex] at (-0.9, -1) {};
+        % \node (2) [vertex] at (+0.9, -1) {};
+        % \node (label0) [text=red!50!black!80] at (0, -1.25) {\(-I\)};
 
-        % Triângulo baixo direita
-        \node (9) [vertex] at (+1.9, -3.5) {};
+        % % Triângulo da esquerda
+        % \node (3) [vertex] at (-2.75, -1) {};
+        % \node (4) [vertex] at (-1.3, -2) {};
+        % \node (label1) [text=green!50!black!80] at (-0.8, -1.5) {\(+I\)};
 
-        \path[]
-        (0) edge (1) edge (2)
-        (1) edge (2) edge (3) edge (4)
-        (2) edge (5) edge (6)
-        (3) edge (4)
-        (4) edge (7) edge (8)
-        (5) edge (6)
-        (6) edge (7) edge (9)
-        (7) edge (8) edge (9)
-        ;
+        % % Triângulo da direita
+        % \node (5) [vertex] at (+2.75, -1) {};
+        % \node (6) [vertex] at (+1.3, -2) {};
+        % \node (label1) [text=green!50!black!80] at (+0.8, -1.5) {\(+I\)};
+
+        % % Fechar pentágono
+        % \node (7) [vertex] at (0, -2.75) {};
+        % \node (label2) [text=green!50!black!80] at (+0.5, -2.1) {\(+I\)};
+        % \node (label3) [text=green!50!black!80] at (-0.5, -2.1) {\(+I\)};
+
+        % % Triângulo baixo esquerda
+        % \node (8) [vertex] at (-1.9, -3.5) {};
+
+        % % Triângulo baixo direita
+        % \node (9) [vertex] at (+1.9, -3.5) {};
+
+        % \path[]
+        % (0) edge (1) edge (2)
+        % (1) edge (2) edge (3) edge (4)
+        % (2) edge (5) edge (6)
+        % (3) edge (4)
+        % (4) edge (7) edge (8)
+        % (5) edge (6)
+        % (6) edge (7) edge (9)
+        % (7) edge (8) edge (9)
+        % ;
       \end{tikzpicture}
@@
   \begin{itemize}[<+(1)->]
-  \item A paridade é \(-1\) se o número de rótulos \(-1\) é ímpar ou \(-1\) caso contrário
+  \item A paridade é \(-1\) se o número de rótulos \(-1\) é ímpar ou \(+1\) caso contrário
 
@@
     O grafo de interseção de um arranjo \(A = (V, E, \ell)\) é o grafo
-    não-direcionado \(G = (V', E', \ell')\) tal que \(V' = E\) e
+    não-direcionado \(G = (V', E')\) tal que \(V' = E\) e
     existe uma aresta entre \(e_{0}, e_{1} \in V'\) para cada vértice
-    na interseção \(e_{0} \cap e_{1}\) das hiperarestas. A rotulação
-    \(\ell'\colon V' \mapsto \{+1, -1\}\) é a mesma do arranjo \(A\),
-    isto é, \(\ell(e) = \ell'(e)\).
+    na interseção \(e_{0} \cap e_{1}\) das hiperarestas.
+    % A rotulação
+    % \(\ell'\colon V' \mapsto \{+1, -1\}\) é a mesma do arranjo \(A\),
+    % isto é, \(\ell(e) = \ell'(e)\).
   \end{cbox}
@@
 
+\begin{frame}{Teorema 3 (Caracterização por Grafo Planar)}
+  \begin{cbox}{}{main-result}
+    Um arranjo é magico se, e somente se, o seu grafo de interseção
+    não é planar.
+  \end{cbox}
+
+  \begin{itemize}[<+(1)->]
+  \item Grafo de interseção planar \(\implies\) arranjo não mágico:
+    \begin{itemize}
+    \item O objetivo é mostrar que, se o grafo de interseção é planar, a paridade é \(+1\)
+
+    \item A estratégia é contrair arestas do grafo de interseção e mostrar propriedades
+
+    \item Contrair uma aresta é unir os dois vértices \(v\) e \(w\) em cada ponta
+
+    \item As arestas que apontavam para \(v\) e \(w\), apontam para o novo vértice \(u\)
+
+    \item A aresta \emph{entre} \(v\) e \(w\) se torna dois laços
+
+    \item Propriedade 1: o grafo, após a contração da aresta, continua planar
+
+    \item Propriedade 2: a paridade (produto dos rótulos dos vértices) continua a mesma
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Teorema 3 (Caracterização por Grafo Planar)}
+  \begin{itemize}[<+->]
+  \item Propriedade 3: o produto dos observáveis nas arestas ao redor
+    do vértice, em sentido anti-horário, é igual a identidade
+    multiplicada pelo signal do vértice
+
+    \begin{itemize}
+    \item Se \(M_{1} \ldots M_{n} = I\), com \(M^{2} = I\)
+      (similar para \(-I\)), então, para qualquer ponto de início \(k\),
+      \(M_{k}M_{k + 1} \ldots M_{n} M_{1} \ldots M_{k-1} = I\), pois
+      \begin{align*}
+        M_{k} M_{k + 1} \ldots M_{n} M_{1} M_{k - 1}
+        &= (M_{k - 1} \ldots M_{1})(M_{1} \ldots M_{n}) (M_{1} \ldots M_{k - 1}) \\
+        &= (M_{k - 1} \ldots M_{1}) I (M_{1} \ldots M_{k - 1}) = I
+      \end{align*}
+
+    \item Seja \(X\) o observável na aresta a ser contraída, \(M_{1}, \ldots, M_{m} X\)  os observáveis ao
+      redor de \(v\) e \(X N_{1}, \ldots, N_{n}\) os observáveis ao redor de \(w\). Temos
+      \[
+        M_{1} \ldots M_{m} X = \ell(v) I \text{ e } X N_{1} \ldots N_{n} = \ell(w) I
+      \]
+
+    \item Multiplicando, temos \(M_{1}\ldots M_{m} N_{1} \ldots N_{n} = \ell(v)\ell(w) I = \ell(u) I\)
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Teorema 3 (Caracterização por Grafo Planar)}
+  \begin{itemize}[<+->]
+  \item Eventualmente, o grafo vai ser reduzido a um único vértice, com vários laços
+
+  \item O rótulo deste vértice é o produto dos rótulos dos vértices originais, i.e.\
+    a paridade
+
+  \item Cada laço contribui com \(+I\). Logo, o rótulo do vértice final é \(+1\)
+
+  \item Consequentemente, a paridade do arranjo é \(+1\) e ele não é mágico
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Teorema 3 (Caracterização por Grafo Planar)}
+  \begin{itemize}[<+->]
+  \item Grafo de interseção não-planar \(\implies\) arranjo mágico
+    \begin{itemize}
+    \item A estratégia é mostrar que se o grafo de interseção \(G\)
+      contém um grafo de interseção mágico \(H\) como um
+      menor topológico, então \(G\) é mágico
+
+    \item Qualquer grafo não-planar contém o grafo \(K_{3, 3}\) ou
+      o \(K_{5}\) como um menor topológico (Pontyagin e Kuratowski)
+
+    \item Tanto o \(K_{3, 3}\) (quadrado \(3 \times 3\))
+      quanto o \(K_{5}\) (pentagrama) são mágicos
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Definição 7 (Menor Topológico)}
+  \begin{cbox}{}{top-minor}
+    Um grafo \(H\) é um menor topológico de \(G\) se \(G\) contém um
+    subgrafo isomórfico a uma subdivisão de \(H\). Equivalentemente,
+    existe um mapeamento \(\phi\) injetivo de cada vértice \(v \in H\)
+    para um vértice \(\phi(v) \in G\), e de cada aresta
+    \((u, v) \in H\) para um caminho simples entre
+    \(\phi(u) e \phi(v)\) em \(G\), tal que os caminhos são disjuntos
+    (com exceção das extremidades \(u\) e \(v\)).
+  \end{cbox}
+\end{frame}
+
+\begin{frame}{Teorema 3 (Caracterização por Grafo Planar)}
+  \begin{itemize}[<+->]
+  \item Vamos construir uma realização quântica de \(G\) a partir da
+    realização de \(H\)
+
+    \begin{enumerate}
+    \item Para cada \(v \in H\), assuma
+      \(\ell_{G}(\phi(v)) = \ell_{H}(v)\)
+
+    \item Assuma que os vértices restantes de \(G\) são rotulados com \(+1\)
+
+    \item Para cada aresta \(e \in H\) tal que \(c_{H}(e) = M\), rotule
+      cada aresta \(e_{i}\) no caminho correspondente em \(G\) com o mesmo
+      observável \(M\); i.e.\ \(c_{G}(e_{i}) = c_{H}(e)\)
+
+    \item Rotule as demais arestas de \(G\) com \(+I\)
+    \end{enumerate}
+
+  \item Cada medição \(M\) em \(G\) ou está em \(H\) ou \(M = I\)
+    \(\implies M = M^{*}\) e \(M^{2} = M\)
+
+  \item Cada vértice de \(\phi(v) \in G\) toca os mesmo observáveis tocados
+    por \(v \in H\), mais \(I\)'s \(\implies\) os observáveis
+    comutam e multiplicam para \(\ell_{H}(v) I = \ell_{G}(\phi(v)) I\)
+
+  \item Cada vértice de \(G\) em um caminho entre \(\phi(u)\) e \(\phi(v)\)
+    toca dois vértices rotulados com o mesmo observável, e cópias de \(I\)
+    \(\implies\) comutam e multiplicam para \(+I\)
+
+  \item Os vértices restantes tocam apenas \(I\)'s \(\implies\)
+    comutam e multiplicam para \(+I\)
+ \end{itemize}
+  \qed
+\end{frame}
+
 \end{document}

### 2023-07-02 slides/main.tex
slides => fix labels
slides => fix def number
slides => fix typos

@@
 \date{03/07/2023}
-\title[Jogos Mágicos]{Jogos Mágicos}
+\title[Jogos Mágicos Quânticos]{Jogos Mágicos Quânticos}
 
@@
 
-        \node [text=red!50!black!80] (label0--2) at ($(01)!0.5!(12) - (0, 0.25)$) {\(-I\)};
-        \node [text=green!50!black!80] (label1--4) at ($(01)!0.5!(04) + (-0.3, -0.1)$) {\(+I\)};
-        \node [text=green!50!black!80] (label0--3) at ($(04)!0.5!(34) + (-0.1, 0.25)$) {\(+I\)};
-        \node [text=green!50!black!80] (label2--4) at ($(23)!0.5!(34) + (+0.1, 0.25)$) {\(+I\)};
-        \node [text=green!50!black!80] (label1--3) at ($(12)!0.5!(23) + (+0.3, -0.1)$) {\(+I\)};
+        \node [text=red!50!black!80] (label0--2) at ($(01)!0.5!(12) - (0, 0.25)$) {\(-1\)};
+        \node [text=green!50!black!80] (label1--4) at ($(01)!0.5!(04) + (-0.3, -0.1)$) {\(+1\)};
+        \node [text=green!50!black!80] (label0--3) at ($(04)!0.5!(34) + (-0.1, 0.25)$) {\(+1\)};
+        \node [text=green!50!black!80] (label2--4) at ($(23)!0.5!(34) + (+0.1, 0.25)$) {\(+1\)};
+        \node [text=green!50!black!80] (label1--3) at ($(12)!0.5!(23) + (+0.3, -0.1)$) {\(+1\)};
 
@@
 
-        \only<.(1)->{\node (r0) [text=green!50!black!80] at (1.65, -0.05) {\(+I\)};}
-        \only<.(1)->{\node (r1) [text=green!50!black!80] at (1.65, -1.20) {\(+I\)};}
-        \only<.(1)->{\node (r2) [text=green!50!black!80] at (1.65, -2.45) {\(+I\)};}
-
-        \only<.(1)->{\node (c0) [text=red!50!black!80] at (-1.2, -2.8) {\(-I\)};}
-        \only<.(1)->{\node (c1) [text=red!50!black!80] at (-0.05, -2.8) {\(-I\)};}
-        \only<.(1)->{\node (c2) [text=red!50!black!80] at (1.2, -2.8) {\(-I\)};}
+        \only<.(1)->{\node (r0) [text=green!50!black!80] at (1.65, -0.05) {\(+1\)};}
+        \only<.(1)->{\node (r1) [text=green!50!black!80] at (1.65, -1.20) {\(+1\)};}
+        \only<.(1)->{\node (r2) [text=green!50!black!80] at (1.65, -2.45) {\(+1\)};}
+
+        \only<.(1)->{\node (c0) [text=red!50!black!80] at (-1.2, -2.8) {\(-1\)};}
+        \only<.(1)->{\node (c1) [text=red!50!black!80] at (-0.05, -2.8) {\(-1\)};}
+        \only<.(1)->{\node (c2) [text=red!50!black!80] at (1.2, -2.8) {\(-1\)};}
 
@@
 
-\begin{frame}{Definição 3 (Paridade)}
+\begin{frame}{Definição 4 (Paridade)}
   \begin{cbox}{}{parity}
@@
     \[
-      p(\ell) = \prod_{e \in E} \ell(E).
+      p(\ell) = \prod_{e \in E} \ell(e).
     \]
@@
 
-\begin{frame}{Definição 4 (Arranjo Mágico)}
+\begin{frame}{Definição 5 (Arranjo Mágico)}
   \begin{cbox}{}{magic-arrang}
@@
 
-\begin{frame}{Definição 5 (Jogos de Paridade Pseudotelepáticos)}
+\begin{frame}{Definição 6 (Jogos de Paridade Pseudotelepáticos)}
   \begin{cbox}{}{parity}
@@
 
-    \item Charlie envia \(u\) para Alice e \(e\) para Bob
+    \item Charlie envia o vértice \(u\) para Alice e a aresta \(e\) para Bob
 
@@
 
-\begin{frame}{Definição 6 (Grafo de Interseção)}
+\begin{frame}{Definição 7 (Grafo de Interseção)}
   \begin{cbox}{}{intersection-graph}
@@
 
+    \item O rótulo de \(u\) é o produto dos rótulos de \(v\) e \(w\)
+
     \item Propriedade 1: o grafo, após a contração da aresta, continua planar
@@
     do vértice, em sentido anti-horário, é igual a identidade
-    multiplicada pelo signal do vértice
+    multiplicada pelo sinal do vértice
 
@@
       \begin{align*}
-        M_{k} M_{k + 1} \ldots M_{n} M_{1} M_{k - 1}
+        M_{k} M_{k + 1} \ldots M_{n} M_{1} \ldots M_{k - 1}
         &= (M_{k - 1} \ldots M_{1})(M_{1} \ldots M_{n}) (M_{1} \ldots M_{k - 1}) \\
@@
 
-\begin{frame}{Definição 7 (Menor Topológico)}
+\begin{frame}{Definição 8 (Menor Topológico)}
   \begin{cbox}{}{top-minor}
@@
     \((u, v) \in H\) para um caminho simples entre
-    \(\phi(u) e \phi(v)\) em \(G\), tal que os caminhos são disjuntos
+    \(\phi(u)\) e \(\phi(v)\) em \(G\), tal que os caminhos são disjuntos
     (com exceção das extremidades \(u\) e \(v\)).

### 2023-07-03 paper/main.tex
paper => fix third column
paper => hypergraphs

@@
 \begin{document}
-\title{Quantum Pseudo-Telepathy}
-\subtitle{The Magic Square Game}
+\title{Quantum Magic Games}
 
@@
 strategies that Alice and Bob can adopt. It is not difficult to
-convince yourself that, no matter how they decide to fill in
-their entries, it is impossible for them to come up with predefined
-answers that always win. Any deterministic strategy is a pair of
-matrices, one for Alice and another for Bob. The only way that they could
-design a strategy that wins with certainty every round is to prepare two
-identical matrices satisfying the requirements for each row and for each
-column. That is, a single matrix for which the product of every row is
-\(+1\) and the product of every column is \(-1\). Such a matrix cannot
-possibly exist! It turns out that the best that they can do is to win
-with probability \(\nicefrac{8}{9}\).
+convince yourself that, no matter how they decide to fill in their
+entries, it is impossible for them to come up with predefined answers
+that always win. Any deterministic strategy is a pair of matrices, one
+for Alice and another for Bob. The only way that they could design a
+strategy that wins with certainty every round is to prepare two
+identical matrices satisfying the requirements for each row and for
+each column. That is, a single matrix for which the product of every
+row is \(+1\) and the product of every column is \(-1\). Such a matrix
+cannot possibly exist!  To see that, consider the constraints over
+each row and column:
+\[\begin{aligned}
+    m_{0,0}\, m_{0,1}\, m_{0,2} &= +1 \\
+    m_{1,0}\, m_{1,1}\, m_{1,2} &= +1 \\
+    m_{2,0}\, m_{2,1}\, m_{2,2} &= +1 \\
+    m_{0,0}\, m_{1,0}\, m_{2,0} &= -1 \\
+    m_{0,1}\, m_{1,1}\, m_{2,1} &= -1 \\
+    m_{0,2}\, m_{1,2}\, m_{2,2} &= -1 \\
+    \midrule
+    +1 &\neq -1
+  \end{aligned}\]
+
+It turns out that the best that they can do is to win
+with probability \(\nicefrac{8}{9}\)
 
@@
 bounded by the winning probability of the best deterministic strategy,
-which is \(\nicefrac{8}{9}\). Theorem~\ref{thm:classical-success}
-formalizes this argument.
+which is \(\nicefrac{8}{9}\). A formal proof is given in~\ref{xxx}
+for any pseudo-telepathy game (i.e.\ games whose quantum strategies
+exhibit this notion of pseudo-telapathy).
 
@@
 
-\section{Quantum Unitaries (? research)}
-\label{sec:quantum-unitaries}
+\section{Characterizing Quantum Magic Games}
+\label{sec:extending}
+What if we change the format of the Mermin-Peres magic square game?
+Maybe increase the number of rows and columns, or even change the
+shape entirely? Figure~\ref{fig:as-graph} (a) gives an example of the
+magic pentagram game, in which the product of the labels (\(+1\) or
+\(-1\)) assigned to each of four vertices in a line must equal the
+labels of that line (the product of the four vertices in the topmost
+horizontal line, for example, must be \(-1\)). Notice that we are now
+changing the visualization format to
+hypergraphs. Figure~\ref{fig:as-graph} (b) shows the magic square as a
+hypergraph. In this section, we explore a characterization of games that
+follow the same style as the magic square and pentagram, given
+by~\ref{arkhipov2012}.
 
+\begin{figure}[htbp]
+  \centering
+  \begin{subfigure}[t]{0.49\textwidth}
+    \begin{center}
+      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
+        \node (00) [vertex] at (-1.25, 0) {};
+        \node (01) [vertex] at (0,  0) {};
+        \node (02) [vertex] at (1.25,  0) {};
+
+        \node (10) [vertex] at (-1.25, -1.25) {};
+        \node (11) [vertex] at (0,  -1.25) {};
+        \node (12) [vertex] at (1.25,  -1.25) {};
+
+        \node (20) [vertex] at (-1.25, -2.5) {};
+        \node (21) [vertex] at (0,  -2.5) {};
+        \node (22) [vertex] at (1.25, -2.5) {};
+
+        \node (r0) [text=green!50!black!80] at (1.65, -0.05) {\(+1\)};
+        \node (r1) [text=green!50!black!80] at (1.65, -1.20) {\(+1\)};
+        \node (r2) [text=green!50!black!80] at (1.65, -2.45) {\(+1\)};
+
+        \node (c0) [text=red!50!black!80] at (-1.2, -2.8) {\(-1\)};
+        \node (c1) [text=red!50!black!80] at (-0.05, -2.8) {\(-1\)};
+        \node (c2) [text=red!50!black!80] at (1.2, -2.8) {\(-1\)};
+
+        \path[]
+        (00) edge (01) edge (10)
+        (01) edge (02) edge (11)
+        (02) edge (12)
+
+        (10) edge (11) edge (20)
+        (11) edge (12) edge (21)
+        (12) edge (22)
+
+        (20) edge (21)
+        (21) edge (22)
+        ;
+      \end{tikzpicture}
+    \end{center}
+    \caption{The magic square game as a hypergraph.}
+  \end{subfigure}
+  \hfill{}
+   \begin{subfigure}[t]{0.49\textwidth}
+    \begin{center}
+      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
+        \foreach \c [evaluate=\c as \ang using {18 + 72*\c}] in {0, 1, 2, 3, 4} {
+          \node [vertex] (\c) at (\ang:25mm) {};
+        }
+
+        \draw [name path=0--2] (0) -- (2);
+        \draw [name path=0--3] (0) -- (3);
+        \draw [name path=1--3] (1) -- (3);
+        \draw [name path=1--4] (1) -- (4);
+        \draw [name path=2--4] (2) -- (4);
+
+        \node [vertex] (01) at (intersection of 0--2 and 1--4) {};
+        \node [vertex] (04) at (intersection of 0--3 and 1--4) {};
+        \node [vertex] (12) at (intersection of 1--3 and 0--2) {};
+        \node [vertex] (23) at (intersection of 1--3 and 2--4) {};
+        \node [vertex] (34) at (intersection of 0--3 and 2--4) {};
+
+        \node [text=red!50!black!80] (label0--2) at ($(01)!0.5!(12) - (0, 0.25)$) {\(-1\)};
+        \node [text=green!50!black!80] (label1--4) at ($(01)!0.5!(04) + (-0.3, -0.1)$) {\(+1\)};
+        \node [text=green!50!black!80] (label0--3) at ($(04)!0.5!(34) + (-0.1, 0.25)$) {\(+1\)};
+        \node [text=green!50!black!80] (label2--4) at ($(23)!0.5!(34) + (+0.1, 0.25)$) {\(+1\)};
+        \node [text=green!50!black!80] (label1--3) at ($(12)!0.5!(23) + (+0.3, -0.1)$) {\(+1\)};
+      \end{tikzpicture}
+    \end{center}
+    \caption{The pentagram game as a hypergraph.}
+  \end{subfigure}
+  \caption{Examples of hypergraphs representing quantum magic games~\ref{arkhipov2012}.}
+\end{figure}
 \printbibliography{}

### 2023-07-03 paper/main.tex
paper => up to magic arrangement

@@
 \usepackage{amsmath}
+\usepackage{amsfonts}
 \usepackage{nicefrac}
@@
 What if we change the format of the Mermin-Peres magic square game?
-Maybe increase the number of rows and columns, or even change the
-shape entirely? Figure~\ref{fig:as-graph} (a) gives an example of the
-magic pentagram game, in which the product of the labels (\(+1\) or
-\(-1\)) assigned to each of four vertices in a line must equal the
-labels of that line (the product of the four vertices in the topmost
-horizontal line, for example, must be \(-1\)). Notice that we are now
-changing the visualization format to
-hypergraphs. Figure~\ref{fig:as-graph} (b) shows the magic square as a
-hypergraph. In this section, we explore a characterization of games that
-follow the same style as the magic square and pentagram, given
-by~\ref{arkhipov2012}.
+Maybe increase the dimensions, or even change the shape entirely?
+Figure~\ref{fig:as-graph} (a) gives an example of the magic pentagram
+game, in which the product of the labels (\(\pm{}1\)) assigned to each
+of four vertices in a line must equal the labels of that line (the
+product of the four vertices in the topmost horizontal line, for
+example, must be \(-1\)). Notice that we are now changing the
+visualization format to hypergraphs.  Figure~\ref{fig:as-graph} (b)
+shows the magic square as a hypergraph.  As the magic square, the
+pentagram is also due to Mermin~\ref{xxx}.  In this section, we
+explore a characterization of Mermin-style games, given
+by~\cite{arkhipov2012}.
 
@@
   \centering
-  \begin{subfigure}[t]{0.49\textwidth}
-    \begin{center}
-      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
-        \node (00) [vertex] at (-1.25, 0) {};
-        \node (01) [vertex] at (0,  0) {};
-        \node (02) [vertex] at (1.25,  0) {};
-
-        \node (10) [vertex] at (-1.25, -1.25) {};
-        \node (11) [vertex] at (0,  -1.25) {};
-        \node (12) [vertex] at (1.25,  -1.25) {};
-
-        \node (20) [vertex] at (-1.25, -2.5) {};
-        \node (21) [vertex] at (0,  -2.5) {};
-        \node (22) [vertex] at (1.25, -2.5) {};
-
-        \node (r0) [text=green!50!black!80] at (1.65, -0.05) {\(+1\)};
-        \node (r1) [text=green!50!black!80] at (1.65, -1.20) {\(+1\)};
-        \node (r2) [text=green!50!black!80] at (1.65, -2.45) {\(+1\)};
-
-        \node (c0) [text=red!50!black!80] at (-1.2, -2.8) {\(-1\)};
-        \node (c1) [text=red!50!black!80] at (-0.05, -2.8) {\(-1\)};
-        \node (c2) [text=red!50!black!80] at (1.2, -2.8) {\(-1\)};
-
-        \path[]
-        (00) edge (01) edge (10)
-        (01) edge (02) edge (11)
-        (02) edge (12)
-
-        (10) edge (11) edge (20)
-        (11) edge (12) edge (21)
-        (12) edge (22)
-
-        (20) edge (21)
-        (21) edge (22)
-        ;
-      \end{tikzpicture}
-    \end{center}
-    \caption{The magic square game as a hypergraph.}
-  \end{subfigure}
-  \hfill{}
    \begin{subfigure}[t]{0.49\textwidth}
@@
   \end{subfigure}
-  \caption{Examples of hypergraphs representing quantum magic games~\ref{arkhipov2012}.}
+  \hfill{}
+  \begin{subfigure}[t]{0.49\textwidth}
+    \begin{center}
+      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
+        \node (00) [vertex] at (-1.25, 0) {};
+        \node (01) [vertex] at (0,  0) {};
+        \node (02) [vertex] at (1.25,  0) {};
+
+        \node (10) [vertex] at (-1.25, -1.25) {};
+        \node (11) [vertex] at (0,  -1.25) {};
+        \node (12) [vertex] at (1.25,  -1.25) {};
+
+        \node (20) [vertex] at (-1.25, -2.5) {};
+        \node (21) [vertex] at (0,  -2.5) {};
+        \node (22) [vertex] at (1.25, -2.5) {};
+
+        \node (r0) [text=green!50!black!80] at (1.65, -0.05) {\(+1\)};
+        \node (r1) [text=green!50!black!80] at (1.65, -1.20) {\(+1\)};
+        \node (r2) [text=green!50!black!80] at (1.65, -2.45) {\(+1\)};
+
+        \node (c0) [text=red!50!black!80] at (-1.2, -2.8) {\(-1\)};
+        \node (c1) [text=red!50!black!80] at (-0.05, -2.8) {\(-1\)};
+        \node (c2) [text=red!50!black!80] at (1.2, -2.8) {\(-1\)};
+
+        \path[]
+        (00) edge (01) edge (10)
+        (01) edge (02) edge (11)
+        (02) edge (12)
+
+        (10) edge (11) edge (20)
+        (11) edge (12) edge (21)
+        (12) edge (22)
+
+        (20) edge (21)
+        (21) edge (22)
+        ;
+      \end{tikzpicture}
+    \end{center}
+    \caption{The magic square game as a hypergraph.}
+  \end{subfigure}
+  \caption{Examples of hypergraphs representing quantum magic games~\cite{arkhipov2012}.\label{fig:as-graph}}
 \end{figure}
+
+We start by defining the notion of \emph{arrangements}, which are
+configurations on which Mermin-style games may be
+played. \cite{arkhipov2012} defines both unsigned and signed
+arrangements. Instead, we shall focus  on \emph{signed}
+arrangements, and thus anytime we say ``arrangement'' we mean the
+signed version.
+
+\begin{definition}[Arrangement~\cite{arkhipov2012}]\label{def:arrangement}
+  An arrangement \(A = (V, E, \ell)\) is a finite connected hypergraph
+  with vertex set \(V\) and hyperedge set \(E\), where a hyperedge is
+  a nonempty subset of \(V\), such that every vertex \(v \in V\) lies
+  in exactly two hyperedges \(e_{0}, e_{1} \in E\) (\emph{connected}
+  means that the hypegraph cannot be split into two smaller disjoint
+  hypergraphs). The labelling function \(\ell\colon E \to \{+1, -1\}\)
+  maps each hyperedge to a sign \(+1\) or \(-1\).
+\end{definition}
+
+We will oftenly refer to a hyperedge as a \emph{line}. In
+Figure~\ref{fig:as-graph} (a), the lines going through sequences of
+four vertices are the hyperedges. Similarly, in
+Figure~\ref{fig:as-graph} (b), the horizontal and vertical lines
+touching the sequences of three vertices are the hyperedges.  As
+already mentioned, arrangements define the configurations on which
+games may be played.
+
+\begin{definition}[Classical Realization~\cite{arkhipov2012}]\label{def:classical-re}
+  A classical realization of an arrangement \(A = (V, E, \ell)\) is a
+  labelling \(c\colon V \to \{+1, -1\}\) that, for every hyperedge
+  \(e \in E\), satisfies the property 
+  \[
+    \prod_{v \in e} c(v) = \ell(e).
+  \]
+\end{definition}
+
+\begin{tcbexample}{Classical Realization}{class-re}
+  Figure~\ref{fig:class-re} depicts an example of a classically
+  realizable arrangement. That is, an arrangement for which there exists
+  a classical realization.
+
+  \begin{figure}[H]
+    \begin{center}
+      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
+        \node (00) [vertex] at (-1.25, 0) {};
+        \node (01) [vertex] at (0,  0) {};
+        \node (02) [vertex] at (1.25,  0) {};
+
+        \node (10) [vertex] at (-1.25, -1.25) {};
+        \node (11) [vertex] at (0,  -1.25) {};
+        \node (12) [vertex] at (1.25,  -1.25) {};
+
+        \node (r0) [text=red!50!black!80] at (1.65, -0.05) {\(-1\)};
+        \node (r1) [text=red!50!black!80] at (1.65, -1.20) {\(-1\)};
+
+        \node (c0) [text=green!50!black!80] at (-1.2, -1.65) {\(+1\)};
+        \node (c1) [text=green!50!black!80] at (-0.05, -1.65) {\(+1\)};
+        \node (c2) [text=green!50!black!80] at (1.2, -1.65) {\(+1\)};
+
+        \path[]
+        (00) edge (01) edge (10)
+        (01) edge (02) edge (11)
+        (02) edge (12)
+
+        (10) edge (11)
+        (11) edge (12)
+        ;
+      \end{tikzpicture}
+    \end{center}
+    \caption{Example of a classically realizable arrangement.\label{fig:class-re}}
+  \end{figure}
+
+    A classical realization \(c\) for this arrangement is
+  \begin{align*}
+    c(v_{00}) = c(v_{01}) = c(v_{10}) = c(v_{11}) &= +1 \\
+    c(v_{02}) = c(v_{12}) &= -1.
+  \end{align*}
+\end{tcbexample}
+
+\begin{definition}[Quantum Realization~\cite{arkhipov2012}]\label{def:quantum-re}
+  A quantum realization of an arrangement \(A = (V, E, \ell)\) is a
+  labelling \(q\colon V \to \operatorname{GL}(\mathcal{H})\) is a
+  mapping from each vertex to an observable \(M\) on a fixed
+  finite-dimensional Hilbert-space \(\mathcal{H}\), such that
+  \begin{itemize}
+  \item \(M\) is Hermitian and squares to the identity, or
+    equivalently, has eigenvalues \(\pm{}1\);
+
+  \item For each hyperedge, the observable assigned to its vertices
+    pairwise commute and
+
+  \item For each hyperedge \(e \in E\), the labelling of its vertices
+    satisfies the property
+    \[
+      \prod_{v \in e} q(v) = \ell(e) I.
+    \]
+  \end{itemize}
+\end{definition}
+
+A classical realization is simply a quantum realization in which
+\(\mathcal{H} = \mathbb{R}\). As such, every classically realizable
+arrangement is quantumly realizable. An example of quantum realization
+was given in Section~\ref{sec:quantum-sol} for the magic square game.
+Any arrangement that is quantumly realizable with observables that all
+mutually commute, then it is also classically
+realizable~\cite[Proposition 8]{arkhipov2012}. The proof follows by
+the simultaneous diagonalization of the observables, similar to our
+proof for Lemma~\ref{lem:product}.
+
+It turns out that the existence of a classical or quantum realization
+of an arrangement depends only on whether the number of \(-1\) labels
+is odd or even. This is called the \emph{parity} of the arrangement.
+
+\begin{definition}[Parity~\cite{arkhipov2012}]\label{def:parity}
+  The parity \(p(\ell)\) of an arrangement \(A = (V, E, \ell)\) is
+  \[
+    p(\ell) = \prod_{e \in E} \ell(E),
+  \]
+  which is \(-1\) if there is an odd number of \(-1\) labels, or \(+1\) otherwise.
+\end{definition}
+
+If there exists a realization (either classical or quantum) of an
+arrangement \(A = (V, E, \ell)\), then it is possible to construct a
+realization for \(A' = (V, E, \ell')\) from the realization of
+\(A\)~\cite[Propositions 10 and 12]{arkhipov2012}. Furthermore, an
+arrangement is classically realizable if, and only if, its parity is
+\(+1\)~\cite[Proposition 11]{arkhipov2012}. Despite this fundamental result,
+Classically realizable arrangements are not as much interesting as the
+quantumly ones. Therefore, the goal is to characterize the gap between
+these two worlds. The arrangements that are quantumly realizable, but
+are not classically realizable, are called \emph{magic} and are
+defined as follows:
+
+\begin{definition}[Magic Arrangement~\cite{arkhipov}]\label{def:magic-arr}
+  An arrangement is said magic its parity is \(-1\) and it is
+  quantumly realizable.
+\end{definition}
+
+The magic square and the pentagram are examples of magic arrangements.
+Equipped with all these tools, we now define a generalization of \emph{parity}
+pseudo-telepathy games (Mermin-style games):
+
 \printbibliography{}

### 2023-07-03 paper/main.tex
paper => proof main result, first direction

@@
 
+\usepackage[parfill]{parskip} % noindent + space between paragraph (I really prefer...)
 \usepackage[table]{xcolor}
@@
 
+\begin{definition}[Parity Telepathy Game~\cite{arkhipov2012}]\label{def:parity-game}
+  The parity telepathy game on an arrangement \(A = (V, E, \ell)\) is
+  a two-players cooperative game (say, played by Alice and Bob). The
+  game is conducted by a referee charlie. Alice and Bob may agree on a
+  prior strategy, but cannot communicate once the game starts. At each
+  round,
+  \begin{enumerate}
+  \item Charlie randomly picks a vertex \(u \in V\) and one of the hyperedges
+    \(e \in E\) that contains \(u\);
+
+  \item Charlie sends the vertex \(u\) to Alice and the hyperedge \(e\) to Bob;
+
+  \item Alice labels the vertex \(u\) with \(a(u) = \pm{}1\) and sends
+    \(a(u)\) to Charlie;
+
+  \item Bob labels each vertex \(v \in e\) with \(b(v) = \pm{}1\) and sends
+    each \(b(v)\) to Charlie;
+
+  \item Alice and Bob win if \(a(u) = b(u)\) and \(\prod_{v} b(v) = \ell(e)\).
+  \end{enumerate}
+\end{definition}
+
+Notice that the generalization above differs a bit from the magic
+square game seen in Section~\ref{sec:magic-square}, where Alice
+receives a hyperedge from Charlie. This modification generalizes to
+arrangements that do not share the property exhibited by the magic
+square that its lines can be split into two disjoint sets (rows and
+columns). In this sense, one can simply understand the magic square
+game as a combination of two rounds. In the first ``half'' of the
+round, Charlie sends the vertex \(u\) to Alice and the line \(e\) to
+Bob. In the second half, Charlie sends \(u\) to Bob, but
+\emph{another} line \(e' \neq e\) to Alice.
+
+There exists a strategy that wins with certainty a parity telepathy
+game played on a magic arrangement that has a quantum realization in
+which all the operators have all real eigenvalues, provided that Alice
+and Bob can share entanglement in advance~\cite[Theorem
+17]{arkhipov2012}. It suffices for them to share a maximally entangled
+state
+\[
+  \rho_{AB} = \sum_{i = 0}^{n-1} \ket{i}\ket{i},
+\]
+where \(\{\ket{i}\}\) is a basis for the finite-dimensional
+Hilbert-space \(\mathcal{H}\) of dimension \(n\). In the case of the
+magic square, \(n = 4\) and
+\(\{\ket{i}\} = \{\ket{0}, \ket{1}, \ket{2}, \ket{3}\}\), which,
+rewritten as binary strings, is
+\(\{\ket{00}, \ket{01}, \ket{10}, \ket{11}\}\). The proof is similar
+to our proof for Theorem~\ref{theo:quantum-wins}, using the
+simultaneous diagonalization of operators in the same hyperedge and
+the symmetry of the state.
+
+\subsection{Main Result: Characterization of Magic Arrangements by Planar Graphs}
+
+We now move on to the main result of~\cite{arkhipov2012}. We shall
+derive a characterization of magic arrangements by the planarity of
+its corresponding intersection graph.
+
+\begin{definition}[Intersection Graph]\label{def:intersec}
+  The intersection graph of an arrangement \(A = (V, E)\) is the
+  undirected graph \(G = (V', E')\), where \(V' = E\), and there is an
+  edge between two vertices \(e_{0}, e_{1} \in V'\) for each vertex in
+  the insection of \(e_{0}\) and \(e_{1}\).
+\end{definition}
+
+The intersection graph of an arrangement is a dual representation in
+which the roles of vertices and hyperedges are switched. The vertices
+of the intersection graph are labelled with the same values of the
+corresponding hyperedges in the arrangement. Similarly, a quantum
+realization of the intersection graph assigns to its edges the same
+measurements ascribed to the corresponding vertices in the
+arrangement. The properties observed in the arrangement are also
+carried to the intersection graph. In particular, the observables
+assigned to the edges around a vertex in the intersection graph (by
+around, we mean the edges that touch that vertex) mutually commute and
+its product equals the identity times the label of the vertex. To
+illustrate, the intersection graph of the magic square is the complete
+bipartite graph on six vertices \(K_{3, 3}\) and the intersection
+graph of the magic pentagram is the complete graph on five vertices
+\(K_{5}\).
+
+We are also going to need the definition of a topological minor:
+
+\begin{definition}[Topological Minor]\label{def:topo}
+  A graph \(H\) is a topological minor of \(G\) if there is an
+  embedding of \(H\) in \(G\) that consists of an injective map
+  \(\phi\) from every vertex \(v \in H\) to a vertex
+  \(\phi(v) \in G\), and a map from each edge \((u, v) \in H\) to a
+  simple path from \(\phi(u)\) to \(\phi(v)\) in G, such that these
+  paths are disjoint (except on their endpoints).
+\end{definition}
+
+We now restate the main result of~\cite{arkhipov2012} and its proof,
+further illustrating it with examples.
+
+\begin{theorem}\label{theo:main}
+  An arrangement is magic if and only if its intersection graph is not
+  planar.
+\end{theorem}
+
+We start by considering the direction that says that ``nonplanar
+implies magic'', or equivalently, if the intersection graph is planar,
+then its arrangement is not magic.
+
+\begin{proof}
+  First of all, assume that there exists a quantum realization of the
+  arrangement (if there is none, then the arrangement is not magic).
+  The goal is to show that, if there exists a quantum realization and
+  the intersection graph is planar, then the parity of the arrangement
+  is \(+1\) and, consequently, it is not magic. The strategy consists
+  of repeatedly contracting edges of the intersection, and show that
+  contraction preserves a few properties. To contract an edge is to
+  merge the two endpoints \(v\) and \(w\) into a new vertex
+  \(u\). Every edge that used to touch \(v\), now touches \(u\), and
+  every edge that used to touch \(w\), now touches
+  \(u\). Consequently, the edge that was contracted becomes two
+  self-loops. Moreover, we define the label of the new vertex \(w\) as
+  the product of the labels of \(u\) and \(v\). We observe that
+  contraction preserves the following properties:
+
+  \begin{enumerate}
+  \item The resulting graph remains planar.
+
+  \item The parity (product of all the vertex labels) remains the
+    same. This follows directly from the definition of the label of
+    thenew vertex.
+
+  \item The product of the labels of edges around any vertex, in
+    cyclic order (say, without loss of generality, counterclockwise),
+    equals the identity times the label of the vertex. To see this,
+    first notice that this property holds for the initial graph, since
+    all observables around a vertex pairwise commute (recall that
+    these observables correspond to the observables assigned by the
+    quantum realization to vertices that lie in the hyperedge in the
+    arrangement). However, the commutative property does not
+    necessarily hold after contraction. Nevertheless, if we follow a
+    cyclic order, we can still see that this property is
+    preserved. Let \(M_{0}, \ldots, M_{n-1}\) be the observables
+    around a vertex \(v\), going counterclockwise. If
+    \(M_{0} \ldots M_{n - 1} = \ell(v) I\), then for any starting
+    point \(k\),
+    \(M_{k} M_{k+1}\ldots M_{n-1}M_{0}\ldots M_{k-1} = \ell(v) I\),
+    since
+    \begin{align}
+      M_{k}M_{k+1} \ldots M_{n-1}M_{0}\ldots M_{k-1}
+      &= (M_{k-1}\ldots M_{0})(M_{0} \ldots M_{n-1})(M_{0}\ldots M_{k-1})  \label{eq:cyclic1} \\
+      &= (M_{k-1}\ldots M_{0})\ell(v) I(M_{0}\ldots M_{k-1}) = \ell(v) I,  \label{eq:cyclic2}
+    \end{align}
+    where (\ref{eq:cyclic1}) follows from the fact that
+    \(M_{i} M_{i} = \ell(v) I\). Now, let \(X\) be the measurement assigned to
+    the edge that is being contracted and let the labels around its
+    endpoints \(v\) and \(w\) be \(M_{0}\ldots M_{m-1}X\) and
+    \(X N_{0}\ldots N_{n-1}\) going counterclockwise. Then,
+    \(M_{0} \ldots M_{m-1} X = \ell(v)I\) and
+    \(X N_{0} \ldots N_{n-1} = \ell(w)I\). Multiplying these gives
+    \[
+      M_{0}\ldots M_{m-1} X^{2} N_{0} \ldots N_{n-1} =
+      M_{0}\ldots M_{m-1} N_{0} \ldots N_{n-1} =
+      \ell(v) \ell(w) I = \ell(u) I,
+    \]
+    so the product of the observables around the new vertex \(w\)
+    still is the identity times its label. Notice that key to this
+    strategy is the fact that the graph is planar, and thus we can
+    draw the edges around the new vertex without mixing the edges that
+    used to touch \(v\) and \(w\).
+  \end{enumerate}
+
+  By repeatedly contracting edges, eventually we reach a graph with a
+  single vertex.  Due to how we defined the label of each new vertex
+  (i.e.\ as the product of the labels of the vertices being merged),
+  it follows that the label of the last vertex equals the product of
+  the labels of all the original vertices, and therefore equals the
+  parity of the arrangement. The remaining vertex has multiple
+  self-loops, two for each measurement \(M\) ascribed to the original
+  edges.  Since \(M^{2} = I\), going counterclockwise we get a
+  sequence \(M_{0}^{2} \ldots M_{\vert E'\vert -1}^{2} = I\). But, we
+  saw that contraction preserves the third property, which says that
+  the observables around a vertex multiply to the identity times the
+  vertex label. Thus, the label of the final vertex is \(1\) and,
+  consequently, the parity of the arrangement is \(+1\). \qed
+\end{proof}
 \printbibliography{}

### 2023-07-04 paper/main.tex
paper => ex for first direction of main result

@@
 
-\section{Contextuality}
+\subsection{Contextuality}
 \label{sec:context}
@@
       \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
-        \node (00) [vertex] at (-1.25, 0) {};
-        \node (01) [vertex] at (0,  0) {};
-        \node (02) [vertex] at (1.25,  0) {};
-
-        \node (10) [vertex] at (-1.25, -1.25) {};
-        \node (11) [vertex] at (0,  -1.25) {};
-        \node (12) [vertex] at (1.25,  -1.25) {};
+        \node (00) [vertex, label=above left:{\(v_{0}\)}] at (-1.25, 0) {};
+        \node (01) [vertex, label=above left:{\(v_{1}\)}] at (0,  0) {};
+        \node (02) [vertex, label=above left:{\(v_{2}\)}] at (1.25,  0) {};
+
+        \node (10) [vertex, label=above left:{\(v_{3}\)}] at (-1.25, -1.25) {};
+        \node (11) [vertex, label=above left:{\(v_{4}\)}] at (0,  -1.25) {};
+        \node (12) [vertex, label=above left:{\(v_{5}\)}] at (1.25,  -1.25) {};
 
@@
   \begin{align*}
-    c(v_{00}) = c(v_{01}) = c(v_{10}) = c(v_{11}) &= +1 \\
-    c(v_{02}) = c(v_{12}) &= -1.
+    c(v_{0}) = c(v_{1}) = c(v_{3}) = c(v_{4}) &= +1 \\
+    c(v_{2}) = c(v_{5}) &= -1.
   \end{align*}
@@
 \end{proof}
+
+\begin{tcbexample}{Planar Graph \(\implies\) Not Magic}{planar-nmagic}
+  Consider the arrangement depicted in Figure~\ref{fig:class-re} and
+  assume there exists a quantum realization that assigns the
+  observables \(M_{i}\) to each vertex \(v_{i}\). Suppose that we do
+  not know that the parity of this arrangement is \(+1\). We are going
+  to follow the strategy described above, to show that its parity must
+  be \(+1\). Figure~\ref{fig:class-re-inters} shows the intersection graph
+  that corresponds to that arrangement.
+
+  \begin{figure}[H]
+    \begin{center}
+      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
+        \node (line0) [vertex, label=above:{\(e_{0}\)}] at (0, 0) {};
+        \node (line1) [vertex, label=below:{\(e_{1}\)}] at (0, -3) {};
+        \node (col0) [vertex, label=left:{\(e_{2}\)}] at (-1.5, -1.5) {};
+        \node (col1) [vertex, label=right:{\(e_{3}\)}] at (0, -1.5) {};
+        \node (col2) [vertex, label=right:{\(e_{4}\)}] at (1.5, -1.5) {};
+        \path[]
+        (line0) edge node[sloped, above] {\(M_{0}\)} (col0)
+        (line0) edge node[midway, fill=gray!15] {\(M_{1}\)} (col1)
+        (line0) edge node[sloped, above] {\(M_{2}\)} (col2)
+        (line1) edge node[sloped, below] {\(M_{3}\)} (col0)
+        (line1) edge node[midway, fill=gray!15] {\(M_{4}\)} (col1)
+        (line1) edge node[sloped, below] {\(M_{5}\)} (col2)
+        ;
+      \end{tikzpicture}
+    \end{center}
+    \caption{Intersection graph corresponding to the arrangement seen
+      in Figure~\ref{fig:class-re}.\label{fig:class-re-inters}}
+  \end{figure}
+
+  Let us contract the edge labelled by \(M_{0}\) (recall that it
+  corresponds to the vertex \(v_{0}\) in the arrangement). The
+  resulting graph is depicted in Figure~\ref{fig:contract0}.  Notice
+  that \(M_{1}M_{2}M_{0} = \ell(e_{0}) I\) and
+  \(M_{0}M_{3} = \ell(e_{2}) I\). After contraction, we have
+  a new vertex \(e'_{0}\), with \(\ell(e'_{0}) = \ell(e_{0})\ell(e_{2})\)
+  and \(M_{1}M_{2}M_{0}^{2}M_{3} = \ell(e_{0})\ell(e_{2}) I = \ell(e'_{0}) I\).
+
+    \begin{figure}[H]
+    \begin{center}
+      \begin{tikzpicture}[
+        vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt},
+        every loop/.style={}
+        ]
+        \node (line1) [vertex, label=below:{\(e_{1}\)}] at (0, -3) {};
+        \node (e'0) [vertex, label=left:{\(e'_{0}\)}] at (-1.5, -1.5) {};
+        \node (col1) [vertex, label=right:{\(e_{3}\)}] at (0, -1.5) {};
+        \node (col2) [vertex, label=right:{\(e_{4}\)}] at (1.5, -1.5) {};
+        \path[]
+        (e'0) edge[loop above, in=120, out=60, min distance=5mm] node {\(M_{0}^{2}\)} (e'0)
+        (e'0) edge node[midway, fill=gray!15] {\(M_{1}\)} (col1)
+        (e'0) edge[bend left=45] node[sloped, above] {\(M_{2}\)} (col2)
+        (line1) edge node[sloped, below] {\(M_{3}\)} (e'0)
+        (line1) edge node[midway, fill=gray!15] {\(M_{4}\)} (col1)
+        (line1) edge node[sloped, below] {\(M_{5}\)} (col2)
+        ;
+      \end{tikzpicture}
+    \end{center}
+    \caption{Graph that results from the contraction of the edge from
+      \(e_{0}\) to \(e_{2}\) in Figure~\ref{fig:class-re-inters}.\label{fig:contract0}}
+  \end{figure}
+
+  Let us now contract the edge labelled by \(M_{5}\). The resulting graph
+  is shown in Figure~\ref{fig:contract5}.
+
+  \begin{figure}[H]
+    \begin{center}
+      \begin{tikzpicture}[
+        vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt},
+        every loop/.style={}
+        ]
+        \node (e'0) [vertex, label=left:{\(e'_{0}\)}] at (-1.5, -1.5) {};
+        \node (col1) [vertex, label=below:{\(e_{3}\)}] at (0, -1.5) {};
+        \node (e'1) [vertex, label=right:{\(e'_{1}\)}] at (1.5, -1.5) {};
+        \path[]
+        (e'0) edge[loop above, in=120, out=60, min distance=5mm] node {\(M_{0}^{2}\)} (e'0)
+        (e'0) edge node[midway, fill=gray!15] {\(M_{1}\)} (col1)
+        (e'0) edge[bend left=45] node[sloped, above] {\(M_{2}\)} (col2)
+        (e'0) edge[bend right=45] node[sloped, below] {\(M_{3}\)} (e'1)
+        (e'1) edge node[midway, fill=gray!15] {\(M_{4}\)} (col1)
+        (e'1) edge[loop above, in=120, out=60, min distance=5mm] node {\(M_{5}^{2}\)} (e'1)
+        ;
+      \end{tikzpicture}
+    \end{center}
+    \caption{Graph that results from the contraction of the edge from
+      \(e_{1}\) to \(e_{4}\) in Figure~\ref{fig:contract0}.\label{fig:contract5}}
+  \end{figure}
+
+  If we keep contracting edges, eventually we reach a graph with a
+  single node, whose observables going counterclockwise are
+  \(\prod_{i = 0}^{5} M_{i}^{2} = I\). And, because contracting edges
+  preserve the cyclic product property, the product of the observables is the
+  identity times the label of the last vertex. Hence, the parity of
+  this arrangement is \(+1\) (as we already knew).
+\end{tcbexample}
+
 \printbibliography{}

### 2023-07-04 paper/main.tex
paper => main result second direction

@@
 \usepackage{tcolorbox}
-\tcbuselibrary{theorems}
+\tcbuselibrary{breakable, skins, theorems}
 
 \newtcbtheorem{tcbexample}{Example}{
+  breakable,
+  enhanced,
   boxrule=0.15mm,
@@
 {\renewcommand{\arraystretch}{2}
-\begin{figure}
+\begin{figure}[htbp] 
   \centering
@@
   row with the values \(\{+1, -1, -1\}\), whose product is, as
-  required, \(+1\). Upon receiving Alice's answer, Charlie goes to
+  required
+  , \(+1\). Upon receiving Alice's answer, Charlie goes to
   meet Bob. Suppose he assigns the second column to Bob. To fill in
@@
 
+It remains to show the other direction of the result. That is, the
+intersection graph of an arrangement is nonplanar, than the
+arrangement is magic.
+
+\begin{proof}
+  By the Pontyagin and Kuratowski theorem, everry nonplanar graph contains either
+  the \(K_{5}\) or the \(K_{3,3}\) graph as a topological minor. We have already seen
+  that the \(K_{3, 3}\) is the intersection graph that corresponds to the magic square
+  and that the \(K_{5}\) corresponds to the magic pentagram, and both are magic
+  arrangements. Hence, it suffices to demonstrate that, if the intersection graph
+  \(G\) of an arrangement has a magic intersection graph \(H\) as a topological minor,
+  than \(G\) is magic. For that, we are going to construct a quantum realization
+  of \(G\) from the realization of \(H\), as follows:
+
+  \begin{enumerate}
+  \item For every vertex in \(H\), assume that the corresponding vertex in
+    \(G\) is labelled in the same way.
+
+  \item Assume that the label of every other vertex is \(+1\).
+
+  \item For every edge of \(H\), label each edge of the corresponding  path in \(G\) with
+    the same observable.
+
+  \item Label the remaining edges of \(G\) as the identity.
+  \end{enumerate}
+
+  To see why items (1) and (2) are safe to assume, recall that an
+  arrangement depends only on its parity (meaning that it is possible
+  to construct a realization for another arrangement on the same
+  vertices and hyperedges, and of same parity), and thus it does not
+  matter how you label the vertices of \(G\), as long as its parity
+  is \(-1\). It remains to show that the strategy above gives a
+  quantum realization of \(G\). For that, we check each of the
+  properties of a quantum realization:
+
+  \begin{enumerate}
+  \item Every observable \(M\) assigned to a vertex of \(G\) is either one in \(H\) or
+    the identity. Hence, \(M\) is Hermitian and squares to the identity.
+
+  \item Every vertex of \(G\) corresponding to a vertex of \(H\) is
+    surrounded by the same observables on its edges, plus (possibly)
+    copies of the identity. Therefore, these operators mutually
+    commute. Furthermore, they multiply to the identity times the
+    label of the vertex, which is labelled in the same way as its
+    corresponding vertex in \(H\).
+
+  \item Every vertex of \(G\) that lies on a simple path corresponing
+    to an edge in \(H\) touches two edges (in and out) labelled with
+    the same operator \(M\), which is the operator of the edge in
+    \(H\), plus (possibly) copies of the identity. Since
+    \(M^{2} = I\), these operators all commute and multiply to
+    \(+I\). Recall that we labelled these vertices as \(+1\), as they
+    do not have a correspondence in \(H\). Hence, the product of the
+    operators multiply to the identity times the vertex's label, as
+    desired.
+
+  \item Any other vertex of \(G\) is labelled as \(+1\) and is only
+    surrounded by edges labelled as \(+I\), which clearly commute
+    and multiply to \(+I\), i.e.\ the identity times the label of the vertex.
+  \end{enumerate}
+  \qed
+\end{proof}
+
 \printbibliography{}

### 2023-07-04 paper/main.tex
paper => intro

@@
 
+\usepackage[hidelinks]{hyperref}
 \usepackage[parfill]{parskip} % noindent + space between paragraph (I really prefer...)
@@
 \maketitle
-% \begin{abstract}
-% \end{abstract}
+\begin{abstract}
+  \textbf{TODO}
+\end{abstract}
 
@@
 according to classical physics. Certain aspects of the
-quantum realm, however, provide a way of communication that
-for a layman looks as magical as ``true'' telepathy. This
+quantum realm, however, provide a way of communication that,
+for a layman, may look as ``magical'', or as true telepathy. This
 phenomenon is called quantum
@@
 
-Quantum pseudo-telepathy is observed in many contexts,
-usually described in the format of a game: the ``impossible
-colouring games''~\cite{brassard:2005, Kochen1975}; the
-parity games, in which \(n \geq 3\) players are given
-bit-strings and, without communicating to each other, they
-output one of their bits, winning if their outputs combined
-obey certain parity conditions~\cite{brassard:2005,
-  Mermin1990}; the Deutsch-Jozsa games, where Alice and Bob
-are given bit strings \(x\) and \(y\), and must output bit
-strings \(a\) and \(b\) such that \(a = b\) if and only if
-\(x = y\)~\cite{brassard:2005, Brassard_1999}; and, the
-Magic Square game~\cite{brassard:2005, Mermin1990}. None of
-these games admit a classical winning strategy (i.e.\ is not
-possible to always win), yet they can be won systematically,
-without any communication, provided that the players share
-prior entanglement~\cite{brassard:2005}.
-
-In this project, we shall explore the Mermin-Peres Magic Square game
-(hereinafter referred simply as Magic Square). The origins of this
-game date back to the ninities. It was first described ---~albeit not
-in the format of a game~--- in the works of Mermin~\cite{mermin:1990}
-and of Peres~\cite{peres:1990}. Their results provided (as per the
-title of Mermin's review letter) a simplied proof for the
-Kochen-Specker theorem~\cite{Kocher1975}. Later, in 2002, Aravind
-demonstrated how to transform Mermin-Peres's proof of then
-Kochen-Specker theorem into a proof of Bell's
-theorem~\cite{aravind:xxx}. Bell's theorem shows the incompatibility
-of hidden variables (i.e. determinism) and locality, whereas
-Kochen-Specker's theorem demonstrates the conflicting nature of
-determinism and non-contextuality.  These sort of results may seem
+Quantum pseudo-telepathy is observed in many contexts, usually
+described in the format of a game. Examples of such games are: the
+``impossible colouring games''~\cite{cleve:2004}, based on the
+Kochen-Specker theorem~\cite{kochen:1967};
+%% Avoid confusion with our definition of parity telepathy games
+% the
+% ``parity games'', in which \(n \geq 3\) players are given
+% bit-strings and, without communicating to each other, they
+% output one of their bits, winning if their outputs combined
+% obey certain parity conditions~\cite{brassard:2005,
+%   Mermin1990};
+the ``Deutsch-Jozsa games''~\cite{brassard:1999}, based on the Deutsch-Jozsa problem~\cite{deutsch:1992};
+% where Alice and Bob
+% are given bit strings \(x\) and \(y\), and must output bit
+% strings \(a\) and \(b\) such that \(a = b\) if and only if
+% \(x = y\)~\cite{brassard:2005};
+the ``magic square'' game~\cite{aravind:2002}, based on the Mermin-Peres proof of the
+Kochen-Specker theorem~\cite{mermin:1990, peres:1990, mermin:1993, peres:1997}; and many
+others~\cite{cleve:2004, brassard:2005}. None of these games admit a
+classical winning strategy (i.e.\ is not possible to always win), yet
+they can be won systematically, without any communication, provided
+that the players are allowed to share prior entanglement~\cite{brassard:2005}.
+
+In this project, we will explore the Mermin-Peres magic square game
+(hereinafter referred simply as magic square). The origins of this
+game date back to the ninities. It was first described in the works of
+Mermin~\cite{mermin:1990, mermin:1993} and of
+Peres~\cite{peres:1990, peres:1997}. Their results provided (as per the title of
+Mermin's review letter) a simplied proof for the Kochen-Specker
+theorem~\cite{kochen:1967}. Later, in 2002, Aravind demonstrated how
+to transform Mermin-Peres's proof of the Kochen-Specker theorem into a
+proof of Bell's theorem~\cite{aravind:2002}. Bell's
+theorem~\cite{bell:1964} shows the incompatibility of hidden variables
+(i.e. determinism) and locality, and Kochen-Specker's theorem
+demonstrates the conflicting nature of determinism and
+noncontextuality (locality can be regarded as a special case of
+contextuality). These sort of results may seem
 challenging, but their descriptions can be greatly simplified by
@@
 
-\todo{FIX: they talk about contextuality only (both theorems)}
-
 \paragraph{Outline of this paper.}
+In Section~\ref{sec:magic-square}, we detail the intrinsics of the
+magic square game, classical approaches and why it is impossible to
+systematically win the game classically, how and why the quantum
+strategy works, and how to implement it. We also briefly discuss how
+the game translates to the proof of the incompatibility of a
+noncontextual hidden-variable theory. Then, in
+Section~\ref{sec:extending}, we describe a generalization of games
+that follow the same style of the magic square game, given
+by Arkhipov~\cite{arkhipov:2012}. Finally, section~\ref{sec:conc} concludes the
+presentation.
+
+\paragraph{Code.} The implementation of the classical and quantum
+solutions to the magic square game can be found at
+\url{https://github.com/luigidcsoares/quantum-magic-square}.
 
@@
 
+\section{Conclusion}\label{sec:conc}
+
 \printbibliography{}

### 2023-07-04 paper/main.tex
paper => typos

@@
 modeling them as quantum games.  In particular, it is extremely easy
-to show that there cannot be a classical solution to the the Magic
-Square game, and to convince an observer that something ``magical''
+to show that there cannot be a classical solution to the the magic
+square game, and to convince an observer that something ``magical''
 (classically impossible) is happening in a successful implementation
@@
 strategy works, and how to implement it. We also briefly discuss how
-the game translates to the proof of the incompatibility of a
+the game translates to the proof of incompatibility of a
 noncontextual hidden-variable theory. Then, in
@@
 that follow the same style of the magic square game, given
-by Arkhipov~\cite{arkhipov:2012}. Finally, section~\ref{sec:conc} concludes the
+by Arkhipov~\cite{arkhipov:2012}. Finally, Section~\ref{sec:conc} concludes the
 presentation.
@@
 \(+1\). Similarly, the product of every column of a magic square must
-be \(-1\). Is impossible to satisfy these two properties at the same
+be \(-1\). It is impossible to satisfy these two properties at the same
 time, hence the term \emph{magic}: such a matrix cannot exist. The
-Magic Square game features two players, Alice and Bob, that must work
+magic square game features two players, Alice and Bob, that must work
 together to fill in entries of the \(3 \times 3\) table.  At the
@@
       \end{subfigure}
-      \caption{One possible classical deterministic strategy for the Magic
-        Square game. Following this predefined strategy, Alice and Bob
+      \caption{One possible classical deterministic strategy for the magic
+        square game. Following this predefined strategy, Alice and Bob
         lose when assigned, respectively, the first row and third column,
@@
 It turns out that the best that they can do is to win
-with probability \(\nicefrac{8}{9}\)
+with probability \(\nicefrac{8}{9}\).
 
@@
 grids (including those matrices that would lead to invalid
-answers). In other words, a probabilistic strategy for the Magic
-Square game is one in which Alice and Bob randomly select a
+answers). In other words, a probabilistic strategy for the magic
+square game is one in which Alice and Bob randomly select a
 deterministic strategy. Hence, no matter how lucky Alice and Bob are,
@@
 bounded by the winning probability of the best deterministic strategy,
-which is \(\nicefrac{8}{9}\). A formal proof is given in~\ref{xxx}
+which is \(\nicefrac{8}{9}\). A formal proof is given in~\cite{brassard:2005}
 for any pseudo-telepathy game (i.e.\ games whose quantum strategies
@@
 \label{sec:quantum-sol}
-The quantum strategy for the Magic Square game consists of Alice and
-Bob carrying entangled qubits with them. For each round, they need a
-pair of qubits each. Then, when Charlie asks Alice (respectively Bob)
-to fill the entries of the \(i\)-th row (respectively \(j\)-th
-column), Alice measures her two qubits three times. The outcome of
-each measurement gives the value for each cell (in practice, they do
-not even need the third measurement, since they can determine the third
-value from the first two). Key to this strategy is that the outcomes
-of all possible measurements are \(\pm 1\). The initial, entangled state
-is (subscripts \(A\) and \(B\) indicate, respectively,
-Alice's and Bob's qubits)
-\begin{equation}
+The quantum strategy for the magic square game consists of Alice and
+Bob carrying entangled qubits with them. Then, when Charlie asks Alice
+(respectively Bob) to fill the entries of the \(i\)-th row
+(respectively \(j\)-th column), Alice measures her two qubits three
+times. The outcome of each measurement gives the value for each cell
+(in practice, they do not even need the third measurement, since they
+can determine the third value from the first two). Key to this
+strategy is that the outcomes of all possible measurements are
+\(\pm 1\). The initial, entangled state is (subscripts \(A\) and \(B\)
+indicate, respectively, Alice's and Bob's qubits)
+\begin{equation*}
   \ket{\psi} = \frac{1}{2}\left(
@@
   \right).
-\end{equation}
+\end{equation*}
 Figure~\ref{fig:circuit-psi} shows the quantum circuit that can be
@@
 construct a ``quantum magic'' square. Figure~\ref{fig:quantum} shows
-the \(3 \times 3\) grid that Alice and Bob can use to win the Magic
-Square game systematically.  Notice that the eigenvalues of the
+the \(3 \times 3\) grid that Alice and Bob can use to win the magic
+square game systematically.  Notice that the eigenvalues of the
 observables at each cell are \(\pm 1\). Furthermore, the product of
@@
 observables in the \(j\)-th column that was assigned to him, and fills
-each cell of his cells with the outcomes of each
+each of his cells with the outcomes of each
 measurement. Example~\ref{ex:quantum-sol} depicts a round of the game.
@@
     \end{array}\]
-  \caption{Observables used by Alice and Bob to win the Magic Square game.\label{fig:quantum}}
+  \caption{Observables used by Alice and Bob to win the magic square game.\label{fig:quantum}}
 \end{figure}}
@@
 (equiv. -1). Second, the outcome of Alice's measurement on the
-intersection is always equal to the outcome of Bob's
-measurement. Lemma~\ref{lem:product} formalizes the product property.
+intersection is always equal to the outcome of
+Bob's. Lemma~\ref{lem:product} formalizes the product property.
 
@@
 
-\begin{table}[htbp]
+\begin{table}[t]
   \centering
   \caption{Eigenvectors shared by the observables at each row of the quantum magic square.
-    The eigenvectors were taken from~\ref{xxx}, adapting to the correct eigenvalues.}
+    The eigenvectors were taken from~\cite{breinig:online}, adapting to the correct eigenvalues.}
   \label{tab:eigenv-rows}
@@
     \toprule
-    & & Column 1 & Column 2 & Column 3 \\
+    & & Column 0 & Column 1 & Column 2 \\
     \midrule
-    \multirow{2}{*}{Row 1} & \(+1\)
+    \multirow{2}{*}{Row 0} & \(+1\)
       & \ket{00}, \ket{10} & \ket{00}, \ket{01} & \ket{00}, \ket{11} \\
@@
     \midrule
-    \multirow{4}{*}{Row 2} & \multirow{2}{*}{\(+1\)}
+    \multirow{4}{*}{Row 1} & \multirow{2}{*}{\(+1\)}
       & \((\nicefrac{1}{2}) (\ket{00} + \ket{01} + \ket{10} + \ket{11})\),
@@
     \midrule
-    \multirow{4}{*}{Row 3} & \multirow{2}{*}{\(+1\)}
+    \multirow{4}{*}{Row 2} & \multirow{2}{*}{\(+1\)}
       & \((\nicefrac{1}{2}) (\ket{01} - \ket{00} + \ket{10} + \ket{11})\),
@@
 
-\begin{table}[htbp]
+\begin{table}[t]
   \centering
   \caption{Eigenvectors shared by the observables at each column of the quantum magic square.
-    The eigenvectors were taken from~\ref{xxx}, adapting to the correct eigenvalues.}
+    The eigenvectors were taken from~\cite{breinig:online}, adapting to the correct eigenvalues.}
   \label{tab:eigenv-cols}
@@
     \toprule
-    & & Row 1 & Row 2 & Row 3 \\
+    & & Row 0 & Row 1 & Row 2 \\
     \midrule
-    \multirow{4}{*}{Column 1} & \multirow{2}{*}{\(+1\)}
+    \multirow{4}{*}{Column 0} & \multirow{2}{*}{\(+1\)}
       & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{10})\),
@@
     \midrule
-    \multirow{4}{*}{Column 2} & \multirow{2}{*}{\(+1\)}
+    \multirow{4}{*}{Column 1} & \multirow{2}{*}{\(+1\)}
       & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{01})\),
@@
     \midrule
-        \multirow{4}{*}{Column 3} & \multirow{2}{*}{\(+1\)}
+        \multirow{4}{*}{Column 2} & \multirow{2}{*}{\(+1\)}
       & \((\nicefrac{1}{\sqrt{2}}) (\ket{00} + \ket{11})\),
@@
   combination of the \(-1\)-eigenspace depicted in
-  Table~\ref{tab:eigenv-cols} (column 1, row 2).  What is left is to
+  Table~\ref{tab:eigenv-cols} (column 0, row 1).  What is left is to
   show that Bob's state will be exactly the same as Alice's, implying
@@
     There exists a quantum strategy for the Mermin-Peres magic square
-    game, which consists of allowing Alice and Bob to exchange
+    game, which consists of allowing Alice and Bob exchanging
     entangled qubits \emph{before} the game begins, that wins with
@@
 basis. For any other basis \(B\), we must find an unitary
-transformation \(U\) such that \(B = U^{*} (Z \otimes I) U\) (where
-\(U^{*}\) denotes the Hermitian adjoint of \(U\)). For example,
-\(Z \otimes Z = \cnot{} (I \otimes Z) \cnot{}\) and
-\(X \otimes X = (H \otimes H) (Z \otimes Z) (H \otimes H)\). Figure~\ref{fig:change-basis}
-shows the unitaries for each of the nine observables.
+transformation \(U\) such that \(B = U^{*} (Z \otimes I) U\) or
+\(B = U^{*} (I \otimes Z) U\) (where \(U^{*}\) denotes the Hermitian
+adjoint of \(U\)). For example,
+\begin{equation}
+  Z \otimes Z = \cnot{} (I \otimes Z) \cnot{}
+\end{equation}
+and
+\begin{equation}
+  X \otimes X = (H \otimes H) (Z \otimes Z) (H \otimes H).
+\end{equation}
+Figure~\ref{fig:change-basis} shows the unitaries for each of
+the nine observables.
 
@@
 
-  \begin{figure}[htbp]
+  \begin{figure}[H]
     \centering
@@
 
+\subsection{A Note on Simultaneous Measurements}
+\label{sec:sim-meas}
+
 \subsection{Contextuality}
@@
 
+\textbf{TODO}
+
 \section{Characterizing Quantum Magic Games}
 \label{sec:extending}
-What if we change the format of the Mermin-Peres magic square game?
-Maybe increase the dimensions, or even change the shape entirely?
+What if we change the format of the magic square game?  Maybe increase
+the dimensions, or even change the shape entirely?
 Figure~\ref{fig:as-graph} (a) gives an example of the magic pentagram
@@
 shows the magic square as a hypergraph.  As the magic square, the
-pentagram is also due to Mermin~\ref{xxx}.  In this section, we
-explore a characterization of Mermin-style games, given
-by~\cite{arkhipov2012}.
+pentagram is also due to Mermin~\cite{mermin:1993}.  In this section,
+we explore a characterization of Mermin-style games, given
+by~\cite{arkhipov:2012}.
 
@@
   \end{subfigure}
-  \caption{Examples of hypergraphs representing quantum magic games~\cite{arkhipov2012}.\label{fig:as-graph}}
+  \caption{Examples of hypergraphs representing quantum magic games~\cite{arkhipov:2012}.\label{fig:as-graph}}
 \end{figure}
@@
 configurations on which Mermin-style games may be
-played. \cite{arkhipov2012} defines both unsigned and signed
+played. \cite{arkhipov:2012} defines both unsigned and signed
 arrangements. Instead, we shall focus  on \emph{signed}
@@
 
-\begin{definition}[Arrangement~\cite{arkhipov2012}]\label{def:arrangement}
+\begin{definition}[Arrangement~\cite{arkhipov:2012}]\label{def:arrangement}
   An arrangement \(A = (V, E, \ell)\) is a finite connected hypergraph
@@
 
-\begin{definition}[Classical Realization~\cite{arkhipov2012}]\label{def:classical-re}
+\begin{definition}[Classical Realization~\cite{arkhipov:2012}]\label{def:classical-re}
   A classical realization of an arrangement \(A = (V, E, \ell)\) is a
@@
 
-\begin{definition}[Quantum Realization~\cite{arkhipov2012}]\label{def:quantum-re}
-  A quantum realization of an arrangement \(A = (V, E, \ell)\) is a
-  labelling \(q\colon V \to \operatorname{GL}(\mathcal{H})\) is a
-  mapping from each vertex to an observable \(M\) on a fixed
+\begin{definition}[Quantum Realization~\cite{arkhipov:2012}]\label{def:quantum-re}
+  A quantum realization of an arrangement \(A~=~(V, E, \ell)\) is a
+  labelling \(q\colon V \to \operatorname{GL}(\mathcal{H})\) mapping
+  each vertex of the arrangement to an observable \(M\) on a
   finite-dimensional Hilbert-space \(\mathcal{H}\), such that
@@
   \item \(M\) is Hermitian and squares to the identity, or
-    equivalently, has eigenvalues \(\pm{}1\);
+    equivalently, has eigenvalues \(\pm{}1\).
 
   \item For each hyperedge, the observable assigned to its vertices
-    pairwise commute and
+    pairwise commute and.
 
@@
 Any arrangement that is quantumly realizable with observables that all
-mutually commute, then it is also classically
-realizable~\cite[Proposition 8]{arkhipov2012}. The proof follows by
+mutually commute is also classically
+realizable~\cite[Proposition 8]{arkhipov:2012}. The proof follows by
 the simultaneous diagonalization of the observables, similar to our
@@
 
-It turns out that the existence of a classical or quantum realization
-of an arrangement depends only on whether the number of \(-1\) labels
-is odd or even. This is called the \emph{parity} of the arrangement.
-
-\begin{definition}[Parity~\cite{arkhipov2012}]\label{def:parity}
+It turns out that the existence of a realization of an arrangement
+depends only on whether the number of \(-1\) labels is odd or
+even. This is called the \emph{parity} of the arrangement.
+
+\begin{definition}[Parity~\cite{arkhipov:2012}]\label{def:parity}
   The parity \(p(\ell)\) of an arrangement \(A = (V, E, \ell)\) is
@@
 realization for \(A' = (V, E, \ell')\) from the realization of
-\(A\)~\cite[Propositions 10 and 12]{arkhipov2012}. Furthermore, an
+\(A\)~\cite[Propositions 10 and 12]{arkhipov:2012}. Furthermore, an
 arrangement is classically realizable if, and only if, its parity is
-\(+1\)~\cite[Proposition 11]{arkhipov2012}. Despite this fundamental result,
-Classically realizable arrangements are not as much interesting as the
+\(+1\)~\cite[Proposition 11]{arkhipov:2012}. Despite this fundamental result,
+classically realizable arrangements are not as much interesting as the
 quantumly ones. Therefore, the goal is to characterize the gap between
@@
 
-\begin{definition}[Magic Arrangement~\cite{arkhipov}]\label{def:magic-arr}
-  An arrangement is said magic its parity is \(-1\) and it is
-  quantumly realizable.
+\begin{definition}[Magic Arrangement~\cite{arkhipov:2012}]\label{def:magic-arr}
+  An arrangement is said magic its parity is \(-1\) and there exists
+  a quantum realization of it.
 \end{definition}
@@
 
-\begin{definition}[Parity Telepathy Game~\cite{arkhipov2012}]\label{def:parity-game}
-  The parity telepathy game on an arrangement \(A = (V, E, \ell)\) is
+\begin{definition}[Parity Pseudo-Telepathy Game~\cite{arkhipov:2012}]\label{def:parity-game}
+  A parity pseudo-telepathy game on an arrangement \(A = (V, E, \ell)\) is
   a two-players cooperative game (say, played by Alice and Bob). The
-  game is conducted by a referee charlie. Alice and Bob may agree on a
+  game is conducted by a referee Charlie. Alice and Bob may agree on a
   prior strategy, but cannot communicate once the game starts. At each
@@
   \item Charlie randomly picks a vertex \(u \in V\) and one of the hyperedges
-    \(e \in E\) that contains \(u\);
-
-  \item Charlie sends the vertex \(u\) to Alice and the hyperedge \(e\) to Bob;
+    \(e \in E\) that contains \(u\).
+
+  \item Charlie sends the vertex \(u\) to Alice and the hyperedge \(e\) to Bob.
 
   \item Alice labels the vertex \(u\) with \(a(u) = \pm{}1\) and sends
-    \(a(u)\) to Charlie;
+    \(a(u)\) to Charlie.
 
   \item Bob labels each vertex \(v \in e\) with \(b(v) = \pm{}1\) and sends
-    each \(b(v)\) to Charlie;
+    each \(b(v)\) to Charlie.
 
@@
 square game seen in Section~\ref{sec:magic-square}, where Alice
-receives a hyperedge from Charlie. This modification generalizes to
+receives a hyperedge. This modification generalizes to
 arrangements that do not share the property exhibited by the magic
@@
 
-There exists a strategy that wins with certainty a parity telepathy
+There exists a strategy that wins with certainty a parity pseudo-telepathy
 game played on a magic arrangement that has a quantum realization in
@@
 and Bob can share entanglement in advance~\cite[Theorem
-17]{arkhipov2012}. It suffices for them to share a maximally entangled
+17]{arkhipov:2012}. It suffices for them to share a maximally entangled
 state
@@
 
-We now move on to the main result of~\cite{arkhipov2012}. We shall
+We now move on to the main result of~\cite{arkhipov:2012}. We shall
 derive a characterization of magic arrangements by the planarity of
@@
 
-We now restate the main result of~\cite{arkhipov2012} and its proof,
+We now restate the main result of~\cite{arkhipov:2012} and its proof,
 further illustrating it with examples.
@@
   is \(+1\) and, consequently, it is not magic. The strategy consists
-  of repeatedly contracting edges of the intersection, and show that
-  contraction preserves a few properties. To contract an edge is to
-  merge the two endpoints \(v\) and \(w\) into a new vertex
-  \(u\). Every edge that used to touch \(v\), now touches \(u\), and
-  every edge that used to touch \(w\), now touches
-  \(u\). Consequently, the edge that was contracted becomes two
-  self-loops. Moreover, we define the label of the new vertex \(w\) as
-  the product of the labels of \(u\) and \(v\). We observe that
-  contraction preserves the following properties:
+  of repeatedly contracting edges of the intersection, and showing
+  that contraction preserves a few properties. To contract an edge is
+  to merge the two endpoints \(e_{0}\) and \(e_{1}\) into a new vertex
+  \(e'\) (notice that we are using \(e\) to represent vertices,
+  because these vertices correspond to hyperedges of the
+  arrangement). Every edge that used to touch \(e_{0}\), now touches
+  \(e'\), and every edge that used to touch \(e_{1}\), now touches
+  \(e'\). Consequently, the edge that was contracted becomes two
+  self-loops. Moreover, we define the label of the new vertex \(e'\)
+  as the product of the labels of \(e_{0}\) and \(e_{1}\). We observe
+  that contraction preserves the following properties:
 
@@
     preserved. Let \(M_{0}, \ldots, M_{n-1}\) be the observables
-    around a vertex \(v\), going counterclockwise. If
-    \(M_{0} \ldots M_{n - 1} = \ell(v) I\), then for any starting
+    around a vertex \(e\), going counterclockwise. If
+    \(M_{0} \ldots M_{n - 1} = \ell(e) I\), then for any starting
     point \(k\),
-    \(M_{k} M_{k+1}\ldots M_{n-1}M_{0}\ldots M_{k-1} = \ell(v) I\),
+    \(M_{k} M_{k+1}\ldots M_{n-1}M_{0}\ldots M_{k-1} = \ell(e) I\),
     since
@@
       &= (M_{k-1}\ldots M_{0})(M_{0} \ldots M_{n-1})(M_{0}\ldots M_{k-1})  \label{eq:cyclic1} \\
-      &= (M_{k-1}\ldots M_{0})\ell(v) I(M_{0}\ldots M_{k-1}) = \ell(v) I,  \label{eq:cyclic2}
+      &= (M_{k-1}\ldots M_{0})\ell(e) I(M_{0}\ldots M_{k-1}) \\
+      &= \ell(e) I,  \label{eq:cyclic2}
     \end{align}
     where (\ref{eq:cyclic1}) follows from the fact that
-    \(M_{i} M_{i} = \ell(v) I\). Now, let \(X\) be the measurement assigned to
+    \(M_{i} M_{i} = I\). Now, let \(X\) be the measurement assigned to
     the edge that is being contracted and let the labels around its
-    endpoints \(v\) and \(w\) be \(M_{0}\ldots M_{m-1}X\) and
+    endpoints \(e_{0}\) and \(e_{1}\) be \(M_{0}\ldots M_{m-1}X\) and
     \(X N_{0}\ldots N_{n-1}\) going counterclockwise. Then,
-    \(M_{0} \ldots M_{m-1} X = \ell(v)I\) and
-    \(X N_{0} \ldots N_{n-1} = \ell(w)I\). Multiplying these gives
+    \[
+      M_{0} \ldots M_{m-1} X = \ell(e_{0})I
+    \]
+    and
+    \[
+      X N_{0} \ldots N_{n-1} = \ell(e_{1})I.
+    \]
+    Multiplying these gives
     \[
@@
       M_{0}\ldots M_{m-1} N_{0} \ldots N_{n-1} =
-      \ell(v) \ell(w) I = \ell(u) I,
+      \ell(e_{0}) \ell(e_{1}) I = \ell(e') I,
     \]
-    so the product of the observables around the new vertex \(w\)
+    so the product of the observables around the new vertex \(e'\)
     still is the identity times its label. Notice that key to this
@@
     draw the edges around the new vertex without mixing the edges that
-    used to touch \(v\) and \(w\).
+    used to touch \(e_{0}\) and \(e_{1}\).
   \end{enumerate}
@@
 
-It remains to show the other direction of the result. That is, the
+It remains to show the other direction of the result. That is, if the
 intersection graph of an arrangement is nonplanar, than the
@@
 \begin{proof}
-  By the Pontyagin and Kuratowski theorem, everry nonplanar graph contains either
+  By the Pontyagin-Kuratowski theorem, everry nonplanar graph contains either
   the \(K_{5}\) or the \(K_{3,3}\) graph as a topological minor. We have already seen
@@
   to construct a realization for another arrangement on the same
-  vertices and hyperedges, and of same parity), and thus it does not
+  vertices and hyperedges and of same parity), and thus it does not
   matter how you label the vertices of \(G\), as long as its parity
@@
 
-  \item Every vertex of \(G\) that lies on a simple path corresponing
+  \item Every vertex of \(G\) that lies on a simple path corresponding
     to an edge in \(H\) touches two edges (in and out) labelled with

### 2023-07-04 paper/main.tex
paper => compatibility

@@
 
-\subsection{Formal Proof}
+\subsection{Formal Proof}\label{sec:msquare-proof}
 To prove that the quantum solution indeed works, we must demonstrate
@@
 
-\subsection{A Note on Simultaneous Measurements}
+\subsection{A Note on Compatible Observables}
 \label{sec:sim-meas}
+
+As seen in the Section~\ref{sec:msquare-proof}, the operators on each
+row and column are compatible. That is, for any row and any column,
+the observables pairwise commute. This means that they can be
+simultaneously diagonalized by the same eigenvectors. It turns out
+that the simultaneous measurement of compatible operators is
+equivalent to the measurement of a single nondegenerate
+operator~\cite{peres:1997}. That is, instead of performing three
+measurements, one for each cell, Alice and Bob could perform a single
+measurement each, whose answers would tell them to which of the four
+common eigenvectors their qubits would have collapsed to, had they
+performed the individual measurements. Based on this, they could fill
+each cell with the eigenvalue that corresponds to that eigenvector. To
+construct these single measurements for each row and column, it
+suffices to take the projectors onto the eigenvectors shared by the
+observables. Example~\ref{ex:sim-meas} further illustrates this idea.
+
+\begin{tcbexample}{Simultaneous Measurement}{sim-meas}
+  Consider, for instance, the first row of the quantum solution for
+  the magic square game, depicted in Figure~\ref{fig:quantum}. The
+  observables in this row are \(I \otimes Z\), \(Z \otimes I\), and
+  \(Z \otimes Z\). The eigenvectors common to these operators are
+  \ket{00}, \ket{01}, \ket{10}, and \ket{11}. Alice, then, could
+  simply construct an observable
+  \[M = \ketbra{00}{00} + 2 \ketbra{01}{01} + 3 \ketbra{10}{10} + 4
+    \ketbra{11}{11},\] which corresponds to the diagonal matrix
+  \begin{equation*}
+    M = \begin{pmatrix}
+          1 & 0 & 0 & 0 \\
+          0 & 2 & 0 & 0 \\
+          0 & 0 & 3 & 0 \\
+          0 & 0 & 0 & 4
+    \end{pmatrix}.
+  \end{equation*}
+  By measuring \(M\) on her qubits, she would observe (with
+  probability \(\nicefrac{1}{4}\)) the outcomes \(1\), \(2\), \(3\), or
+  \(4\) , which uniquely identifies one of the four eigenvectors
+  \ket{00}, \ket{01}, \ket{10}, or \ket{11}. Consequently, she would
+  know the eigenvalues associated with the eigenvector ``observed'',
+  and would be able to correctly fill the cells of the first row. For
+  example, outcome \(3\) corresponds to \ket{10}. Hence, if she
+  observes \(3\), she fills the first row with \(\{+1, -1, -1\}\).
+\end{tcbexample}
 
@@
 \label{sec:context}
-
-\textbf{TODO}
 

### 2023-07-05 paper/main.tex
paper => typos

@@
 \begin{definition}[Magic Arrangement~\cite{arkhipov:2012}]\label{def:magic-arr}
-  An arrangement is said magic its parity is \(-1\) and there exists
+  An arrangement is said magic if its parity is \(-1\) and there exists
   a quantum realization of it.

### 2023-07-05 paper/main.tex
paper => proof kochen-specker

@@
 
-\subsection{Contextuality}
+\subsection{A Proof of The Kochen-Specker Theorem}
 \label{sec:context}
+
+The Kochen-Specker theorem~\cite{kochen:1967} demonstrates
+the incompatilibty between an interpretation of quantum mechanics
+that is both deterministic ---~in the sense that there exists
+hidden variables that we do not have access to, and thus
+the stochasticity that we observe is merely epistemic~--- and,
+at the same time, noncontextual. Noncontextuality means that
+the outcomes of a measurement do not depend on the context,
+where a context is a set of compatible observables.
+
+Consider the magic square game described above. In a noncontextual
+hidden-variable model, we should be able to ascribe pre-determined
+outcomes to the nine observables in each cell. That is, for each
+observable \(M_{i, j}\) in a cell \((i, j)\), there should be an
+assignment \(v(M_{i, j}) = \pm{}1\). However, as seen in
+Section~\ref{sec:classic-sol}, this is impossible. Hence, either the
+model must be contextual, meaning that the outcomes of the
+measurements are influenced by the context in which they are inserted
+---~for instance, pick any observable in the \(3 \times 3\) grid shown
+in Figure~\ref{fig:quantum} and recall that it commutes with the other
+two observables in the row and also in the column; then, the result of
+measuring this observable is influenced by whether you are measuring
+it in the row or in the column~---, or there cannot exist hidden
+variables governing the values assigned to each observable.
 

### 2023-07-06 paper/main.tex
paper => example main result

@@
 
+\begin{tcbexample}{Nonplanar Graph \(\implies\) Magic}{nplanar-magic}
+  Recall that the complete bipartite graph \(K_{3, 3}\) is the intersection
+  graph of the magic square. Figure~\ref{fig:k33} shows the
+  \(K_{3, 3}\), labelled accordingly to the magic square game
+  described in Section~\ref{sec:magic-square}.
+
+  \begin{figure}[H]
+    \begin{center}
+      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
+        \node (e'0) [vertex, label=above right:{\(e'_{0}\)}, label=above left:{\color{green!50!black!80}\(+I\)}] at (0, 0) {};
+        \node (e'1) [vertex, label=above right:{\(e'_{1}\)}, label=above left:{\color{green!50!black!80}\(+I\)}] at (4, 0) {};
+        \node (e'2) [vertex, label=above right:{\(e'_{2}\)}, label=above left:{\color{green!50!black!80}\(+I\)}] at (8, 0) {};
+        \node (e'3) [vertex, label=below right:{\(e'_{3}\)}, label=below left:{\color{red!50!black!80}\(-I\)}] at (0, -3) {};
+        \node (e'4) [vertex, label=below right:{\(e'_{4}\)}, label=below left:{\color{red!50!black!80}\(-I\)}] at (4, -3) {};
+        \node (e'5) [vertex, label=below right:{\(e'_{5}\)}, label=below left:{\color{red!50!black!80}\(-I\)}] at (8, -3) {};
+
+        \path[]
+        (e'0) edge node[midway, fill=gray!15] {\(I \otimes Z\)} (e'3)
+        edge node[near start, fill=gray!15, xshift=-.3cm] {\(Z \otimes I\)} (e'4)
+        edge node[near start, fill=gray!15] {\(Z \otimes Z\)} (e'5)
+
+        (e'1) edge node[near end, fill=gray!15] {\(X \otimes I\)} (e'3)
+        edge node[near end, fill=gray!15] {\(I \otimes X\)} (e'4)
+        edge node[near end, fill=gray!15, xshift=0.3cm] {\(X \otimes X\)} (e'5)
+
+        (e'2) edge node[near start, fill=gray!15, xshift=-0.1cm, yshift=.1cm] {\(-X \otimes Z\)} (e'3)
+        edge node[near start, fill=gray!15, xshift=0.3cm] {\(-Z \otimes X\)} (e'4)
+        edge node[midway, fill=gray!15] {\(Y \otimes Y\)} (e'5)
+        ;
+      \end{tikzpicture}
+    \end{center}
+    \caption{\(K_{3, 3}\) corresponding to the magic square arrangement.\label{fig:k33}}
+  \end{figure}
+  Consider the Petersen graph shown in Figure~\ref{fig:petersen} (a).
+  Figure~\ref{fig:petersen} (b) shows the same graph, rewritten in a
+  way that it is easy to see that it has the \(K_{3, 3}\) graph as a
+  topological minor.
+
+  \begin{figure}[H]
+    \begin{subfigure}{0.475\textwidth}
+      \begin{center}
+        \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
+          \foreach \l [
+          count=\c,
+          evaluate=\c as \ang using {18 + 72*\c},
+          evaluate=\c as \e using {iseven(\c - 1)?"{\color{green!50!black!80}+I}":"{\color{red!50!black!80}-I}"}
+          ] in {0, 1, 2, 3, 4} {
+            \node [vertex] (e\l) at (\ang:20mm) {};
+            \node at (\ang:24mm) {\(e_{\l}\)};
+            \node at ({\ang + 11}:22mm) {\(\e\)};
+          }
+
+          \foreach \l [
+          count=\c,
+          evaluate=\c as \ang using {18 + 72*\c},
+          evaluate=\c as \e using {\c>1?"{\color{green!50!black!80}+I}":"{\color{red!50!black!80}-I}"}
+          ] in {5, 6, 7, 8, 9} {
+            \node [vertex] (e\l) at (\ang:10mm) {};
+            \node at ({\ang - 18}:12mm) {\(e_{\l}\)};
+            \node at ({\ang + 18}:12mm) {\(\e\)};
+          }
+
+          \path[]
+          (e0) edge (e1) edge (e4) edge (e5)
+          (e1) edge (e2) edge (e6)
+          (e2) edge (e3) edge (e7)
+          (e3) edge (e8) edge (e4)
+          (e4) edge (e9)
+          (e5) edge (e7) edge (e8)
+          (e6) edge (e8) edge (e9)
+          (e7) edge (e9)
+          ;
+        \end{tikzpicture}
+      \end{center}
+      \caption{}
+    \end{subfigure}
+    \hfill{}
+    \begin{subfigure}{0.475\textwidth}
+      \begin{center}
+        \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
+          \node (e0) [vertex, label=left:{\(e_{0}\)}] at (0, 0) {};
+          \node (e2) [vertex, label=left:{\(e_{2}\)}] at (2.5, 0) {};
+          \node (e8) [vertex, label=left:{\(e_{8}\)}] at (5, 0) {};
+          \node (e1) [vertex, label=left:{\(e_{1}\)}] at (0, -2) {};
+          \node (e3) [vertex, label=left:{\(e_{3}\)}] at (2.5, -2) {};
+          \node (e5) [vertex, label=below:{\(e_{5}\)}] at (5, -2) {};
+
+          \node (e4) [vertex, label=above:{\(e_{4}\)}] at (1.25, 0) {};
+          \node (e6) [vertex, label=below:{\(e_{6}\)}] at (1.25, -2) {};
+          \node (e7) [vertex, label=left:{\(e_{7}\)}] at (3.75, -2) {};
+          \node (e9) [vertex, label=left:{\(e_{9}\)}] at (3.75, 0) {};
+
+          \path[]
+          (e0) edge (e1) edge (e4) edge (e5)
+          (e1) edge (e2) edge (e6)
+          (e2) edge (e3) edge (e7)
+          (e3) edge (e8) edge (e4)
+          (e4) edge[bend left] (e9)
+          (e5) edge (e7) edge (e8)
+          (e6) edge (e8) edge (e9)
+          (e7) edge (e9)
+          ;
+        \end{tikzpicture}
+      \end{center}
+      \caption{}
+    \end{subfigure}
+    \caption{Petersen graph.\label{fig:petersen}}
+  \end{figure}
+
+  Let \(\phi\) be the function mapping vertices from \(K_{3, 3}\)
+  graph to the Petersen graph. Then,
+  \begin{align*}
+    \phi(e'_{0}) &= e_{0} \\
+    \phi(e'_{1}) &= e_{2} \\
+    \phi(e'_{2}) &= e_{8} \\
+    \phi(e'_{3}) &= e_{1} \\
+    \phi(e'_{4}) &= e_{3} \\
+    \phi(e'_{5}) &= e_{5}.
+  \end{align*}
+
+  Following the proof of Theorem~\ref{theo:main}, we assume that the
+  vertices with a correspondence in the \(K_{3, 3}\) graph are
+  labelled in the same way, and the remaining are labelled with
+  \(+I\).  To construct a quantum realization of the Petersen graph,
+  we first look for simples paths that correspond to edges in
+  \(K_{3, 3}\). For example, the edge \((e_{0}, e_{1})\) in Petersen
+  corresponds exactly to the edge \((e'_{0}, e'_{3})\) in
+  \(K_{3, 3}\), so we assign the operator \(I \otimes Z\) to
+  it. Similarly, the path \((e_{0}, e_{4}, e_{3})\) in Petersen
+  corresponds to the edge \((e'_{0}, e'_{4})\) in \(K_{3, 3}\), so we
+  assign the operator \(Z \otimes I\) to both edges \((e_{0}, e_{4})\)
+  and \((e_{4}, e_{3})\). We keep doing this for every path that has a
+  correspondence in the \(K_{3, 3}\) graph. Then, we label the
+  remaining edges with \(+I\). Figure~\ref{fig:petersen-final} shows
+  the quantum realization constructed for the Petersen graph.
+
+  \begin{figure}[H]
+    \begin{center}
+      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
+        \foreach \l [
+        count=\c,
+        evaluate=\c as \ang using {18 + 72*\c},
+        evaluate=\c as \e using {iseven(\c - 1)?"{\color{green!50!black!80}+I}":"{\color{red!50!black!80}-I}"}
+        ] in {0, 1, 2, 3, 4} {
+          \node [vertex] (e\l) at (\ang:30mm) {};
+          \node at (\ang:34mm) {\(e_{\l}\)};
+          \node at ({\ang + 8}:32mm) {\(\e\)};
+        }
+
+        \foreach \l [
+        count=\c,
+        evaluate=\c as \ang using {18 + 72*\c},
+        evaluate=\c as \e using {\c>1?"{\color{green!50!black!80}+I}":"{\color{red!50!black!80}-I}"}
+        ] in {5, 6, 7, 8, 9} {
+          \node [vertex] (e\l) at (\ang:20mm) {};
+          \node at ({\ang - 10}:20mm) {\(e_{\l}\)};
+          \node at ({\ang + 13}:20mm) {\(\e\)};
+        }
+
+        \path[]
+        (e0) edge node[midway, fill=gray!15] {\(I \otimes Z\)} (e1)
+        edge node[midway, fill=gray!15] {\(Z \otimes I\)} (e4)
+        edge node[midway, fill=gray!15] {\(Z \otimes Z\)} (e5)
+        (e1) edge node[midway, fill=gray!15] {\(X \otimes I\)} (e2)
+        edge node[midway, fill=gray!15, rotate=80] {\(-X \otimes Z\)} (e6)
+        (e2) edge node[midway, fill=gray!15] {\(I \otimes X\)} (e3)
+        edge node[midway, fill=gray!15, rotate=-30] {\(X \otimes X\)} (e7)
+        (e3) edge node[midway, fill=gray!15, rotate=30] {\(-Z \otimes X\)} (e8)
+        edge node[midway, fill=gray!15] {\(Z \otimes I\)} (e4)
+        (e4) edge node[midway, fill=gray!15, rotate=-30] {\(+I\)} (e9)
+        (e5) edge node[midway, fill=gray!15] {\(X \otimes X\)} (e7) edge node[midway, fill=gray!15] {\(Y \otimes Y\)} (e8)
+        (e6) edge node[midway, fill=gray!15, rotate=45] {\(-X \otimes Z\)} (e8)
+        edge node[midway, fill=gray!15] {\(+I\)} (e9)
+        (e7) edge node[midway, fill=gray!15, rotate=-45] {\(+I\)} (e9)
+        ;
+      \end{tikzpicture}
+    \end{center}
+    \caption{Quantum realiation of the Petersen graph, constructed from \(K_{3, 3}\) (magic square)}
+    \label{fig:petersen-final}
+  \end{figure}
+\end{tcbexample}
+
 \section{Conclusion}\label{sec:conc}

### 2023-07-06 paper/main.tex
paper => refactor

@@
 \begin{abstract}
-  \textbf{TODO}
+This paper explores the phenomenon of quantum pseudo-telepathy, a form of communication that exhibits properties resembling telepathy by leveraging aspects of the quantum realm.
+Specifically, the focus is on the Mermin-Peres magic square game, which exemplifies quantum pseudo-telepathy and provides a simplified proof for the Kochen-Specker theorem.
+The paper begins by discussing various examples of quantum pseudo-telepathy games and their incompatibility with classical winning strategies, highlighting the necessity of prior entanglement between players.
+Additionally, it delves into the intricacies of the magic square game, classical approaches, the impossibility of consistent classical winning, and the rationale behind the successful implementation of a quantum strategy.
+Moreover, it explores the connection between the game and the proof of the incompatibility of noncontextual hidden-variable theories.
+Furthermore, a generalization of games similar to the magic square, proposed by Arkhipov, is presented.
+Ultimately, through this investigation, the paper sheds light on the fascinating realm of quantum pseudo-telepathy and its implications for our understanding of classical physics and quantum mechanics.
 \end{abstract}
@@
 that follow the same style of the magic square game, given
-by Arkhipov~\cite{arkhipov:2012}. Finally, Section~\ref{sec:conc} concludes the
-presentation.
+by Arkhipov~\cite{arkhipov:2012}. Finally, Section~\ref{sec:conc} concludes this report.
 
@@
 observables in the \(j\)-th column that was assigned to him, and fills
-each of his cells with the outcomes of each
-measurement. Example~\ref{ex:quantum-sol} depicts a round of the game.
+each of his cells with the outcomes of each measurement. (It is worth
+to point out that the order of their measurements is not important.)
+Example~\ref{ex:quantum-sol} depicts a round of the game.
 
@@
   \begin{equation}
-    \ket{\psi}_{A1} =  \frac{1}{\sqrt{2}}(\ket{0000} + \ket{1010}),
+    \ket{\psi}_{A0} =  \frac{1}{\sqrt{2}}(\ket{0000} + \ket{1010}),
   \end{equation}
-  where the subscript \(A1\) denotes the state after Alice's first
+  where the subscript \(A0\) denotes the state after Alice's first
   measurement.  For the second cell, Alice measures the observable
@@
   \begin{equation}
-    \ket{\psi}_{A2} =  \ket{1010}.
+    \ket{\psi}_{A1} =  \ket{1010}.
   \end{equation}
@@
   \(-1\), and the state does not change, i.e.
-  \(\ket{\psi}_{A3} = \ket{\psi}_{A2}\).  Alice, then, fills the first
+  \(\ket{\psi}_{A2} = \ket{\psi}_{A1}\).  Alice, then, fills the first
   row with the values \(\{+1, -1, -1\}\), whose product is, as
@@
   I\). The only possible outcome, considering the state
-  \(\ket{\psi}_{A3}\), is \(-1\) ---~which matches Alice's answer~---
+  \(\ket{\psi}_{A2}\), is \(-1\) ---~which matches Alice's answer~---
   and the state will not change again:
-  \(\ket{\psi}_{B1} = \ket{\psi}_{A3}\). Moving on to the second cell,
+  \(\ket{\psi}_{B0} = \ket{\psi}_{A2}\). Moving on to the second cell,
   Bob measures the observable \(I \otimes X\), whose possible outcomes
@@
   \begin{equation}
-    \ket{\psi}_{B2} =  \frac{1}{\sqrt{2}}(\ket{1010} + \ket{1011}).
+    \ket{\psi}_{B1} =  \frac{1}{\sqrt{2}}(\ket{1010} + \ket{1011}).
   \end{equation}
@@
   Bob will for sure observe the outcome \(+1\) and the state does not
- change, i.e.  \(\ket{\psi}_{B3} = \ket{\psi}_{B2}\). Therefore, Bob
+ change, i.e.  \(\ket{\psi}_{B2} = \ket{\psi}_{B1}\). Therefore, Bob
   answers \(\{-1, +1, +1\}\). Alice's answer satisfies the property of
@@
 three measurements on each row (equivalently, column) is equal to 1
-(equiv. -1). Second, the outcome of Alice's measurement on the
+(equivalently, -1). Second, the outcome of Alice's measurement on the
 intersection is always equal to the outcome of
@@
   \(P_{i}\Lambda_{i}P_{i}^{-1} = I\); thus, \(\Lambda_{i} = I\) and
-  the only possible value for the product is \(1\) (equivalently
+  the only possible value for the product is \(1\) (equivalently,
   \(-1\) for columns). \qed
@@
   second qubits) and the symmetry is preserved by any measurement
-  performed by Alice and Bob. For the first row, it is easy to see.
+  performed by Alice and Bob. For the first row, this is easy to see.
   The others are trickier, but it all boils down to doing the
@@
   \((\nicefrac{1}{2}) (\ket{00} - \ket{01} - \ket{10} +
-  \ket{11})\). The state after the first measurement is
+  \ket{11})\). The complete state after the first measurement is
   \begin{align}
@@
     There exists a quantum strategy for the Mermin-Peres magic square
-    game, which consists of allowing Alice and Bob exchanging
+    game, which consists of allowing Alice and Bob to exchange
     entangled qubits \emph{before} the game begins, that wins with
@@
       \end{array}\]
-    \caption{Unitary transformations required for measuring in the
-      different basis. The actual basis measured is the middle
+    \caption{Unitary transformations required for measuring in
+      different bases. The actual basis measured is the middle
       term of each cell, which, after expanding, is either
@@
 
-As seen in the Section~\ref{sec:msquare-proof}, the operators on each
+As seen in Section~\ref{sec:msquare-proof}, the operators on each
 row and column are compatible. That is, for any row and any column,
@@
   probability \(\nicefrac{1}{4}\)) the outcomes \(1\), \(2\), \(3\), or
-  \(4\) , which uniquely identifies one of the four eigenvectors
+  \(4\), which uniquely identifies one of the four eigenvectors
   \ket{00}, \ket{01}, \ket{10}, or \ket{11}. Consequently, she would
@@
 round, Charlie sends the vertex \(u\) to Alice and the line \(e\) to
-Bob. In the second half, Charlie sends \(u\) to Bob, but
-\emph{another} line \(e' \neq e\) to Alice.
+Bob. In the second half, Charlie sends \(u\) to Bob, but the other
+line \(e'\) containing \(u\) to Alice.
 
@@
   \(+I\).  To construct a quantum realization of the Petersen graph,
-  we first look for simples paths that correspond to edges in
+  we first look for simple paths that correspond to edges in
   \(K_{3, 3}\). For example, the edge \((e_{0}, e_{1})\) in Petersen
@@
 \section{Conclusion}\label{sec:conc}
+In this work, we described the two-players cooperative quantum magic
+game known as the magic square game, that exhibits the so-called
+property of pseudo-telepathy. In other words, it is a game that is
+impossible to systematically win under classical assumptions (i.e.\
+when restricted to a classical solution, if the players are always
+winning, the referee can suspect that they are somehow cheating and
+communicating), but that there exists a quantum strategy that wins
+every round with certainty, which gives the impression that some sort
+of communication is going on (hence ``pseudo-telepathy'').
+We described the classical and quantum strategies, showed why
+the quantum approach works, and how to implement it with
+quantum circuits. We also briefly discussed the connection between the
+magic square game and the Kochen-Specker theorem, which states the
+incompatibility between a quantum mechanics model that is both
+noncontextual and deterministic.
+
+We concluded by describing a generalization of games that follow the same
+style of the magic square, also known as Mermin-style games, given by
+Arkhipov~\cite{arkhipov:2012}. In this generalization, the quantum
+games are represented by hypergraphs whose hyperedges encode the
+constraints of the game and whose vertices must be labelled by the
+players in a way that this labelling respects those constraints. In the
+case of the magic square, the hyperedges are the three rows and three
+columns, and the vertices are each cell of the grid. Arkhipov showed
+in his work that there exists a subset of these games that are
+``magical'' in the sense that they cannot be won classically, but they
+admit a quantum strategy. This quantum solution, as in the magic
+square case, consists of the two players sharing a symmetric,
+entangled state. Furthermore, the arrangement on which these games are
+played can be characterized in terms of the (non)planarity of the
+corresponding intersection graphs: the arrangement is magic if, and
+only if, its intersection graph is nonplanar.
 

### 2023-07-06 paper/main.tex
Paper => typos
refactor intro

@@
 
-In this project, we will explore the Mermin-Peres magic square game
-(hereinafter referred simply as magic square). The origins of this
-game date back to the ninities. It was first described in the works of
-Mermin~\cite{mermin:1990, mermin:1993} and of
-Peres~\cite{peres:1990, peres:1997}. Their results provided (as per the title of
-Mermin's review letter) a simplied proof for the Kochen-Specker
+In this project, we will explore the Mermin-Peres magic square game.
+% (hereinafter referred simply as magic square).
+The origins of this
+game date back to the ninities. It was first described by
+Mermin~\cite{mermin:1990, mermin:1993} and 
+Peres~\cite{peres:1990, peres:1997}. Their results provided
+% (as per the title of Mermin's review letter)
+a simplied proof for the Kochen-Specker
 theorem~\cite{kochen:1967}. Later, in 2002, Aravind demonstrated how
@@
 challenging, but their descriptions can be greatly simplified by
-modeling them as quantum games.  In particular, it is extremely easy
+modeling them as quantum games.  In particular, it is easy
 to show that there cannot be a classical solution to the the magic
@@
 (classically impossible) is happening in a successful implementation
-of a quantum winnin strategy~\cite{brassard:2005}.
+of a quantum winning strategy~\cite{brassard:2005}.
 
 \paragraph{Outline of this paper.}
-In Section~\ref{sec:magic-square}, we detail the intrinsics of the
-magic square game, classical approaches and why it is impossible to
-systematically win the game classically, how and why the quantum
-strategy works, and how to implement it. We also briefly discuss how
-the game translates to the proof of incompatibility of a
-noncontextual hidden-variable theory. Then, in
-Section~\ref{sec:extending}, we describe a generalization of games
-that follow the same style of the magic square game, given
-by Arkhipov~\cite{arkhipov:2012}. Finally, Section~\ref{sec:conc} concludes this report.
+In Section~\ref{sec:magic-square}, we detail the magic square game,
+classical approaches and why it is impossible to systematically win
+the game classically, how and why the quantum strategy works, and how
+to implement it. We also briefly discuss how the game translates to
+the proof of incompatibility of a noncontextual hidden-variable
+theory. Then, in Section~\ref{sec:extending}, we describe a
+generalization of games of the same style, given by
+Arkhipov~\cite{arkhipov:2012}. Section~\ref{sec:conc} concludes this
+report.
 
@@
 strategy is that the outcomes of all possible measurements are
-\(\pm 1\). The initial, entangled state is (subscripts \(A\) and \(B\)
+\(\pm 1\). The initial entangled state is (subscripts \(A\) and \(B\)
 indicate, respectively, Alice's and Bob's qubits)

### 2023-07-06 paper/main.tex
paper => conclusion

--- 2023-07-06 paper/main.tex
@@
 \begin{abstract}
-This paper explores the phenomenon of quantum pseudo-telepathy, a form of communication that exhibits properties resembling telepathy by leveraging aspects of the quantum realm.
-Specifically, the focus is on the Mermin-Peres magic square game, which exemplifies quantum pseudo-telepathy and provides a simplified proof for the Kochen-Specker theorem.
-The paper begins by discussing various examples of quantum pseudo-telepathy games and their incompatibility with classical winning strategies, highlighting the necessity of prior entanglement between players.
-Additionally, it delves into the intricacies of the magic square game, classical approaches, the impossibility of consistent classical winning, and the rationale behind the successful implementation of a quantum strategy.
-Moreover, it explores the connection between the game and the proof of the incompatibility of noncontextual hidden-variable theories.
-Furthermore, a generalization of games similar to the magic square, proposed by Arkhipov, is presented.
-Ultimately, through this investigation, the paper sheds light on the fascinating realm of quantum pseudo-telepathy and its implications for our understanding of classical physics and quantum mechanics.
+  \textbf{TODO}
 \end{abstract}
@@
 that follow the same style of the magic square game, given
-by Arkhipov~\cite{arkhipov:2012}. Finally, Section~\ref{sec:conc} concludes this report.
+by Arkhipov~\cite{arkhipov:2012}. Finally, Section~\ref{sec:conc} concludes the
+presentation.
 
@@
 observables in the \(j\)-th column that was assigned to him, and fills
-each of his cells with the outcomes of each measurement. (It is worth
-to point out that the order of their measurements is not important.)
-Example~\ref{ex:quantum-sol} depicts a round of the game.
+each of his cells with the outcomes of each
+measurement. Example~\ref{ex:quantum-sol} depicts a round of the game.
 
